### 2012-07-07 article.tex
comment: initalia push

%\documentclass[a4paper,10pt]{article}
\documentclass[journal]{IEEEtran}
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

\usepackage{cite} %for citations

 %this is for math typing (eg: cases)
\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{epsfig} %for figures

\usepackage[center]{caption}%for captions
\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures

%opening
\title{ 
	Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.
}

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
	Brian~Quang-Huy~Nguyen,
	Nicholas~Chan-Hua~Vun%
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen, Nicholas~Chan-Hua~Vun, and Ian~McLoughlin are with School of Computer Engineering, 
Nanyang Technological University, Singapore,}% <-this % stops a space
%\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, Jul~2012}%
{ Le \MakeLowercase{\textit{et al.}}: Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters }

\begin{document}

\maketitle

\begin{abstract}

Logarithmic transformation has the potential to convert 
	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
	a simpler additive and homoskedastic distribution model.
From this homoskedastic model, within the log-transformed domain, 
	a few consistent measures of distance emerge.
With these subtractive differences become consistent and predictable, 
	we show, through experiments and analysis, that 
	the familiar mean squared error (MSE) criteria can reliably serve 
		as a single unifying performance indicator to evaluate SAR speckle filters. 
In homogeneous areas, we determine a mathematical relationship that links the variance of log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
	is shown to be equivalent to the ratio-based radiometric preservation criteria usually assessed in the original domain. 
Through experiments, and analysis, we show that lower MSE suggests better feature detection and classification ability, an important requirement for subsequent post-filtering steps in practical SAR data processing.
Combined, we propose and describe the use of log-transformed MSE to evaluate SAR speckle filters.

\end{abstract}

\begin{IEEEkeywords}
Synthetic aperture radar, speckle-filtering, homoskedasticity, mean-squared-error
\end{IEEEkeywords}

%\textbf{Keywords: } Synthetic Aperture Radar, speckle-filtering, homoskedasticity

\IEEEpeerreviewmaketitle

\section{Introduction}

The nature of SAR speckle is that:
	it is stochastic even when the underlying radiometry is constant, 
	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
Nevertheless, statistical models are developed to derive the underlying back-scattering coefficient ($\sigma$) from the measured SAR data. 
Then speckle filters are, by and large, estimators that attempt to determine the unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluating of the performance of estimators. 
The estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance, hence lower MSE, indicates better performances. 
Ideally, estimators' evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
Also, due to the stochastic nature of SAR and simulation process, 
	statistical summaries of repeated simulating experiments are normally preferred to single-run results.

A survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is found to be inapplicable.
%This makes the standard mean-squared-error evaluation to be inapplicable, at least in the original domain. 
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric to evaluate speckle filters.

The common theme is that each newly proposed speckle filter is often found to be published along with a customised methodology of evaluating its own performance.
And many papers lack any comparative basis beyond simple visual qualititave comparisions on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, regretably it lacks scientific objectivity. 
Other papers do present quantitative measurements, 
	however  due to the lack of a standardized performance criteria, 
	the evaluation metrics change eccentrically from one paper to the next.

The rest of this paper is structured as follows.
While Section \ref{sec:lit_review} briefly surveys related work in published literature, Section \ref{sec:log_transform} provides a quick discussion of the Logarithmic Transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous area.
Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
	to choose the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, section \ref{sec:discussion} discusses the findings and presents concluding remarks.

\section{Related Work in Literature}
\label{sec:lit_review}

%Addressing this issue, 
There has been a few published articles dedicated to the topic of evaluating speckle filters.
However, our survey of SAR speckle filtering research indicates 
	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
In the rest of this introductory section, we briefly review published work 
	related to the topic of evaluating SAR speckle filters.

It is customary to divide the evaluation of speckle filters into two scenarios:
	homogeneous area and heterogeneous scenes.
In homogeneous area,
	speckle filters are expected to estimate with negligible radiometric bias.
Thus evaluating speckle filters on homogeneous area have traditionally been focused on evaluating the variation of the estimators' output.
In contrast, the methodologies to evaluate speckle filters in heterogeneous area are much more complex, probably due to the following difficulties.
The first difficulty is to find out an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is to come up with a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
In this subsection, various published work in evaluating SAR speckle filters are critically reviewed.

The general requirement for speckle filters is that its application should allow easier detection and classification of the imaging features.
As shown in the subsequent section, 
	one can choose to work in original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
In this log-transformed domain, the requirement of speckle filtering can be broken down into two smaller requirements.
On the one hand, the filters should preserve the underlying radiometric signal (i.e. radiometric preservation), while on the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression).
These smaller requirements can be intepreted and evaluated by evaluating, also in log-transformed domain, the output's bias and variance error.
The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirement of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

For homogeneous scenes, 
	where the underlying radiometry is assumed to be unchanged, 
	the filtered results can be statistically considered as samples of 
		a single but complex stochastic process.
%Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
From the logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can then be judged using the familiar bias and variance evaluation.
	%are expected to estimate with no radiometry bias. 
%The best filters achieve maximum speckle suppression power in such areas.

A metric that can be used to detect radiomtric distortion is the ratio between the noisy pixel to the estimated value $r = X_{org}/X_{est}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
In the log-transformed domain, the equivalent index would, of course, be a simple substraction.
In \cite{Shi_IGARSS_1994}, Shi et al found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we also observe that all of these standard filters not only can preserves the expected radiometric values, but in the log-transformed domain they also can preserve a few substractive and consistent measures of distance.

A few metrics have been used to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In section 3, it will be shown that, for homogeneous areas, ENL is related to variance in log-transformed domain.
The link is also consistent with other independent results concerning measures of homogeneity where, Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ to evaluate scene heterogeneity.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
In this paper we propose the use of variance to evaluate the noise suppression power of speckle filters.
Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
	which is a component of MSE evaluation, 
	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters in homogeneous area.

Real-life and practical images, however, are not homogeneous, 
	and there are a few associated difficulties in evaluating speckle filters in heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scene is to find the bases for comparision. 
It is trivially easy to estimate the underlying radiometric co-efficient if an area is known to be homogeneous
However, without simulation or access to lab environment ground-truth, it is practically impossible to do so for real-life images (thus the need for speckle filters' estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
Under a multiplicative model, the ratio images is expected to comprise the noise being removed, (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluations, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
The ratio image then becomes a simple substraction image.
The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see section \ref{sec:practical_conjecture}).

Another way to evaluate speckle filters is by assessing the feature preservation characteristics of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied extract features; some that have been used are the Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} or edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, we have serious doubts about the precision of this methodology.
This is because feature extraction algorithms are only approximations 
	whose accuracy is 
		not only dependent upon the characteristics of the original image 
		but also heavily reliant on the inherent noise.
Unfortunately, speckle filters invariably alter the noise's characteristics.
Thus without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interprete the accuracy of its results.
%is just too imprecise for us.

Since SAR statistical models are quite well understood, 
	simulation experiments with known ground-truth can be employed 
		to evaluate speckle filters.
		%without the need to apply feature detection. 
In this paper, we also make use of a similar methodology discussed above with two important changes.
Firstly, our simulated experiments offer absolute ground-truth, serving as the base of comparisons.
Secondly, our threshold based feature extraction algorithm is extremely simple.
More importantly, the dependency between the algorithm's performance and the noise level is well established. 
This performance 
	can conveniently be visualised by plotting the Receiver Operating Characteristics Curve (ROC) 
	as well as objectively be quantified by measuring the Area Under this Curve (AUC). 
As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria then allow for the comparative evaluation of feature preservation capabilities of different speckle filters.

%There are two main ways that ground truths are used in evaluating speckle filters.
%A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. 
%Normally the image is large, with a number of different features and test conducted in once. 
%The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. 
%The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. 
%It is of course, also dependent upon the nature of the test image and noise embedded process employed.
%
%Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
%Since the structure is repeated many times, the combined results become more representative. Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
%The drawback is that only a single type of target can be tested per image. These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements too.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional level.
In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preservating underlying radiometric differences (such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

(TO REWRITE) Overall, we see many different methods and metrics used for evaluating speckle filters. However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. Wang \cite{Wang_2005_MIPR} has attempted to look at the problem: he proposed using fuzzy membership to weight opinions of an expert panel. Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and is still subjective in nature.

Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
%Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
%Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
%	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
%	where $E()$ denotes expectation operator.

Another attempt is to apply a universal mean squared error criteria into the context of SAR data. However since SAR data is heteroskedastic, the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. Others have suggest the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

In this paper, we propose the use of MSE in the homoskedastic log-transformed domain. This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean). We also show experimentally that this MSE measure is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability can be.

\section{Logarithmic Transformation}
\label{sec:log_transform}

In the first portion of this section,
    the SAR speckle model in the original domain is shown to be multiplicative and heteroskedastic.
Next the impacts of heteroskedasticity on speckle filtering is discussed.
Then logarithmic transformation is shown to convert original speckle data into an homoskedastic model, where the noise is not only additive, but also independent of the underlying radiometric signal.
From the consistent and additive noise in log-transformed domain,
    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and variance ($var(ln(I))$) are described.

\subsection{Original Heteroskedastic Model}

SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scaterring components, each reflecting from different and distributed elementary scaterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. These interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

\begin{equation}
\label{eqn:component_signal_pdf}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.

\begin{IEEEeqnarray}{l l l}
pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -{A^2}/{\sigma^2} \right) }\\
pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -{I}/{\sigma^2} \right) }
\end{IEEEeqnarray}

From a statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to $\sigma$ unit distributions given below:

\begin{IEEEeqnarray}{l l l}
pdf(A_1) &=& 2A_1 e^{ \left( A_1^2 \right) }\\
pdf(I_1) &=& e^{ \left( -I_1 \right) }
\end{IEEEeqnarray}

It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
These relationships evidently manifest a mutiplicative nature. 
In fact, this condition has long been noted, but from different perspectives, in various SAR models including multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. Consequently, the population expected mean and variance of the four distributions are given in table \ref{tbl:orginal_sar_avg_var}

\begin{table}[!h]
\caption{Both the mean and the variance of noisy SAR image data are related to the scale factor $\sigma$.}
\label{tbl:orginal_sar_avg_var}
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(A_1) = { \sqrt{\pi}}/{2}$ & $var(A_1) = {(4-\pi)}/{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = {\sigma \cdot \sqrt{\pi}}/{2} $ & $var(A) = \sigma^2 \cdot {(4-\pi)}/{4} $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline
\end{tabular}

%\end{center}
\end{table}

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean. 
In the context of speckle filtering, table \ref{tbl:orginal_sar_avg_var} indicates the vicious circle: estimating variance is equal to estimating the mean and is equivalent to the main problem, ie. estimating the unknown parameter $\sigma$.

The formulas above has long been noted. In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al has noted the ratio of expected standard deviation to mean is a constant in both cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.

\subsection{ The effects of Heteroskedasticity on Speckle Filters }

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: 
Eventhough, the statistical model within individual resolution cell is well established, the applicability of its models is restricted to homogenous areas. 
Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial varition also gives rise to the heteroskedasticity phenomena. 
Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying back-scattering coefficient $(\sigma)$. 
It is believed that this heteroskedasticity give rise to serious negative impacts at various stages of speckle-filtering.

In modelling, heteroskedasticity has direct consequences to the central question of homogeneity or heterogeneity. 
In normal images, the contrast or variance among neighboring pixels is often used to measure homogeneity. 
Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent to estimating $\sigma$).
%The fact give rise to the vicious circle in SAR speckle filtering.

Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator. 
Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, together with the normal Mean Squared Error evaluation criteria in serious doubt. 
If the variance is known \textit{a priori}, it has been proven, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. 
The caveat however is that in SAR speckle filtering, variance is not known a priori. 
And eventhough variance can be estimated from observable values, as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.

Case in point can be illustrated in the recently published improved sigma filter\cite{Lee_TGRS_2009}. 
The technique determines outlying points as being too far away from the standard deviation. 
However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required and used. 
It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.

Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. 
Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. 
Each of these tasks require good similarity or discriminant functions. 
Foundational to these is the need of a consistent measures of distance. 
Unfortunately, by definition heteroskedasticity leads to inconsistent measures of distance. 
This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods are believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods for SAR classification to underperform.

\subsection{ Homoskedastic effect of Logarithmic Transformation }

In this paper, we propose using base-2 logarithmic transformtion of SAR orignal random variables. Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet it maintains the ability to transform heterskedactic speckle into a homoskedastic relationship. Thus the original variables become:

\begin{IEEEeqnarray}{l l l l l}
L_{1}^{A} &=& \log_2(A_1) &=& L_{1}^{I} / 2 \\
L_A &=& \log_2(A) 	&=& L_{1}^{A} + \log_2\sigma \\
L_{1}^{I} &=& \log_2(I_1) &=& 2 L_{1}^{A} \\
L_I &=& \log_2(I) 	&=& L_{1}^{I} + 2 \log_2\sigma
\end{IEEEeqnarray}

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as follows:

\begin{IEEEeqnarray}{l l l}
pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left[ 2 L_{1}^{A} - 2^{2 L_{1}^{A}} \right]} \\
pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
pdf(L_{1}^{I}) &=& 2^{\left[ L_{1}^{I} - 2^{L_{1}^{I}} \right]} \\
pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} 
\end{IEEEeqnarray}

Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$

\begin{table}[!h]
\caption{ Mean and Variance of Log Transformed SAR values. }
\label{tbl:sar_log_domain_avg_var}
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}

%\end{center}
\end{table}

The equations above also highlight the relationships among random variables in the log-transformed domain. 
Two conclusions become evident from these formula. 
Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation is clearly manifested. 
Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  defined as the independence of the conditional expected variance on the conditional expectation of the mean.

This result is consistence with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}.  
The main difference would be the use of base-2 logarithm which is prefered here for faster computation.

Table \ref{tbl:sar_variables_properties} summarize the discussion so far. 
It can be seen that while the original data, especially intensity values, should be prefered for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast. 
Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (inculding wavelets) and computational (including artificial neural network) techniques into SAR data.

\begin{table*}[t]
\normalsize
%\hrulefill

%\begin{center}
\centering
\caption{ The properties of observable SAR random variables }
\label{tbl:sar_variables_properties}

\begin{tabular}{|l|l|l|l|}
\hline
 RV & Relationships  & Variance (skedasticity) & Mean (biasness) \\
\hline
$A$ & $A=\sigma A_1 $ & Heteroskedastic $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ & Unbiased $avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ \\
$I$ & $I=A^2=\sigma^2 I_1 $ & Heteroskedastic $ var(I) = \sigma^4$ & Unbiased $avg(I) = \sigma^2 $\\
$L_A$ & $L_A=\ln(A)=L_{1^A} + \log_2{\sigma}$ & Homoskedastic $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ \\
$L_I$ & $L_I=\ln(I)=L_{1^I} + 2 \log_2{\sigma}$  & Homoskedastic $var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ \\
\hline
\end{tabular}

%\end{center}
\end{table*}

In order to explore this experimentally, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
The excellent agreement is self-evident in the graph which confirmed the log-transformed model. 
In fact, this modelling has been used successful in explaining speckle phenomena, also verified through scientific experiments \cite{Ulaby_TGRS_1988}.

\begin{figure}[h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/amplitude_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/intensity_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

\subsection{Consistent measures of distance in Log-Transformed domain}

The consistent sense is explored and illustrated in this section from two different perspectives. 
First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}. Consider the random variable deviation defined as the distance between an observable sample and its expected value:

\begin{IEEEeqnarray}{l l l l l}
D_A &=& A &-& avg(A) \\
D_I &=& I &-& avg(I) \\
D_{L^A} &=& L_A &-& avg(L_A) = log_2{ \left( \frac{A}{avg(A)} \right)}\\
D_{L^I} &=& L_I &-& avg(L_I) = log_2{ \left( \frac{I}{avg(I)} \right)}
\end{IEEEeqnarray}

Noting the results from previous section, the pdf for these variable can be trivially given as

\begin{IEEEeqnarray}{l l l}
pdf(D_A) &=& 2 \cdot \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)}{\sigma^2}e^{ \left[ - \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)^2}{\sigma^2}   \right] } \\
pdf(D_I) &=& \frac{1}{\sigma^2}e^{\left[ -\left( D_I + \sigma^2 \right) / \sigma^2 \right] } \\
pdf(D_{L^A}) &=& 2 \cdot 2^{\left[ \left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
pdf(D_{L^I}) &=& 2^{\left[ \left( D_{L^I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} \right]}
\end{IEEEeqnarray}

It is evident from the equations that these distributions are dependent on $\sigma$ in the original SAR data but are independent of it in the log-transformed domain.

From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider the random variable defined as the contrast between two measured samples, in the log-transformed domain:

\begin{IEEEeqnarray}{l l l l l}
C_{L^A} &=& L_1^{A_\sigma} &-& L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }\\
C_{L^I} &=& L_1^{I_\sigma} &-& L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
\end{IEEEeqnarray}

Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is consistent in the log-domain but inconsistent in the original domain. The pdf of these variables can be given as:

\begin{IEEEeqnarray}{l l l}
pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{1+2^{\left( C_{L^I} \right)}} \ln2 
\end{IEEEeqnarray}

Figure \ref{fig:residual_as_noise} illustrates this, showing excellent agreement between the analytical pdf and observable histogram of deviation and contrast of the same area in a log-transformed intensity RADARSAT-2 image. 
Distance is calculated as the difference between each value point and the average value of that region, while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.

\begin{figure}[h!]
\centering
%\begin{tabular}{c}
	\subfloat[dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_dispersion_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill
	\subfloat[contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_contrast_histogram.eps} 	
		 \label{intensity}
	}
%\end{tabular}
\caption{Observed and modelled pdf of deviation and contrast in homogenous log-transformed intensity images.}
\label{fig:residual_as_noise}
\end{figure}

Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the measure of observable deviation in original SAR data differs, ie. is inconsistent, across different homogenous areas. 
The observable deviation in the log-transformed domain however is consistently the same across different homogenous areas. 
One possible benefit is that should the sigma filter\cite{Lee_TGRS_2009} be designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.

\subsection{Sampling distribution of Variance in Log-Transformed domain}

From the previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as

\begin{eqnarray}
pdf(V_{L^I}) &=& 
	\ln2 \frac{ 2^{\sqrt{V_{L^I}}}}{\sqrt{V_{L^I}} \left( 1+2^{\sqrt{V_{L^I}}} \right)^2} \\
pdf(V_{L^A}) &=&
	\ln2 \frac{2^{\sqrt{4V_{L^A}}}}{\sqrt{4V_{L^A}} \left( 1+2^{\sqrt{4V_{L^A}}} \right)^2} 
\end{eqnarray}

It could be seen that, in the log-transformed domain, not only the expected mean of observable variance is constant, the sampling distribution of this random variable is independent of $\sigma$. 
We have seen this analytically for two sample variances. 
For larger number of samples, Monte-Carlo simulation is used to visualise the PDF of sample variances.

In summary, a few measures of distance is shown to be consistent, which agrees with the consistent sense of variance / deviation and homoskedasticity.
The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use as illustrated in our kMLE speckle filter.
The consistent sense of contrast can be used to test if the any pair of measured data point belong to the same class of scatterrer, 
	and it may also explain why in original SAR domain the ratio based detector / classifier is prefered to the differential measures, which is not consistent. 
An example application of this is described in our fMLE speckle filter.
The consistent sense of contrast also gives rise to the consistent measure of variance, which can be used to test if a group of pixel can form an homogenous area.
This is applied in a clustering algorithm described in \cite{Le_2010_ACRS}.

\section{Evaluating Speckle Filters on Homogeneous Areas}
\label{sec:eval_homo}

In this section, the methodology to evaluate speckle filters on homogeneous area in log-transformed domain is illustrated.
Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring its speckle suppression power using the ENL index.
Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
The following subsection gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.

\subsection{ Speckle Filtering Process: General Schema and Evaluation Metrics }

Before we begin, Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of the various experiments presented in this paper.
The ``SAR Processor'' block indicates either 
	the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is captured in $\tilde{X}$ or
	the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.

The ``SAR Speckle Filter'' block indicates the speckle filtering process, 
	which takes in the noisy speckled SAR data $\tilde{X}$ 
		and outputs $\hat{X}$ as a better estimate of the ground-truth (i.e. $X$).
The speckle filters used in this paper are: 
	boxcar filter, Lee filter, Kuan filter, Frost filter, Gamma Map filter and PDE filter.
Evidently when there is no filter applied then $\hat{X}_{none} = \tilde{X}$.

\begin{figure}
 \centering
 \epsfxsize=3in
 \epsfysize=1.5in
 \epsffile{src/simulation_schema.eps} 	
\caption{SAR simulation, processing and filtering schema}
\label{fig:simul_process_filter_schema}
\end{figure}

Different metrics to evaluate speckle filters, that are investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
When ground-truth is available, 
	either in simulated experiments or in homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated values and its true values.
In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be think of as the level of noise being removed by speckle filtering process.
While as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) is normally known or can be estimated reasonably well.
Thus the base MSE level which also a measure of the speckle noise level can also be estimated.
Naturally, the speckle filter should remove as much noise as possible, 
	while it also should not remove more variations than that caused by the speckle noise.
%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base

\begin{subequations} \label{eqn:eval_metric}
\begin{align}
MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
\end{align}
\end{subequations}
%\begin{eqnarray}
%MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
%MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
%MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
%MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
%\end{eqnarray}

\subsection{ Estimating ENL from MSE index in homogeneous areas }

In this subsection, we show that the variance in log-transformed domain is equationally related to the universal ENL index. 
Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
Assuming the filters achieves negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
	then the MSE evaluation reduces to variance evaluation.
That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in log-transformed domain.

Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
%Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variable as: 
\begin{equation}
var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
\label{eqn:perf_index_theoretical}
\end{equation}

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
In fact, we could estimate:
\begin{equation}
  var(\hat{X}^L) = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}
Thus, the Equivalent Number of Look, i.e. L, can be estimated as:
\begin{equation}
L = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

To verify the above analysis an experiment is carried out.
In the experiment, a $512\times512$ homogeneous area is generated and corrupted with Single Look SAR-speckle PDF. 
Different multi-look processing filters are then applied to the patch. 
The observable variance in log-transformed domain is recorded and 
	the ENL is estimated from Equation \ref{eqn:enl_analytic} for each simulation.
We run the simulation multiple times and table \ref{tab:enl_in_log_domain} report the results in mean and standard deviation.
The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
	together with the analytical values from Eqn. \ref{eqn:perf_index_analytic}.
The experimental results evidently validate the analysis given above.
It also shows that: 
	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect, 
	since ENL is supposed to be an integer, its conclusions are unambigous.

\begin{table}
\centering
\begin{tabular}{r|c|c|c|r}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & ENL (Estimated) \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\end{table}

\subsection{Using log-variance to evaluate speckle filters}

Fig. \ref{fig:log_consistency_model} plots the histograms of homogenous SAR data over different radiometric values.
Both single-look simulated and multi-look processed/box-car filtered data is displayed.
Specifically the plots show that the log-transformed domain is consistent while the plots from the original domain are not.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Single Look (Intensity)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/orig_inconsistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi Look (Intensity)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/orig_inconsistency_boxcar.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Single-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_boxcar.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{The Inconsistency evident in the original SAR domain and the Emerged Consistency demonstrated in the log-transformed domain}
\label{fig:log_consistency_model}
\end{figure}

Fig. \ref{fig:log_consistency_filters} shows that the standard filters (Lee, Kuan, Frost and Gamma MAP) preserve this consistency in their filtered output. Intuitively, the boxcar filter is actually multi-look processing thus it also preserve the consistent property.
This consistency will also lead to the consistent sense of distance described earlier and is significant because it is the tell-tale sign of the consistent contrast and variance.
This ensures applicability of various target detection/classification algorithms which employ the statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Lee filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_lee.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_kuan.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_frost.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Gamma MAP filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_map.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Filtered results: consistency in log-transformed domain}
\label{fig:log_consistency_filters}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c|c|r|r|r}
Filter & Set & Log-Variance & ENL (Estimated) & Avg Intensity \\
\hline
none & 1 & 3.4149 (0.0003) & 1.1095 (5.8e-5) & 3.4795 (0.0029)\\
pde & 1 & 1.2674 (0.0014) & 2.1423 (0.0018) & 3.4806 (0.0029)\\
map & 1 & 1.2651 (0.0055) & 2.1454 (0.0072) & 3.1627 (0.0002)\\
lee & 1 & 0.4604 (0.0027) & 5.0206 (0.0268) & 3.4835 (0.0022)\\
kuan & 1 & 0.2979 (0.0024) & 7.4864 (0.0574) & 3.4748 (0.0054)\\
frost & 1 & 0.2852 (0.0012) & 7.7975 (0.0299) & 3.4799 (0.0027)\\
boxcar & 1 & 0.2513 (0.0011) & 8.7819 (0.0353) & 3.4799 (0.0027)\\
\hline
none & 2 & 3.4191 (0.0068) & 1.1088 (0.0012) & 9.4925 (0.0049)\\
pde & 2 & 1.6071 (0.0026) & 1.7952 (0.0021) & 9.4930 (0.0048)\\
map & 2 & 1.2646 (0.0023) & 2.1459 (0.0029) & 8.6091 (0.0162)\\
lee & 2 & 0.4653 (0.0026) & 4.9731 (0.0254) & 9.4936 (0.0080)\\
kuan & 2 & 0.2999 (0.0026) & 7.4391 (0.0602) & 9.4761 (0.0014)\\
frost & 2 & 0.2867 (0.0005) & 7.7595 (0.0128) & 9.4912 (0.0039)\\
boxcar & 2 & 0.2532 (0.0006) & 8.7203 (0.0193) & 9.4914 (0.0040)\\
\hline
none & 3 & 3.4203 (0.0187) & 1.1068 (0.0033) & 25.6234 (0.0389)\\
pde & 3 & 2.0353 (0.0021) & 1.5226 (0.0010) & 25.6236 (0.0389)\\
map & 3 & 1.2799 (0.0091) & 2.1263 (0.0116) & 23.2628 (0.0304)\\
lee & 3 & 0.4633 (2.4e-5) & 4.9926 (0.0002) & 25.6406 (0.0488)\\
kuan & 3 & 0.2964 (0.0010) & 7.5225 (0.0244) & 25.6112 (0.0226)\\
frost & 3 & 0.2862 (0.0008) & 7.7714 (0.0202) & 25.6263 (0.0409)\\
boxcar & 3 & 0.2529 (0.0005) & 8.7296 (0.0178) & 25.6261 (0.0407)
\end{tabular}
\caption{ Filters' Performance: Homogeneous Area }
\label{tab:homogeneous_performance_filters}
\end{table}

Table \ref{tab:homogeneous_performance_filters} gives a quantitative comparison among the filters.
It shows that the filters can all preserves the underlying radiometric values, while their speckle suppression power can be equivalently measured using either variance in the log-transformed domain, or the standard Equivalent Number of Look index.

\section{Evaluating Speckle Filters on Heterogenous Area}
\label{sec:eval_hetero}

For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
First, several test patterns is created to simulate and determine the performance of various speckle filters.
Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.

We believe that the qualitative requirement of speckle suppression can be quantified as the variance in log-transformed domain. 
The visual requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservations and speckle suppression.
These smaller requirements are equivalent to the bias and variance evaluation of statistical estimator.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC curve.
We show experimentally that the MSE inversely correlated with the AUC index, for all of the simulated patterns.

Since we expect the filters to be consistently behaved in the log-transformed domain, then as we repeat a pattern multiple times, the histograms of target and background areas can be obtained.
%They are expected to be consistent in log-transformed domain.
The target and background can then be seperated using a simple threshold based classification model.
We judge the separability of the two stochastic populations by the standard ROC, and the quantitative metric of Area Under the ROC Curve (AUC) can then be used as an evaluation metric.

The types of pattern created here are: point targets, line targets, edge targets and a heterogeneous scene. These test patterns could, of course, be included into a larger composite test image. However we would prefer to highlight the results separately for each individual area.
All patterns are limited to two class of ground-truth: background and target areas. We will follow the convention in the radar community where the target is signified by the brighter area of the image. Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Line: each line is 2 pixel wide, separated by 6 pixels background]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_line2.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Edge: each stripe is 4 pixel in width]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_edge.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Point: each point is a $2 \times 2$ squares spacing 4 pixels apart]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_point.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Checker board: the squares are 2 pixel wide each side]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_checker.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\centering
\caption{Example windows of ground truth patterns, each $32 \times 32$ pixels in size.}
\label{fig:hetero_patterns}
\end{figure}

Large patches of these patterns ($512 \times 512$) are first corrupted with single look noise, and then the filters are applied onto these noised images.
From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} show thats feature preservation can be evaluated by examining the separability of the two background and target populations.
We visualize the separability of the two histograms by plotting the standard Receiver Operating Curve (ROC) and we measure it by computing the Area Under this Curve (AUC) index.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Simulated Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.none.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filtered Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.kuan.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.none.fi.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Histograms: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.fi.png.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[ROC AUC: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.roc_auc.edge.none.fi.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[ROC AUC: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.roc_auc.edge.kuan.fi.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Target and Clutter Separability: ROC and AUC indices}
\label{fig:hetero_patterns_roc_auc}
\end{figure}

From a detailed analysis point of view, Fig. \ref{fig:hetero_patterns_mse} shows how the MSE is related to the histograms' capability to seperate.
In pre-filtered images, subfigures \ref{fig:hetero_patterns_mse}(c and d), there is no bias error.
Then the seperability of clutter and target populations depends only on the variance of the additive noise. This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) the better the separation capability can be.

In post-filtered images (subfigures \ref{fig:hetero_patterns_mse}(d and f), the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account bias error.
Sub fig. \ref{fig:hetero_patterns_mse}(d) show that the Kuan filter, and in fact all of the other filters (whose plots are not reproduced here), introduces a bias error.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are always over-estimated.
This is probably due to the entropy reduction effect of speckle filters, and apparently, assuming that the variances are fixed, the lesser these bias errors, the better the separation capability.

%Also the speckle suppression is related to the measured variance.
Thus we believe: the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
In fact, table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
We note that the MSE in inversely correlated to this separability index, suggesting that the lower MSE achivable by the filters would lead to better feature preservation in general.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Error Image: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.none.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Error Image: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Error Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Error Histograms: Kuan-filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
		 \label{intensity}
	}  %\\
%	\subfloat[MSE: Unfiltered]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/heterogenous_patterns.mse_histogram.edge.none.gt.png.eps} 	
%		 \label{amplitude}
%	} 
%	\hfill	
%	\subfloat[MSE: Kuan Filtered]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/heterogenous_patterns.mse_histogram.edge.kuan.gt.png.eps} 	
%		 \label{intensity}
%	} 
\end{tabular}
%}
\caption{MSE: Bias Error and Variance Error}
\label{fig:hetero_patterns_roc_auc}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & MSE (true)   & MSE (noise)      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline

%edge & unfiltered & 0.8492 & 4.1557 & 1.4e-33\\
%edge & frost & 0.8858 & 1.0889 & 5.8681\\
%edge & boxcar & 0.9121 & 0.9717 & 5.3482\\
%edge & map & 0.9168 & 2.0949 & 1.9044\\
%edge & kuan & 0.9423 & 0.8222 & 4.5087\\
%edge & lee & 0.9543 & 0.8278 & 3.3109\\
%\hline
%line2 & unfiltered & 0.8499 & 4.1306 & 1.7e-33\\
%line2 & frost & 0.8926 & 1.0901 & 5.8411\\
%line2 & map & 0.8945 & 2.0882 & 1.8861\\
%line2 & boxcar & 0.9181 & 0.9733 & 5.3236\\
%line2 & lee & 0.9421 & 0.8228 & 3.2832\\
%line2 & kuan & 0.9438 & 0.8058 & 4.4654\\
%\hline
%point & unfiltered & 0.8479 & 4.1142 & 1.9e-33\\
%point & map & 0.8616 & 1.7622 & 2.0999\\
%point & frost & 0.8991 & 0.6649 & 5.1823\\
%point & lee & 0.9105 & 0.6681 & 3.1121\\
%point & boxcar & 0.9369 & 0.5842 & 4.6936\\
%point & kuan & 0.9492 & 0.5192 & 3.9910\\
%\hline
%checker & unfiltered & 0.8502 & 4.1282 & 1.4e-33\\
%checker & frost & 0.7598 & 1.6317 & 6.6242\\
%checker & boxcar & 0.8110 & 1.4516 & 6.0471\\
%checker & kuan & 0.8736 & 1.1765 & 5.0167\\
%checker & map & 0.8842 & 2.5391 & 1.6571\\
%checker & lee & 0.9058 & 1.0927 & 3.4421\\
%\hline
\end{tabular}

\caption{Lower MSE suggest better feature detection, measured by the AUC index}
\label{tab:mse_auc_in_log_domain}
\end{table}

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & AUC - true MSE (p-value) & AUC - benchmark MSE (p-value) \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

\caption{The correlation between MSE and AUC measure of feature discrimination (inside the brackets are corresponding p-values)}
\label{tab:mse_auc_corr_coeff}
\end{table}

\section{Using MSE to find the most suitable speckle filter for practical SAR images}
\label{sec:practical_conjecture}

In this section our conjecture of using MSE in log-transformed domain to find the most suitable speckle filter for any given SAR images are described.
The experiments in the previous sections are repeated on SLC SAR images 
	which are simulated from given ground-truth aerial images. 
Experimental results are presented as empirical evidence supporting the conjecture.
The a heuristic rule is that 
	if the best filtered results are those with minimal MSE 
	then just by observing the residual MSE, 
	the observable measure of these results will also achieve 
		being the closest to the MSE of the inherent noise.
This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters in any captured SAR images, 
	where the ground-truth and hence true MSE is not available.
Besides using visual evaluation to validate the conjecture, 
	the full justification of this conjecture is outside the scope of this paper.

Real images however are more complex than the patterns illustrated above. 
We also apply the filters on simulated SAR images, built by adding Single Look Noise into various aerial images. 
Fig. \ref{fig:real_simulated_images} illustrates some of the images used for our experiments.

\begin{figure}
\begin{tabular}{c}
	\subfloat[A Rural Area in Vietnam]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/P1090360.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[A Suburb of Ha Noi]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/P1090253.eps} 	
		 \label{intensity}
	} %\\
%	\subfloat[NTU Campus]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/Aerialcampus.eps} 	
%		 \label{amplitude}
%	} 
%	\hfill	
%	\subfloat[Chu Thap Island of Vietnam]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/fiery.eps} 	
%		 \label{intensity}
%	} 
\end{tabular}
\caption{Ground Truth Images for simulation}
\label{fig:real_simulated_images}
\end{figure}

With the use of MSE being validated from previous experiments, 
	the most suitable filter can be considered as the one with the lowest true MSE.
Table \ref{tab:mse_true_noise_log_domain} shows that among the various filters used, 
	the most suitable filter are also the filter that 
		have the its observable residual MSE value being closest to the noise MSE (4.1167 in our case).
We validate the idea by qualititative evaluation, an example of which is presented in Fig. \ref{fig:real_simulated_image_results}.
The same conclusion can be found in our experiments with more images, which cannot be shown here due to space limitation.

\begin{table}
\centering
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & MSE (true)   & MSE (noise)      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
vietnam rural	& none		& 4.1174	& 3.9e-35\\
vietnam rural	& pde			& 3.8022	& 0.0368\\
vietnam rural	& lee			& 0.4984	& 3.2555\\
vietnam rural	& frost		& 0.3490	& 4.6856\\
vietnam rural	& kuan		& 0.3396	& 3.6877\\
vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
hanoi suburb	& none		& 4.1321	& 4.1e-35\\
hanoi suburb	& pde			& 3.8004	& 0.0391\\
hanoi suburb	& lee			& 0.5261	& 3.2598\\
hanoi suburb	& frost		& 0.3811	& 4.7427\\
hanoi suburb	& kuan		& 0.3619	& 3.7270\\
hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}

\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
\label{tab:mse_true_noise_log_domain}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[Simulated GrayScale Image (ground-truth)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Unfiltered Noisy Image (true MSE = 4.1174)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[PDE Result (true MSE = 3.8022, residual MSE = 0.0073)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Lee Result (true MSE = 0.4984, residual MSE = 3.25553)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Result (true MSE = 0.3490, residual MSE = 4.6856)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Result (true MSE = 0.3107, residual MSE = 4.2328)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Simulated Real Images: Qualititative Validation}
\label{fig:real_simulated_image_results}
\end{center}
\end{figure}
%\end{figure*}

In real SAR captured images, the radiometric ground-truth normally is not available.
The most common way to evaluate speckle filters then is by qualitative visual evaluation.
A more analytical method is to investigate the ratio images between the filtered output and the noisy input images.
Since logarithmic transformation convert these ratio into substractive residual
	, which are consistent, residual analysis can be used to analyse and evaluate the performance of speckle filters.
To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig. \ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is extremely subjective.

Our qualititative conclusion is that
	a. it is apparently easier to notice the ``visible structure'' being removed in the residual noise pictures than the ratio mages, and
	b. even so, the above conclusion is at best quite subjective.
Thus to compare the filters against each other, 
	quantitative measures are preferred.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Original Patch]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Filtered Result]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.boxcar.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Ratio: Filtered / Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.ratio2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Ratio: Original / Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.ratio1.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[Log Residual: Filtered - Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.residual2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Log Residual: Original - Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.residual1.eps} 	
		 \label{intensity}
	} 
\end{tabular}
\caption{Error Images: Ratio vs. Residual}
\label{fig:real_image_ratio_vs_residual}
\end{figure}

Table \ref{tab:mse_in_real_image} tabulate the computed MSE of the ``removed'' additive noise.
Apparently all filters still left some noise ``unremoved'', in which case, the higher removed noise MSE would probably suggest a more suitable filter.
Fig. \ref{fig:real_image_results} qualitatively confirmed our evaluation.

\begin{table}
\centering
\begin{tabular}{c|r}
filter & MSE (noise)\\
\hline
pde & 0.2583\\
map & 2.6936\\
kuan & 3.3924\\
lee & 3.4172\\
boxcar & 3.6918\\
frost & 4.1191\\
\hline
SLC unfiltered MSE & 4.1167  
\end{tabular}
\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
\label{tab:mse_in_real_image}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[PDE Filter: MSE (noise) = 0.2583]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.pde.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[MAP Filter: MSE (noise) = 2.6936]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.map.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Lee Filter: MSE (noise) = 3.4172]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.lee.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Frost Filter: MSE (noise) = 4.1191]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.frost.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Real Images: Visual Validation}
\label{fig:real_image_results}
\end{center}
\end{figure}
%\end{figure*}

\section{Discussion and Conclusion}
\label{sec:discussion}
\subsection{Discussion}

Although it is widely known that log transformation transform multiplicative SAR speckle into additive noise, 
	one should note that the noise is not Gaussian.
In fact, figures presented in previous sections show that 
	they are not even centered around the origin. 
This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not work very well in practice.
To counter this, the use of maximum likelihood estimation instead of simple averaging is suggested \cite{Le_2011_ACRS}. 
Interestingly, averaging is also the MLE operator in the SAR's original domain.

%It is interesting to note that all of the standard filters' outputs exhibit consistent plots of histogram in the log-transformed domain, suggesting a consistent sense of distance. 
Log tranformation also brings about a few consistent measures of dissimilarity.
These consistency can be found not only in single-look or multi-look SAR data, 
	but can also be found in filtered data of various ``standard'' speckle filters.
This is significant probably because it ensures applicability of various target detection/classification algorithms
	, which exploits these consitent statistical properties, 
	into not only pre-filtered data but also post-filtered data as well.
%There are numerous

This consistent measures of distance in log-transformed domain could probably have implications beyond speckle filtering.
For example, in the subsequent tasks of designing target detector or classifier design, 
	it is normally desirable to engineer the solution to not only work on single-look or multi-look SAR data,
	but also be applicable on post-filtered data.
In such cases, these consistent measures of distance in log-transformed domain could provide a sound theoretical basis.
In fact, a number of already proposed solutions appears to make use of this feature. 
%(cite here some SAR classification papers)
An example is the ratio based discriminator in the original domain.
Looking backwards, in designing new speckle filters, by ensuring that the filtered output preserves this consistent property,
	the new speckle filters would be eligible to be used as a pre-processing steps for availble classifiers / detector.

Of course, there are other speckle filters that do not preserve such consistency (e.g. the pde filter \cite{You_TIP_2000}).
One could argue that it would not be fair to the judge such filters using the MSE criteria, 
	which is probably favors the ``standard'' filters.
While we respect any other criteria that are used, we wish to reiterate two points.
First, our MSE criteria is closely related to the basic ENL criteria.
And our experimental results indicates that the ENL measures for such filter (i.e. the pde filter) differ depending on the radiometric values.
Second, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
The MSE criteria is shown to be related to feature preservation requirements.
Thus it is relevant towards subsequent target detection / classification processing, 
	which is believed to be a pretty common subsequent processing step.
For these two reasons, the MSE criteria is strongly advocated.

In the experiments above, speckle filters with a $3 \times 3$ sliding window were used, 
	eventhough we are aware that the normal window size used is much larger. 
The reasons for maintaining a small window in these tests is that 
	smaller-sized filters facilitate the use of smaller patterns without too much concern about crosstalk among adjacent targets.
Secondly, we want to focus on advocating the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
	and do not wish to advocate which filter is the ``best'' filter. 
In other words, we are mainly addressing the methodology to evaluate speckle filters, 
	and not directly addressing the issue of designing speckle filters.
However, interested filter designers however are invited to download our Matlab evaluation code online to evaluate their designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.

In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators (i.e. speckle filters).
%The use of simulation and modelling in speckle filtering research allows for faster simulation and evaluation of different underlying scenarios. 
The use of small and simple patterns allow detailed analysis can then be done repeatedly and reliably against the stochastic nature of SAR data.% on simulated small data sets without the need of a common real large image that is somehow representative. 
This helps the mapping of qualititative requirements for the speckle removal process into specific and quantitative requirements in the design of speckle filters.
Its use also provides an absolute ground-truth, a solid base for comparison results.

Its main drawback is that ground truth does not exist in real-captured SAR images.%, there is no ground-truth.
Thus the result extension towards real images is only analogical.
While the proposed rule is probably heuristics, 
	the experimental results presented in this paper is evidently and empirically valid,
	supporting the final conjecture.

We distinctively divided speckle filtering into two distinct scenarios, that of homogeneity and heterogeneity.
%In fact, we believe the situation is more fuzzy when it comes to classifying a given noisy captured SAR scene 
While perfect homogeneous ground truth can be defined, 
	different heterogenous patterns exhibits different levels of heterogeneity. 
Eventhough different measures have been proposed to evaluate scene heterogeneity level or to test homogeneity hypothesis, 
	for real captured images, where the absolute ground-truth is not available, 
	there does not appears to exist any certain way to assert a given image as being perfectly homogenous or absolutely heterogenous.
Thus while the distinction helps in clarifying the concepts, 
	it is probably a leaky abstraction.
%However, without ground trutth, there appears to not exist any certain way of classifying a given captured imagary scene as homogeneous or heterogenous. 
%In fact a few different measures have been proposed to evaluate scene homogeneity / heterogeneity.

%Similarly for 
The patterns used is chosen based on our exeriences and they may affects evaluation results. 
As different patterns results in different degree in the scale of scene homogeneity / heterogeneity, 
	and they also appears to affect the performance and ranking of each speckle filters.
One extreme case is that of perfect homogeneity, where boxcar filters would be the best performer,
	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that boxcar would actually lose out.
%Our work suggest that the performance of speckle filters is probably scene dependent, 
%	our conjecture is that it may depends on the level of scene homogeneity.
%The full justification of that, however is outside the scope of this paper.
%In fact, we do not know of any pattern that would be fair towards every possible filters.
%So the patterns should only serves as guide lines, and filter designers may not want to overly optimize their filter's performance on any single of these patterns.
%As doing so may make the filter lose out in other aspects.

%While the patterns may not be the primary evaluative criteria, we believe that the MSE measure in the log-transformed domain (particularly log-2 transformed domain) should receive serious considerations by future filter designers. Again, this is due to good reasons: that the Gauss Markov theorem is applicable in this domain (and not in the original domain). Thus, we believe an optimization for minimal MSE is likely to succeed in good real-world performance.

Readers may also find that the idea of matching the most suitable speckle filter with a given scene is a bit foreign.
In fact, one of our hope before carrying out this study is being able to find ``the single best'' speckle filter.
In reality, the numbers in our experimental results however do not unanimous advocate a single best filter. 
In hind-sight, this is probably not to be expected,
	given that the well known trade off where a power speckle-suppression filter (e.g. the boxcar filter) would likely to perform poorly in highly heterogeneous scenes, where radiometric preservation becomes more critical.
Such insight, when coupled with the fuzzy notion of homogeneity as being the special case of generalized heterogeneity, allow us to welcome the idea.

Our current scheme of finding the most suitable speckle filter requires the application of all the filters before a decision is made.
A probably better alternative is to predict the choice, thus escape such massive requirements of processing.
Such study, however, is outside the scope of this paper.

\subsection{Conclusion}

To summarize, speckle filters are generally evaluated using many different qualitative criteria.
To compare the filters against each other, however, a method is needed to quantify and measure these various qualitative requirements and results.
Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
With the Guass-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.

Our contribution is mainly centered around a few points. 
Firstly, we develop an equation to links the ENL index to the variance in the log-transformed domain, and illustrate it's efficacy for test images.
Secondly we show that MSE is inversely correlated to the AUC index for heterogenous areas, suggesting that the smaller MSE a filter can achieve, the better would be its ability to discriminate features.
Thirdly, our major practical contribution is to suggest an heuristic rules using the benchmark MSE to find the most suitable speckle filter for any given scene. 
In short, propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation scenarios, and suggest several test images that may be useful in this regard.

It should also be noted that a similar consistent sense of distance also exists in POLSAR data. 
Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.
%We also excited with the prospect of applying a wide variety of MSE-based or discriminator based algorithms into SAR and POLSAR values in log-transformed domain.

% references section
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,article}

\end{document}

### 2012-07-07 article_ivm.tex
comment: initalia push

%\documentclass[a4paper,10pt]{article}
\documentclass[journal]{IEEEtran}
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

\usepackage{cite} %for citations

 %this is for math typing (eg: cases)
\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{epsfig} %for figures

%\usepackage[caption=false]{caption}%for captions
\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures

%opening
\title{ 
	Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.
}

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
	Brian~Quang-Huy~Nguyen %
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen and Ian~McLoughlin are with School of Computer Engineering, 
Nanyang Technological University, Singapore,}% <-this % stops a space
%\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, April~2012}%
{ Le \MakeLowercase{\textit{et al.}}: SLC SAR speckle filtering using Homoskedastic effects of Logarithmic Transfomation }

\begin{document}

\maketitle

\begin{abstract}

Logarithmic transformation has potential to convert heteroskedastic SAR data into homoskedastic data sets, so that the universal Gauss-Markov theorem becomes applicable. This suggests that the familiar mean squared error (MSE) could become a useful evaluation criteria for statistical estimators (i.e. speckle filters) when operating in the logarithmic transformed domain.
In this paper, we show, through experiments and analysis, that the MSE criteria in the log-transformed domain can serve as a reliable performance indicator to evaluate performance of SAR speckle filters. Furthermore, we determine a mathematical relationship that, in homogeneous areas, links variance (and hence MSE) with the canonical Equivalent Number of Looks index.
For heterogenous areas, the usual ratio-based radiometric preservation criteria is shown to be related to the standard estimator bias evaluation in the log-transformed domain. 
Combined with the fact that variance is an effective measure of speckle suppression power, it is apparent that MSE can then serve as a usable performance criteria to evaluate feature preservation properties of SAR speckle filters.
Through experiment, analysis, and discussion, we show that lower MSE suggests better feature detection and classication ability in filtered images, an important requirement for speckle filters.
%, which can be visuallized using the standard Receiver Operating Curve (ROC) and quantified by measuring the Area Under this Curve (AUC).
%correlates with higher Area Under the ROC curve (AUC), a metric frequently used to evaluate separability of target and clutter statistical populations in feature detection / classification scenarios.

%Under the assumption of homogeneity, the sampling distribution of variance in log-transformed domain is constant and independent to the underlying back scattering coefficient. Then the observable sample variance in the log-transformed domain can be used as a measure of spatial non-homogeneity, thus statistical test on log-transformed variance can be formed to detect heterogeneity in a window of analysis. Using clustering algorithms, a novel speckle filtering algorithm is proposed to partition a non-homogenous area,  detected by the statistical test, into homogenous areas with estimated back scattering coefficient values.
\end{abstract}

\begin{IEEEkeywords}
Synthetic aperture radar, speckle-filtering, homoskedasticity, mean-squared-error
\end{IEEEkeywords}

%\textbf{Keywords: } Synthetic Aperture Radar, speckle-filtering, homoskedasticity

\IEEEpeerreviewmaketitle

\section{Introduction}

%SAR Speckle filter is an active area of research, 
The nature of SAR speckle is that it is stochastic over homogenous areas and heteroskedastic heterogenously. 
[IVM:what does this mean??]
In the general case of SAR processing, statistical models are used to derive the underlying back-scattering coefficient ($\sigma$) from measured data. Then speckle filters are, by and large, estimators that attempt to determine the unknown coefficient from observable SAR data. 
SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. This means that the stages in this statistical framework consist of statistical modelling, estimator development and evaluating of the performance of estimators.

Such estimators are typically evaluated based on the bias and variance properties of their estimates, with lower bias and variance indicating better performance [IVM: check this addition of mine is true??]. This evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. Also, due to the stochastic nature of the simulation process, statistical summaries of repeated simulating experiments are normally preferred to single-run results.

%SAR speckle filters have been put within the statistical estimation framework (cite Touzi)
A survey of SAR speckle filter research, however, indicates a different picture from the standard practice of the statistical framework, specifically in the stage of performance evaluation. Due to the multiplicative nature of speckle noise, bias and variance evaluation may not be the most useful measures. Also the heteroskedastic nature of the data causes the common mean-squared-error evaluation to be inapplicable without some adaptation. In fact, a survey of relevant literature fails to reveal a single universally agreed quantitative metric to evaluate speckle filters.

The result of this is that each newly proposed speckle filter is likely to be published along with a new methodology of evaluating its own performance, and many papers lack any comparative basis beyond simple visual qualititave comparisions on a few image scenes. While such visual comparison is useful, as an evaluative methodology, it lacks objectivity. Other papers do present quantitative measurements, however the evaluation metrics used vary significantly from one paper to the next due to the lack of a standardized evaluation criteria.

Despite this, there have been a few articles published which are dedicated to the topic of evaluating speckle filters through a universal evaluation crieria. In these papers, the evaluation metrics and simulation procedures receive much more thorough treatment, however several different metrics exist to cater to the variety of image classes.

In this paper, we note that log-transformation convert multiplicative and heteroskedastic SAR data into a more familiar additive and homoskedastic domain and thus we propose the use of MSE in the log-transformed domain as a single unifying evaluation criteria across different scenarios.

\subsection{Related Work in Literature}

It is customary to devide the evaluation of speckle filters into two scenarios of homogeneous and heterogeneous areas.
In homogeneous areas, where the underlying radiometry is assumed to be unchanged, the filters are expected to estimate with no radiometry bias. The best filters achieve maximum speckle suppression power in such areas.

To evaluate estimation bias, the normal metric used is Radiometry Loss index

\begin{equation}
R_{loss} = 10 log_{10} \left\{\frac{X_f}{E(X)} \right\}
\end{equation}

In the log-transformed domain, the equivalent index would, of course, be a simple substraction.
Shi (1994) found that all of the standard filters (boxcar, Lee, Kuan, Frost, MAP) can achieve negligible bias. In this paper, we also observe that all of these standard filters can not only preserves the expected radiometric values, they also preserve a consistent sense of distance (which we will describe later) in the log-transformed domain.

A few metrics have been used to evaluate speckle suppression power.
The most common one is probably the Equivalent Number of Looks index 
\begin{equation}
ENL=avg(I)^2/var(I)
\end{equation}

that was proposed by Lee (cite).
Another metric is the ratio of mean to standard deviation, $R=std(I)/avg(I)$ (cite Gagnon)
%Lopes proposed the variation coefficient $C_v=var(I)/avg(I)$, which suppose to measure the scene's homogeneity (cite Lopes TGRS). 
Since log-transformation converts multiplcative and heteroskedastic SAR data into additive and homoskedastic models, we suggest that the variance in the log-transformed domain can be used to evaluate the noise suppression power of speckle filters.

In fact, Solbo used standard deviation in the log-transformed domain to measure homogeneity. Extending this, we will show that for homogeneous areas, ENL is related to this variance.

However real-life and practical images are not homogeneous, and there are many proposed methods of evaluating speckle filters in such areas. It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
Under conditions of heterogeneity, even the standard speckle filters will introduce radiometric loss, normally at local or regional level.

In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preservating underlying radiometric differences (such as causing excessive blurring), and vice versa. One can relatively easily satisfy one of these criteria, but not easily satisfy both.

So the first difficulty in evaluating speckle filters for heterogeneous scene is to find one or more bases for comparision. It is trivially easy to estimate the underlying radiometric co-efficient if an area is known to be homogeneous, it is however virtually impossible to do so without simulation or access to accurate ground-truth for real-life images.

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, which is the ratio between the orignal speckled image and the filtered image (cite). Under a multiplicative model, the ratio images is expected to comprise the noise being removed, (i.e. it should be completely random). Being random, this should display as little ``visible'' structure as possible. Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
When displaying such images, ratios that are smaller than unity are much harder to distinguish than those that are bigger (cite Merdios), meaning that a purely visual analysis may be insufficient.

We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
The ratio image then becomes a simple substraction image.
The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and view.

Another way to evaluate speckle filters is by assessing the feature preservation characteristics of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied extract features; some that have been used are the Hough Transform (Merdios), Sobel edge detector (cite) or edge map (Frost).
While significant effort has been spent on these evaluations, we believe that the methodology is overly imprecise because feature extraction algorithms are thesleves only approximations whose accuracy is dependent upon noise, and heavily dependent upon the characteristics of the original image.
Thus without a clear understanding of these dependencies, and how they relate to the characteristics of the speckle filter under evaluation, one may question the effectiveness, repeatibility and accuracy of such an approach. 
%Note that also, using feature extraction algorithms to evaluate speckle filters, which invariably suppress the same noise, leave serious questions on how to interprete those quantitative measurement results.
%is just too imprecise for us.

Since SAR statistical models are quite well understood, the use of simulation experiments with known ground-truth offers a reasonably good approach without the need to apply feature detection. However we also propose the use of extremely simple feature extraction algorithms (i.e. a simple threshold based classifier) for which any dependency between its performance and noise can be (or already has been) very well established. The performance dependency can be sufficiently captured by knowledge of the Receiver [IVM: Operating??] Characteristics Curve (ROC) and the Area Under the curve (AUC). The can then enable the comparative evaluation of feature preservation capabilities of different speckle filters.

There are two main ways that ground truths are used in evaluating speckle filters.
A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. Normally the image is large, with a number of different features and test conducted in once. The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. It is of course, also dependent upon the nature of the test image and noise embedded process employed.

%IVM The methodology could also be applicable in log-transformed domain, however, as the evaluation methodology is the same, we prefer to apply the technique on investigating the residual image in log-transformed domain on real-life image instead.

Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
Since the structure is repeated many times, the combined results become more representative. Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
The drawback is that only a single type of target can be tested per image. These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements too. The most common image processing method to detect a target from its background is to compute their differences in intensity or amplitude domain. However since SAR noise is multiplicative, this difference is not only dependent on the noise level but also on the amplitude level of the signal itself.
Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
	where $E()$ denotes expectation operator.

Lopes also proposed the variation co-efficient index $C_v = var(I)/avg(I)$ to evaluate speckle filters.
However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.

Since we expect the filters to be consistently behaved in the log-transformed domain, then as we repeat a pattern multiple times, the histograms of target and background areas can be obtained.

%They are expected to be consistent in log-transformed domain.
The target and background can then be seperated using a simple threshold based classification model.
We judge the separability of the two stochastic populations by the standard ROC, and the quantitative metric of Area Under the ROC Curve (AUC) can then be used as an evaluation metric.

Overall, we see many different methods and metrics used for evaluating speckle filters. However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. Wang has attempted to look at the problem: he proposed using fuzzy membership to weight opinions of an expert panel. Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and is still subjective in nature.

Another attempt is to apply a universal mean squared error criteria into the context of SAR data. However since SAR data is heteroskedastic, the use of MSE is not straightforward. Thus Gagnon suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. Others have suggest the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

In this paper, we propose the use of MSE in the homoskedastic log-transformed domain. This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean). We also show experimentally that this MSE measure is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability can be.

To explore this concept, the rest of this paper is structured as follows.
Section 2 will provide a brief discussion of Log Transformation, followed in Section 3 by the use of MSE in the log-transformed domain to evaluate different filter's speckle suppression power in homogeneous area.
Section 4 will illustrate the use of the same MSE to evaluate different filters' performance in heterogeneous area, while Section 5 will analyse these results and provide concluding remarks.

\section{Logarithmic Transformation}

%\section{Logarithmic Transformation of SAR Single look data}

%The nature of SAR speckle is stochastics over homogenous areas and heteroskedastic heterogenously. Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affect the distribution of measured SAR data. Speckle filtering, by and large, are estimators attempting to the unknown coefficient from observable SAR signal $(A)$.

%SAR speckle-filtering can be and has been positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. The statistical framework attempts to estimate unknown statistical parameters from observed data. The stages consist of statistical modelling, estimator development and evaluating of the performance of estimators. Estimators' are evaluated based on the bias and variance properties of their estimates. The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.

%\section{SAR speckle statistic model}

%Useful, robust estimators require un-assuming models. This section will describe our model for speckle filtering. The first part will explain the heteroskedastic nature of original amplitude and intensity SAR data. In extending the original model to log-transformed domain, care has been taken to rely solely on rigorous mathematical and statistical principles.

In this section, we will first discuss the original SAR domain where the noise is primarily multiplicative and heteroskedastic.
Next we will explore log transformation to convert the data into additive and homoskedastic model, where the noise is not only additive but also \textit{independent of the underlying radiometric signal}.
From the consistent and additive noise in log-transformed domain (i.e. given the radiometric value is known, the plots of $ln(I)$ would be fixed), we describe the consistent sense of dispersion and contrast (i.e. the plots of $ln(I)-ln(avg(I))$ and $ln(I_1)-ln(I_2)$ are fixed assuming an underlying homogeneous area with constant radiometric level, regardless of its specific value).
%Note: include the simple equation $ln(I)-ln(avg(I)) = ln(I/avg(I))$ as this provides the cue for later POLSAR paper $ln(det(C)/avg(det(C)))$.

\subsection{Original Heteroskedastic Model}

SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components, each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. These interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scatterer and its response.

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

\begin{equation}
\label{eqn:component_signal_pdf}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.

\begin{IEEEeqnarray}{l l l}
pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -{A^2}/{\sigma^2} \right) }\\
pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -{I}/{\sigma^2} \right) }
\end{IEEEeqnarray}

From a statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to $\sigma$, unit distributions given below:

\begin{IEEEeqnarray}{l l l}
pdf(A_1) &=& 2A_1 e^{ \left( A_1^2 \right) }\\
pdf(I_1) &=& e^{ \left( -I_1 \right) }
\end{IEEEeqnarray}

It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
These relationships evidently manifest a mutiplicative nature. 
%IVMremoved the comment from this:
In fact, this condition has long been noted, but from a different perspective, in various SAR models including the multiplicative model (cite JS Lee) and product model \cite{Jakeman_1980_JPhysAMathGen}.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. Consequently, the expected population mean and variance of the four distributions are given in table \ref{tbl:orginal_sar_avg_var}

\begin{table}[!h]
\caption{Both the mean and the variance of noisy SAR image data are related to the scale factor $\sigma$.}
\label{tbl:orginal_sar_avg_var}
\normalsize
\centering
%\begin{center}
\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
% $avg(A_1) = \frac{ \sqrt{\pi}}{2}$ & $var(A_1) = \frac{(4-\pi)}{4}$ \\
% $avg(I_1) = 1$ & $var(I_1) = 1$ \\
% $avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ & $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ \\
% $avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
%%IVM: I changed some \frac to / so that they fit better on one line:
$avg(A_1) = { \sqrt{\pi}}/{2}$ & $var(A_1) = {(4-\pi)}/{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = {\sqrt{\pi}}/{2} \cdot \sigma $ & $var(A) = {(4-\pi)}/{4} \cdot \sigma^2 $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline
\end{tabular}
%\end{center}
\end{table}

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean. In the context of speckle filtering, table \ref{tbl:orginal_sar_avg_var} indicates the vicious circle: estimating variance is equal to estimating the mean and is equivalent to the main problem, ie. estimating the unknown parameter $\sigma$.

%IVMuncommented this:
The relationship above has, of course, long been noted. In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al. had noted that the ratio of expected standard deviation to mean is a constant in both cases (ie. $snr(A)=\sqrt{{4}/{\pi}-1}$ and $snr(I)=1$). Here, we offer an altrenative intepretation of that fact, leading to the proposed log-transform domain MSE measures later.

\subsection{ The effects of Heteroskedasticity on Speckle Filters }

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: eventhough, the statistical model within individual resolution cell is well established, the applicability of its models is restricted to homogenous areas. 
%Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial varition also gives rise to the heteroskedasticity phenomena. Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying back-scattering coefficient $(\sigma)$. It is believed that this heteroskedasticity give rise to serious negative impacts at various stages of speckle-filtering.

In modelling, heteroskedasticity has direct consequences to the central question of homogeneity or heterogeneity. In normal images, the contrast or variance among neighboring pixels is often used to measure homogeneity. Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent to estimating $\sigma$).

A case in point can be illustrated by the recently published improved sigma filter\cite{Lee_TGRS_2009}. The technique determines outlying points as those being too far away from the standard deviation. However, to estimate standard deviation, an estimator of mean is required and used. It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.

Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator since it directly violates the Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any na\"{i}ve Ordinary Least Square estimator to be in serious doubt \cite{Furno_1991_JStatCompSimul}. 
If the variance is known \textit{a priori}, it has been proven, (cite Aitken), that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} do make use of weighted mean estimators.

The caveat however is that in SAR speckle filtering, variance is not known \textit{a priori}. And although variance can be estimated from observable values, as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.

%Heteroskedastic makes it tricky to evaluate the performance of different estimators, even if quantitative experiments results is reported. In fact several quantitative simulated experiments has been carried out to compare the performance of different estimators\cite{Lee_TGRS_2009}. However only results of single experiment were reported. Due to the stochastic nature of the simulated experiement process, more experiments should be done to report the effectiveness, ie. variance, of each estimators' results.

Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. Each of these tasks require good similarity or discriminant functions. Foundational to these is the need of a consistence sense of distance. Unfortunately, by definition heteroskedasticity leads to inconsistent measures of distance. This inconsistent sense of distance coupled with the failure of the ordinary least square regression methods are believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods to underperform on the SAR classification task.

%In this paper, we aim to neutralize these various impacts. The paper is organized as follows. Section ??? will be devoted to discussion of the heteroskedastic phenomena in the original per-pixel SAR amplitude and intensity model. Logarithmic transformation is extended to the model and the homoskedastic property of it is asserted. Section ??? will discuss how sampling distribution of variance in the log-transformed domain can be used to model various degrees of homogeneity. Section ??? will presents a novel speckle filtering algorithm developed from heterogenous inference made possible by statistical testing of sample variances. Section ??? will present evaluation of our estimator both quantitatively through simulated experiments and qualitatively on real-life images.

\subsection{ Homoskedastic effect of Logarithmic Transformation }

In this paper, we propose using base-2 logarithmic transformtion of SAR orignal random variables. Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet it maintains the ability to transform heterskedactic speckle into a homoskedastic relationship. Thus the original variables become:

%%%%IVM: Hai, these look really strange?  Why have L_{1^A} instead of (for example), L_{1A} or L_{1}A??

\begin{IEEEeqnarray}{l l l l l}
L_{1^A} &=& \log_2(A_1) &=& L_{1^I} / 2 \\
L_A &=& \log_2(A) 	&=& L_{1^A} + \log_2\sigma \\
L_{1^I} &=& \log_2(I_1) \\
L_I &=& \log_2(I) 	&=& L_{1^I} + 2 \log_2\sigma
\end{IEEEeqnarray}

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as follows:

\begin{IEEEeqnarray}{l l l}
pdf(L_{1^A}) &=& 2 \cdot 2^{\left[ 2 L_{1^A} - 2^{2 L_{1^A}} \right]} \\
pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
pdf(L_{1^I}) &=& 2^{\left[ L_{1^I} - 2^{L_{1^I}} \right]} \\
pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} 
\end{IEEEeqnarray}

Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$

\begin{table}[!h]
\caption{ Mean and Variance of Log Transformed SAR values. }
\label{tbl:sar_log_domain_avg_var}
\normalsize
\centering
%\begin{center}
\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}
%\end{center}
\end{table}

The equations above also highlight the relationships among random variables in the log-transformed domain. 
Two conclusions become evident from these formula. 
Firstly, in the log-transformed domain, working on eithre amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation is clearly manifested. 
Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  defined as the independence of the conditional expected variance on the conditional expectation of the mean.

This result is consistence with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}.  
The main difference would be the use of base-2 logarithm which is prefered here for faster computation.

Table \ref{tbl:sar_variables_properties} summarize the discussion so far. It can be seen that while the original data, especially intensity values, should be prefered for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers a consistent sense of dispersion and contrast. Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (inculding wavelets) and computational (including artificial neural network) techniques into SAR data.

\begin{table*}[t]
\normalsize
%\hrulefill

%\begin{center}
\centering
\caption{ The properties of observable SAR random variables }
\label{tbl:sar_variables_properties}

\begin{tabular}{|l|l|l|l|}
\hline
 RV & Relationships  & Variance (skedasticity) & Mean (biasness) \\
\hline
$A$ & $A=\sigma A_1 $ & Heteroskedastic $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ & Unbiased $avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ \\
$I$ & $I=A^2=\sigma^2 I_1 $ & Heteroskedastic $ var(I) = \sigma^4$ & Unbiased $avg(I) = \sigma^2 $\\
$L_A$ & $L_A=\ln(A)=L_{1^A} + \log_2{\sigma}$ & Homoskedastic $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ \\
$L_I$ & $L_I=\ln(I)=L_{1^I} + 2 \log_2{\sigma}$  & Homoskedastic $var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ \\
\hline
\end{tabular}

%\end{center}
\end{table*}

In order to explore this experimentally, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a known homogenous area (from a RADARSAT2 image) against modelled PDF response. The excellent agreement that can be seen in Fig. \ref{fig:modelled_response} between the model and experimental data has long been noted in such graphs. In fact, this modelling has been used successful in explaining speckle phenomena, also verified through scientific experiments \cite{Ulaby_TGRS_1988}.

[IVM: Hai -following this paragraph, how can we say that your work is better/different???]

[IVM: Hai - I can't see the text on the graph. you need to redraw, probably need to add the axes and labels manually... unfortunately this applied to ALL of the graphs...???]
\begin{figure}[h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/amplitude_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/intensity_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_amplitude_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

%Logarithmic transformation has long been noted \cite{Arsenault_JOptSocAm_1976} as being able to transform multiplicative nature of SAR data into additive nature but most of the focus has been on addition of multi-samples for multi-look processing in the log-transformed domain. However, in this paper the investigation of variance is the focus.

%\section{Variance in Log-Transformed Domain}

\subsection{Consistent sense of distance in Log-Transformed domain}

The consistent sense is explored and illustrated in this section from two different perspectives. First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}. Consider the random variable defined as the distance between an observable sample and its expected value:

\begin{IEEEeqnarray}{l l l l l}
D^A &=& A &-& avg(A) \\
D^I &=& I &-& avg(I) \\
D^{L_A} &=& L_A &-& avg(L_A) = log_2{ \left( \frac{A}{avg(A)} \right)}\\
D^{L_I} &=& L_I &-& avg(L_I) = log_2{ \left( \frac{I}{avg(I)} \right)}
\end{IEEEeqnarray}

Noting the results from previous section, the pdf for these variable can be trivially given as

\begin{IEEEeqnarray}{l l l}
pdf(D^A) &=& \frac{2\left( D^A + \frac{\sqrt{\pi}}{2} \sigma \right)}{\sigma^2}e^{ \left( -\frac{\left( D^A + \frac{\sqrt{\pi}}{2} \sigma \right)^2}{\sigma^2} \right) } \\
pdf(D^I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{\left( D^I + \sigma^2 \right)}{\sigma^2} \right) } \\
pdf(D^{L_A}) &=& 2 \cdot 2^{\left[ \left( 2 D^{L_A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D^{L_A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
pdf(D^{L_I}) &=& 2^{\left[ \left( D^{L_I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D^{L_I} + \frac{\gamma}{\ln2} \right)} \right]}
\end{IEEEeqnarray}

It is evident from the equations that these distributions are dependent on $\sigma$ in the original SAR data but are independent of it in the log-transformed domain.

From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider the random variable defined as the contrast between two measured samples, in the log-transformed domain.

\begin{IEEEeqnarray}{l l l l l}
C_{L^A} &=& L_1^{A_\sigma} &-& L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }\\
C_{L^I} &=& L_1^{I_\sigma} &-& L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
\end{IEEEeqnarray}

Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the sense of contrast is consistent in the log-domain but inconsistent in the original domain. The pdf of these variables can be given as:

\begin{IEEEeqnarray}{l l l}
pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{1+2^{\left( C_{L^I} \right)}} \ln2 
\end{IEEEeqnarray}

Figure \ref{fig:residual_as_noise} illustrates this, showing excellent agreement between the analytical pdf and observable histogram of distance and contrast of the same area in a log-transformed intensity RADARSAT-2 image. Distance is calculated as the difference between each value point and the average value of that region, while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.

\begin{figure}[h!]
\centering
%\begin{tabular}{c}
	\subfloat[distance]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_dispersion_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill
	\subfloat[contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_contrast_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	}
%\end{tabular}
\caption{Observed and modelled pdf of distance and contrast in homogenous log-transformed intensity images.}
\label{fig:residual_as_noise}
\end{figure}

Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the sense of observable distance in original SAR data differs, ie. is inconsistent, across different homogenous areas. The observable distance in the log-transformed domain however is consistently the same across different homogenous areas. One possible benefit is that should the sigma filter be designed against the $pdf(C_{L^I})$, the scale estimator would no longer be required.

The consistent sense of distance can be used to test if a pixel belong to a ``known'' scatterer or to test if the any pair of measured data points belongs to the same class of scatterer. 
It may also serve to explain why, in the original SAR data domain, ratio based detector/classifiers are prefered to the differential measures that serve so well for other areas of image processing (the reason being that the differential is not consistent for SAR data).
The consistent sense of contrast also gives rise to the consistent sense of variance, which can be used to test if a group of pixels can form a homogenous area.

%In log transformed domain however, the standard differential methods can be used

%The conclusion in this section can be extended to larger number of pixels via the analysis of observable sample variance.

%\subsection{Sampling distribution of Variance in Log-Transformed domain}
%
%From previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as
%
%\begin{IEEEeqnarray}{l l l}
%pdf(V_{L^I}) &=& 
%	\frac{\ln2}{2} \frac{1}{\sqrt{V_{L^I}}} \left( \frac{2^{\sqrt{V_{L^I}}}}{\left( 1+2^{\sqrt{V_{L^I}}} \right)^2} + \frac{2^{-\sqrt{V_{L^I}}}}{\left( 1+2^{-\sqrt{V_{L^I}}} \right)^2} \right)\\
%pdf(V_{L^A}) &=&
%	\frac{\ln2}{4} \frac{1}{\sqrt{V_{L^A}}} \left( \frac{2^{\sqrt{4 V_{L^A}}}}{\left( 1+2^{\sqrt{4 V_{L^A}}} \right)^2} + \frac{2^{-\sqrt{4 V_{L^A}}}}{\left( 1+2^{-2\sqrt{V_{L^A}}} \right)^2} \right)
%\end{IEEEeqnarray}
%
%As log-transformed amplitude $L_A$ is simply half of log-transformed intensity values $L_I$, for brevity purposes, only results for log-transformed intensity values are presented.
%
%It could be seen that, in log-transformed domain, not only the expected mean of observable variance is constant, the sampling distribution of this random variable is independent to $\sigma$. We have seen this analytically for two sample variances. For larger number of samples, Monte-Carlo simulation is used to visuallize pdf of sample variances.
%
%\begin{enumerate}
%\item Each input sample is a random and independent set of n samples each drawn from a single pdf given in $pdf(L_A)$ or $pdf(L_I)$
%\item For each input set, the sample variance is calculated
%\item For all input set, a histogram of calculated values is ploted
%\item Number of input sets data generated is pre-determined as either 10000 (rough line) or 1000000 (smooth line)
%\end{enumerate}
%
%Here a figure giving simulated sampling distribution of variances with number of samples ranging from 2-9, analytical charts of 2, homogenous sample variances of 9. purpose to show match of is simulation with analytical, and simulation with measured data.
%
%Here gives an example showing sample variance calculated from a SAR image.

\section{Evaluating Speckle Filters on Homogeneous Areas}

\subsection{Experimental Results}

Fig. \ref{fig:log_consistency_model} illustrates the concept of consistency by plotting histograms of homogenous SAR data over different radiometric values.
Both single-look simulated and multi-look processed/box-car filtered data is displayed.
Specifically the plots show that the log-transformed domain is consistent while the plots from the original domain are not.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Single-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_boxcar.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Single Look in Intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/orig_inconsistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi Look in Intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/orig_inconsistency_boxcar.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Consistency demonstrated in the log-transformed domain and inconsistency evenident in the original SAR domain}
\label{fig:log_consistency_model}
\end{figure}

Fig. \ref{fig:log_consistency_filters} shows that the standard filters (Lee, Kuan, Frost and Gamma MAP) preserve this consistency in their filtered output. Intuitively, the reader may want to be reminded that the boxcar filter is actually multi-look processing.
%IVM: why?  I'm not sure I follow this or the sentence below.

This consistency will also lead to the consistent sense of distance described earlier and is significant because it is the tell-tale sign of the consistent contrast and variance.
This ensures applicability of various target detection/classification algorithms which employ the statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.

%We can briefly mention that the expected mean value are also preserved by the filters.

%This consistent sense of distance may explain a few phenomena that appears to be unrelated before.
%First it explain why in SAR edge detector is prefered to normal differential based detectors $R=I_1/I_2$ and $D=ln(I_1)-ln(I_2)$. In other words, in log-transformed domain, the standard differential based detector should also work.
%It leads to consistent variance in log-transformed domain, which we measured across the filtered results for different radiometric values.
%It could also explains why in the origianl domain, the ratio between variance/mean that is the ENL is a robust evaluation metric (it is consistent and thus can be evaluated on homogeneous area, regardless of specific radiometric value).

\begin{figure}
\begin{tabular}{c}
	\subfloat[Lee filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_lee.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_kuan.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_frost.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Gamma MAP filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_map.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Filtered results: consistency in log-transformed domain}
\label{fig:log_consistency_filters}
\end{figure}

\subsection{ Estimating ENL from MSE index in homogeneous areas }

Next we wish to show that the variance in the log-transformed domain can be mathematically related to the universal ENL index.

%Variance computation is theoretically given by Hoek and Xie.
%We show the computation can be simplified as in the confirmation report.
%Thus given an known homogeneous area, the log-variance can be computed and the ENL can be evaluated as ...
%We repeat the experiment in the confirmation report to confirm the agreement between theoretical analysis and experimental results. 
We assume that over homogeneous areas, the ground-truth remains unchanged, i.e. $X^L_i=X^L \forall i$. If a filters is unbiased, or the bias is already compensated for, i.e. $E(Y^L)=X^L$, then the MSE between unfiltered and filtered output becomes:

\begin{equation}
\Psi = \frac{ \sum^N_{i=1}{ (Y^L_i - E(Y^L)) } }{N} = var(Y^L)
\end{equation}

That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in the log-transformed domain.

Now, let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
First of all, since multi-look processing is unbiased, we will take the variance of the log-transformed multi-look processing output as the MSE performance index. 
Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for $L$-look log-transformed random variable as:

\begin{equation}
var(Y^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right)
\end{equation}

Next we will be showing that the ENL, i.e. $L$, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem we have

\begin{equation}
\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} }
\end{equation},

so then

\begin{equation}
\Psi= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right)
\end{equation}.

Noting that

\begin{equation}
\frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}
\end{equation},

then

\begin{equation}
\frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty}
\end{equation}.

In fact, we could estimate:
\begin{equation}
  \Psi = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}

Thus, the Equivalent Number of Looks, i.e. $L$, can be estimated as:
\begin{equation}
ENL = \frac{1}{\Psi \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

Let us demonstrate the above analysis experimentally.
We shall take a known $256\times256$ homogeneous area and corruptit with SAR-speckle pdf. Different multi-look processing filters are then repeatedly applied to the patch and the observable variance in the log-transformed domain is calculated. 
For each simulation run, the mean and variance values are reported in table \ref{tab:enl_in_log_domain}. 
The analysis values are calculated from eqn. \ref{eqn:perf_index_analytic}, together with estimated ENL values from eqn. \ref{eqn:enl_analytic}.
The approximation may not be perfect, but given that ENL is an integer value, the demonstration is extremely clear: the correspondence between actual ENL and estimated ENL is very close.

%%%IVM: Hai, please explain the ontent of the columns (i.e. that's in the brackets??)

\begin{table}
\centering

\begin{tabular}{c|c|c|c}
ENL  & Simulation                      &Analysis   &Est ENL       \\% &85\%             &90\%\\
\hline
2   &1.3397 ($0.1036 \cdot 10^{-03}$) &1.3423	 &2.0536	\\
3   &0.8201 ($0.0188 \cdot 10^{-03}$) &0.8220	 &3.0379	\\
4   &0.5898 ($0.0217 \cdot 10^{-03}$) &0.5907	 &4.0287	\\
5   &0.4595 ($0.0067 \cdot 10^{-03}$) &0.4607	 &5.0292	\\
6   &0.3764 ($0.0013 \cdot 10^{-03}$) &0.3774	 &6.0291	\\
7   &0.3195 ($0.0073 \cdot 10^{-03}$) &0.3196	 &7.0149	\\
8   &0.2773 ($0.0043 \cdot 10^{-03}$) &0.2771	 &8.0056	\\
9   &0.2448 ($0.0016 \cdot 10^{-03}$) &0.2446	 &9.0010	\\
10  &0.2193 ($0.0015 \cdot 10^{-03}$) &0.2189	 &9.9908	\\
11  &0.1975 ($0.0024 \cdot 10^{-03}$) &0.1981	 &11.0400	\\
12  &0.1807 ($0.0013 \cdot 10^{-03}$) &0.1809	 &12.0157	\\
13  &0.1663 ($0.0004 \cdot 10^{-03}$) &0.1664	 &13.0121	\\
14  &0.1544 ($0.0004 \cdot 10^{-03}$) &0.1541	 &13.9783	\\
15  &0.1435 ($0.0003 \cdot 10^{-03}$) &0.1435	 &15.0075	\\
16  &0.1342 ($0.0003 \cdot 10^{-03}$) &0.1342	 &16.0071	\\
17  &0.1263 ($0.0003 \cdot 10^{-03}$) &0.1261	 &16.9765	\\
18  &0.1189 ($0.0004 \cdot 10^{-03}$) &0.1189	 &18.0085	\\
19  &0.1126 ($0.0006 \cdot 10^{-03}$) &0.1125	 &18.9777	\\
20  &0.1070 ($0.0004 \cdot 10^{-03}$) &0.1067	 &19.9528	\\
21  &0.1016 ($0.0003 \cdot 10^{-03}$) &0.1015	 &20.9847	\\
22  &0.0969 ($0.0004 \cdot 10^{-03}$) &0.0968	 &21.9806	\\
23  &0.0924 ($0.0005 \cdot 10^{-03}$) &0.0925	 &23.0188	\\
24  &0.0885 ($0.0002 \cdot 10^{-03}$) &0.0886	 &24.0214	\\
25  &0.0850 ($0.0001 \cdot 10^{-03}$) &0.0849	 &24.9942	
\end{tabular}

\caption{Speckle Suppression Power: ENL and MSE }
\label{tab:enl_in_log_domain}
\end{table}

\section{Evaluating Speckle Filters on Heterogenous Area}

For the purpose of comparative, open and repeatable evaluation, in this section we create several test patterns areas which will be used to determine the performance of various common speckle filters.

[IVM: Hai - here you need to add just one sentence saying **why** you want to do this!!????]

\subsection{Evaluating Filters over Repeating Structured Patterns}

%First we discuss the experiments for repeated structured patterns. 
The types of pattern created here are: point targets, line targets, edge targets and a heterogeneous scene. These test patterns could, of course, be included into a larger composite test image. However we would prefer to highlight the results separately for each individual area.
All patterns are limited to two class of ground-truth: background and target areas. We will follow the convention in the radar community where the target is signified by the brighter area of the image. Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.

%We plots histograms of filtered values on target and background populations in log-transformed domain.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Line: each line is 1 pixel wide, separated by 4 pixels background]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_line.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Edge: each stripe is 4 pixel in width]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_edge.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Point: each point is a $2 \times 2$ squares spacing 4 pixels apart]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_point.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Heterogenous: staggered $1 \times 2$ rectangles]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_hetero.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\centering
\caption{Example windows of four target patterns, each $32 \times 32$ pixels in size.}
\label{fig:hetero_patterns}
\end{figure}

The test patterns are first corrupted with single look noise, and then the filters are applied onto these noised images.
From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} show thats feature preservation can be evaluated by examining the separability of the two background and target populations.
We visualize the separability of the two histograms by plotting the standard Receiver Operating Curve (ROC) and we measure it by computing the Area Under this Curve (AUC) index.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Simulated Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.none.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filtered Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.kuan.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Histograms: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.kuan.png.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[ROC AUC: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.none.roc.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[ROC AUC: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.kuan.roc.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Target and Clutter Separability: ROC and AUC indices}
\label{fig:hetero_patterns_roc_auc}
\end{figure}

From a detailed analysis point of view, Fig. \ref{fig:hetero_patterns_mse} shows how the MSE is related to the histograms' capability to seperate.
%that the radiometric preservation criteria is closely linked to the estimator's bias performance.
In pre-filtered images, subfigures \ref{fig:hetero_patterns_mse}(c and d), there is no bias error.
Then the seperability of clutter and target populations depends only on the variance of the additive noise. This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) the better the separation capability can be.

In post-filtered images (subfigures \ref{fig:hetero_patterns_mse}(d and f), the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account bias error.
Sub fig. \ref{fig:hetero_patterns_mse}(d) show that the Kuan filter, and in fact all of the other filters (whose plots are not reproduced here), introduces a bias error.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are always over-estimated.
This is probably due to the entropy reduction effect of speckle filters, and apparently, assuming that the variances are fixed, the lesser these bias errors, the better the separation capability.

%Also the speckle suppression is related to the measured variance.
Thus we believe: the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
In fact, table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
We note that the MSE in inversely correlated to this separability index, suggesting that the lower MSE achivable by the filters would lead to better feature preservation in general.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Simulated Residual Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.none.residual.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filtered Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.kuan.residual.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.none.residual.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Histograms: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.kuan.png.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[MSE: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.none.residual.mse.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[MSE: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.full.kuan.residual.mse.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{MSE: Bias Error and Variance Error}
\label{fig:hetero_patterns_mse}
\end{figure}

\begin{table}
\centering

\begin{tabular}{c|c|c|c}
pattern  & Filter                     & MSE    & AUC       \\% &85\%             &90\%\\
\hline
edge	& boxcar	& 0.2929	& 0.9157 \\
edge	& kuan	  & 0.2615	& 0.9361 \\
edge	& none	  & 1.9750	& 0.8090
\end{tabular}

\caption{MORE DATA TO COME: Lower MSE suggest better feature detection (AUC) }
\label{tab:mse_auc_in_log_domain}
\end{table}

\subsection{Evaluating Filters over Practical Images}

%The filters are applied on a real SAR data and 
To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig. \ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real SAR image (IVM: Hai - please identify the image - NASA/JPL or RADARSAT****???).
``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is extremely subjective.

[IVM: need to rewrite this later when the following stuff is added:??] Thus to compare the filters against each other, solely using qualitative judgements methodology, be it based on residual or ratio images, would be highly inadequate.
[IVM: Hai... you indicate you will add more...???] Fig. TODO plots the histogram of the residual images in log-transformed domain for various filters, while table TODO tabulate the computed MSE of the removed additive noise.
A quantitative measure would probably be measured as how closely this MSE related to the expected noise level in the original image.

%We plot the histogram of the derived images and evaluate how closely it matches with the noise characteristics of speckled image and show that the two methodologies are equivalent.
%The distance between the histograms can be measured as the difference between its entropy.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Original Patch]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Filtered Result]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.boxcar.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Ratio: Filtered / Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.ratio2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Ratio: Original / Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.ratio1.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[Log Residual: Filtered - Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.residual2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Log Residual: Original - Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.residual1.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Error Images: Ratio vs. Residual}
\label{fig:real_image_ratio_vs_residual}
\end{figure}

%The filters can also be applied on a speckle simulation of an aerial optical image. 
%A similar evaluation methodology can be applied for this type of experiment.
%As the ground-truth is available, an extra metric can be measured is the Mean-Squared-Error.
%However, if this is designed as a single-run experiment, then the measured MSE may not be very representative. 
%Also it should be noted that the performance of the filters may be dependent on the specific scene chosen, and designing an universal scene to comprehensively evaluate speckle filter is still an open question, as far as we know.

\section{Discussion and Conclusion}

\subsection{Discussion}

In the experiments above we used filters with a $3 \times 3$ sliding window altough we are aware that the normal window size used is much larger. The reasons for maintaining a small window in these tests is that filters with a smaller size allow us to use smaller patterns without too much concern about crosstalk among adjacent targets.
Secondly, we want to focus on advocating the use of MSE in the log-2 transformed domain for the evaluation of speckle filters, and do not wish to claim or to make any decision regarding which is the ``best'' filter. In other words, we are addressing the method of evaluating filters, and not claiming to address the issue of filter design itself.

However, interested filter designers however are welcome and encouraged to download our Matlab evaluation code online for the purpose of evaluating their designs\footnote{This can be found at \texttt{http:\\\\www.lintech.org\\Hai\\Matlab}}.

Stochastic simulation is used extensively to evaluate the performance of statistical estimators (i.e. speckle filters).
The use of simulation and modelling in speckle filtering research allows for faster simulation and evaluation of different underlying scenarios. 
Detailed analysis can then be done repeatedly on simulated small data sets without the need of a common real large image that is somehow representative. This allow qualititative requirements for the speckle removal process to be mapped into specific and quantitative requirements in the design of speckle filters.

It is interesting to note that all of the standard filters' outputs exhibit consistent plots of histogram in the log-transformed domain, suggesting a consistent sense of distance. 
This is significant because it is the indicator of consistent contrast and variance.
This in turn ensures applicability of various target detection/classification algorithms, which employ the statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.

We believe that the qualitative requirement of speckle suppression can be quantified as the variance in the log-transformed domain. 
The visual requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservations and speckle suppression.
These smaller requirements are equivalent to the bias and variance evaluation of the statistical estimator.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC curve (AUC).
We show experimentally that the MSE inversely correlates with the AUC index, for all of the simulated test patterns, and real test data.

The patterns used have been chosen based upon our exeriences and may affect evaluation results. It is unlikely that any single test pattern exists that would be `fair' towards every possible filter, filter designers may wish to include these and other test patterns within their evaluations in order to provide a comparative basis for their proposed designs.
However the patterns serve as guidelines, and filter designers may not want to overly optimize their filter's performance on any single of these patterns since doing so may make the filter lose out in other aspects.

While the patterns may not be the primary evaluative criteria, we believe that the MSE measure in the log-transformed domain (particularly log-2 transformed domain) should receive serious considerations by future filter designers. Again, this is due to good reasons: that the Gauss Markov theorem is applicable in this domain (and not in the original domain). Thus, we believe an optimization for minimal MSE is likely to succeed in good real-world performance.

%We hope and expect to see more standard image processing or signal processing algorithm being applicable to SAR images in log-transformed domain. 
%Of course the advice is caveat emptor

Finally, although it is widely known that log transformation converts multiplicative noise into additive noise, one should note that the noise is not Gaussian and not even centered around the origin. This may help to explain why averaging filters in the log-transformed domain proposed by Arsenault do not work well in practice.
To counter this, we suggest the use of maximum likelihood estimation instead of simple averaging (cite our works). In fact, it should be noted that averaging is the MLE estimation in the original domain.

\subsection{Conclusion}

To summarize, speckle filters are generally evaluated using many different qualitative criteria.
To compare the filters against each other, however, a method is needed to quantify and measure these various qualitative requirements and results.
Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
With the Guass-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.

Our contribution is mainly centered around two points. Firstly, we develop an equation to links the ENL index to the variance in the log-transformed domain, and illustrate it's efficacy for test images.
Secondly we show that MSE is inversely correlated to the AUC index for heterogenous areas, suggesting that the smaller MSE a filter can achieve, the better would be its ability to discriminate features.
In short, propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation scenarios, and suggest several test images that may be useful in this regard.
%Thus we suggest to use MSE in log-transformed domain as a single criteria to evaluate SAR speckle filters.
%We hope to provide the ultimate questions of how to evaluate and thus how to design excellent speckle filter stand with a clear and objective answer: MSE in log-transformed domain.

It should also be noted (cite POLSAR paper) that a similar consistent sense of distance also exists in POLSAR data. 
Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.

%IVM commented We also excited with the prospect of applying a wide variety of MSE-based or discriminator based algorithms into SAR and POLSAR values in log-transformed domain.
%We hope this would allow a wide range of developed algorithms, especially those in the fields of image processing, signal processing, machine learning or information processing, to be applicable in solving both SAR and POLSAR remote sensing problems.

%\section{Introduction}
%\appendices
%\section{Discussion and Conclusion}

%\subsection{Conclusion}

%The nature of SAR speckle is stochastics. The speckle filtering problem has been casted into statistical estimation theory framework. Speckle filtering, by and large, means the removal of stochastic component in SAR images. Various negative effects of heteroskedastic statiscal property of original SAR values are discussed. Log-transformation is shown to provide homoskedasticity in SAR modelling. Homoskedastic feature is shown here to help speckle-filtering, it might be possible that this features might also be found helpful in neural networks and other computational intelligence approaches.

%As certain filters are good for certain frequency range, certain estimators are good in certain situations. Combination of estimators, aka. filter banks, may become achievable should their efficiency be estimated, and a situation-dependent measure indicating a prefered estimator is established and employed. Variance in log-transformed domain is shown to be such a measure.

%The speckle filtering technique proposed in this paper has been shown to work for single-look SAR images. Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. The filter is developed from an easy to understand winner take all clustering approach to a more fuzzy possibilistic clustering algorithm. Should the fuzzyness taken to a new level, an optimal filter which requires no clustering may be specified and designed.

% references section
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,article}

\end{document}

### 2012-07-07 old.article.tex
comment: initalia push

%\documentclass[a4paper,10pt]{article}
\documentclass[journal]{IEEEtran}
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

\usepackage{cite} %for citations

 %this is for math typing (eg: cases)
\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{epsfig} %for figures

%\usepackage[caption=false]{caption}%for captions
\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures

%opening
\title{ SLC SAR speckle filtering using Homoskedastic effects of Logarithmic Transfomation }

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
	Brian~Quang-Huy~Nguyen,
	Ken-Yoong~Lee, 
	and Timo~Brestchneider % <-this % stops a space
\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen and Ian~McLoughlin are with the School of Computer Engineering, 
Nanyang Technological University, Singapore,}% <-this % stops a space
\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
\thanks{Manuscript received ?, 2010; revised ?.}}

\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, April~2010}%
{ Le \MakeLowercase{\textit{et al.}}: SLC SAR speckle filtering using Homoskedastic effects of Logarithmic Transfomation }

\begin{document}

\maketitle

\begin{abstract}
This paper note the ability of Logarithmic Transformation to convert heteroskedasticity of SAR single look data to homoskedastic values. Under the assumption of homogeneity, the sampling distribution of variance in log-transformed domain is constant and independent to the underlying back scattering coefficient. Then the observable sample variance in the log-transformed domain can be used as a measure of spatial non-homogeneity, thus statistical test on log-transformed variance can be formed to detect heterogeneity in a window of analysis. Using clustering algorithms, a novel speckle filtering algorithm is proposed to partition a non-homogenous area,  detected by the statistical test, into homogenous areas with estimated back scattering coefficient values.
\end{abstract}

\begin{IEEEkeywords}
Synthetic aperture radar, stochastic-process, speckle-filtering, inverse-problems, homoskedasticity
\end{IEEEkeywords}

%\textbf{Keywords: } Synthetic Aperture Radar, speckle-filtering, homoskedasticity

\IEEEpeerreviewmaketitle

\section{Introduction}
%\section{Logarithmic Transformation of SAR Single look data}

The nature of SAR speckle is stochastics over homogenous areas and heteroskedastic heterogenously. Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affect the distribution of measured SAR data. Speckle filtering, by and large, are estimators attempting to the unknown coefficient from observable SAR signal $(A)$.

SAR speckle-filtering can be and has been positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. The statistical framework attempts to estimate unknown statistical parameters from observed data. The stages consist of statistical modelling, estimator development and evaluating of the performance of estimators. Estimators' are evaluated based on the bias and variance properties of their estimates. The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.

For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily (cite here some latest). That is because: eventhough, the statistical model within individual resolution cell is well established, the applicability of its corresponding estimators is restricted to homogenous areas. Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the model to heterogenous images, virtually none has noted that spatial varition also gives rise to heteroskedasticity phenomena. Heteroskedastic, as explained in section ???, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean or equivalently its underlying back-scaterring coefficient $(\sigma)$. It is believed that heteroskedasticity give rise to serious negative impacts on various stages of speckle-filtering.

In modelling, heteroskedasticity has direct consequences in the central question of homogeneity or heterogeneity. In normal images, the contrast or variance among neighboring pixels have been used to measure homogeneity. Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. This make the problem of estimating variance is equal to the problem of estimating the mean and is the same as the main problem: estimating $\sigma$. The fact give rise to the vicious circle in SAR speckle filtering.

Case in point can be illustrated in the recently published improved sigma filter\cite{Lee_TGRS_2009}. The technique determines outlying points as being too far away from the standard deviation. However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required and used. It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.

Heteroskedasticity also poses numerous challenges in designing an efficient estimator. Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. Thus it renders the efficiency of any naive Ordinary Least Square estimator in serious doubt \cite{Furno_1991_JStatCompSimul}. If the variance is known \textit{a priori}, it has been proven, cite Aitken, that a weighted mean estimator is the best linear unbiased estimator. Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. The caveat however is that in SAR speckle filtering, variance is not known a priori. And eventhough variance can be estimated from observable values. And as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.

Heteroskedastic also decrease the effectiveness of estimators by increasing the variance of even best possible estimations. This fact makes it tricky to evaluate the performance of different estimators, even if quantitative experiments results is reported. In fact several quantitative simulated experiments has been carried out to compare the performance of different estimators\cite{Lee_TGRS_2009}. However only results of single experiment were reported. Due to the stochastic nature of the simulated experiement process, more experiments should be done to report the effectiveness, ie. variance, of each estimators' results.

Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. All of these tasks requires a good similarity or discriminant functions. Foundation to all these is the need of a consistence sense of distance. Unfortunately, by definition heteroskedasticity provided inconsistent measures of distance. This inconsistent sense of distance coupled with the failure of the ordinary least square regression methods are believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods to underperform.

In this paper, we aim to neutralize these various impacts. The paper is organized as follows. Section ??? will be devoted to discussion of the heteroskedastic phenomena in the original per-pixel SAR amplitude and intensity model. Logarithmic transformation is extended to the model and the homoskedastic property of it is asserted. Section ??? will discuss how sampling distribution of variance in the log-transformed domain can be used to model various degrees of homogeneity. Section ??? will presents a novel speckle filtering algorithm developed from heterogenous inference made possible by statistical testing of sample variances. Section ??? will present evaluation of our estimator both quantitatively through simulated experiments and qualitatively on real-life images.

\section{SAR speckle statistic model}

Useful, robust estimators require un-assuming models. This section will describe our model for speckle filtering. The first part will explain the heteroskedastic nature of original amplitude and intensity SAR data. In extending the original model to log-transformed domain, care has been taken to rely solely on rigorous mathematical and statistical principles.

\subsection{Original Heteroskedastic Model}

SAR speckle phenomena is explained as the interference of many coherent but dephased back-scaterring components, each reflecting from different and distributed elementary scaterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. These interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

\begin{equation}
\label{eqn:component_signal_pdf}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distributed and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.

\begin{IEEEeqnarray}{l l l}
pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
\end{IEEEeqnarray}

From statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to $\sigma$ unit distributions given below:

\begin{IEEEeqnarray}{l l l}
pdf(A_1) &=& 2A_1 e^{ \left( A_1^2 \right) }\\
pdf(I_1) &=& e^{ \left( -I_1 \right) }
\end{IEEEeqnarray}

It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. These relationships evidently manifest a mutiplicative nature. In fact, this condition has long been noted, but from different perspectives, in various SAR models including multiplicative model (cite JS Lee) and product model \cite{Jakeman_1980_JPhysAMathGen}.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. Consequently, the population expected mean and variance of the four distributions are given in table \ref{tbl:orginal_sar_avg_var}

\begin{table}[!h]
\caption{ Mean and Variance of Original SAR data are both related to the scale factor $\sigma$ }
\label{tbl:orginal_sar_avg_var}
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(A_1) = \frac{ \sqrt{\pi}}{2}$ & $var(A_1) = \frac{(4-\pi)}{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ & $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline
\end{tabular}

%\end{center}
\end{table}

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean. In the context of speckle filtering, table \ref{tbl:orginal_sar_avg_var} indicates the vicious circle: estimating variance is equal to estimating the mean and is as good as main problem, ie. estimating the unknown parameter $\sigma$

The formulas above has long been noted. In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al has noted the ratio of expected standard deviation to mean is a constant in both cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.

\subsection{ Homoskedastic effect of Logarithmic Transformation }

We propose to consider base 2 logarithmic transformtion of SAR orignal random variables

\begin{IEEEeqnarray}{l l l l l}
L_{1^A} &=& \log_2(A_1) &=& L_{1^I} / 2 \\
L_A &=& \log_2(A) 	&=& L_{1^A} + \log_2\sigma \\
L_{1^I} &=& \log_2(I_1) \\
L_I &=& \log_2(I) 	&=& L_{1^I} + 2 \log_2\sigma
\end{IEEEeqnarray}

The equations above also highlight the relationships among random variables in log-transformed domain. Two conclusions become evident from these formula. Firstly, in log-transformed domain, working on amplitude or intensity will tend to give identical results. Secondly, the effects of converting multiplicative nature to additive nature of logarithmic transformation is clearly manifested. Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as below:

\begin{IEEEeqnarray}{l l l}
pdf(L_{1^A}) &=& 2 \cdot 2^{\left[ 2 L_{1^A} - 2^{2 L_{1^A}} \right]} \\
pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
pdf(L_{1^I}) &=& 2^{\left[ L_{1^I} - 2^{L_{1^I}} \right]} \\
pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} 
\end{IEEEeqnarray}

Noting that these distributions belong to Fisher-Tippet family, the population expected mean and variances are given in table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being Euler-Mascheroni constant.

\begin{table}[!h]
\caption{ Mean and Variance of Log Transformed SAR values. It can be seen that the means are biased and the variances are no longer related to $\sigma$ }
\label{tbl:sar_log_domain_avg_var}
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}

%\end{center}
\end{table}

This result is consistence with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}.  The main difference would be the use of base 2 logarithm which is prefered here for faster computation. Table \ref{tbl:sar_log_domain_avg_var} clearly confirms the condition of homoskedastic,  defined as  the independence of conditional expected variance on the conditional expectation of mean.

Table \ref{tbl:sar_variables_properties} summarize the discussion so far. It can be seen that while original data, especially intensity values, should be prefered for multi-look processing, log-transformed domain, with its homoskedastic effects, offers consistence sense of dispersion and contrasts. Thus log transformation is proven here to be a homomorphic transformation allowing one to apply traditional linear, additive, least squared error regression signal processing (wavelet) and computational (neural networks) techniques into SAR data.

\begin{table*}[t]
\normalsize
%\hrulefill

%\begin{center}
\centering
\caption{ The properties of observable SAR random variables }
\label{tbl:sar_variables_properties}

\begin{tabular}{|l|l|l|l|}
\hline
 RV & Relationships  & Variance (skedasticity) & Mean (biasness) \\
\hline
$A$ & $A=\sigma A_1 $ & Heteroskedastic $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ & Unbiased $avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ \\
$I$ & $I=A^2=\sigma^2 I_1 $ & Heteroskedastic $ var(I) = \sigma^4$ & Unbiased $avg(I) = \sigma^2 $\\
$L_A$ & $L_A=\ln(A)=L_{1^A} + \log_2{\sigma}$ & Homoskedastic $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ \\
$L_I$ & $L_I=\ln(I)=L_{1^I} + 2 \log_2{\sigma}$  & Homoskedastic $var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ \\
\hline
\end{tabular}

%\end{center}
\end{table*}

The result here is experimentally confirmed by inspecting measured data from a known homogenous area. Fig. \ref{fig:modelled_response} plot the histogram of observable data within a homogenous area imaged by RADARSAT2 against modelled PDF response. The excellent agreement between this model and various experiments has long been noted and undisputed. This modelling has been very successful in eplaining speckle phenomena and verified through scientific experiments \cite{Ulaby_TGRS_1988}.

\begin{figure}[h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/amplitude_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/intensity_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_amplitude_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

Logarithmic transformation has long been noted \cite{Arsenault_JOptSocAm_1976} as being able to transform multiplicative nature of SAR data into additive nature but most of the focus has been on addition of multi-samples for multi-look processing in the log-transformed domain. However, in this paper the investigation of variance is the focus.

\section{Variance in Log-Transformed Domain}

\subsection{Consistent sense of distance in Log-Transformed domain}

The consistent sense is illustrated in this section from two different perspective. First, assume the back-scattering coefficient $\sigma$ is known a priori. Consider the random variable defined as the distance between an observable sample and its expected value.

\begin{IEEEeqnarray}{l l l l l}
D^A &=& A &-& avg(A) \\
D^I &=& I &-& avg(I) \\
D^{L_A} &=& L_A &-& avg(L_A) \\
D^{L_I} &=& L_I &-& avg(L_I)
\end{IEEEeqnarray}

Noting the results from previous section, the pdf for these variable can be trivially given as

\begin{IEEEeqnarray}{l l l}
pdf(D^A) &=& \frac{2\left( D^A + \frac{\sqrt{\pi}}{2} \sigma \right)}{\sigma^2}e^{ \left( -\frac{\left( D^A + \frac{\sqrt{\pi}}{2} \sigma \right)^2}{\sigma^2} \right) } \\
pdf(D^I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{\left( D^I + \sigma^2 \right)}{\sigma^2} \right) } \\
pdf(D^{L_A}) &=& 2 \cdot 2^{\left[ \left( 2 D^{L_A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D^{L_A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
pdf(D^{L_I}) &=& 2^{\left[ \left( D^{L_I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D^{L_I} + \frac{\gamma}{\ln2} \right)} \right]}
\end{IEEEeqnarray}

It is evident from the equations that these distributions are dependent on $\sigma$ in the original SAR data but is independent of it in the log-transformed domain.

From another perspective, given two adjacent resolution cells that is known to have the same but unknown back-scattering coefficient $\sigma$, consider the random variable defined as the contrast between two measured samples.

\begin{IEEEeqnarray}{l l l l l}
C_A &=& A_1^{\sigma} &-& A_2^{\sigma} \\
C_I &=& I_1^{\sigma} &-& I_2^{\sigma} \\
C_{L^A} &=& L_1^{A_\sigma} &-& L_2^{A_\sigma} \\
C_{L^I} &=& L_1^{I_\sigma} &-& L_2^{I_\sigma} 
\end{IEEEeqnarray}

The pdf of these variables can be given as:

\begin{IEEEeqnarray}{l l l}
pdf(C_A) &=& \text{ TBD dependent on } \sigma \\
pdf(C_I) &=& \text{ TBD dependent on } \sigma \\
pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{1+2^{\left( C_{L^I} \right)}} \ln2 
\end{IEEEeqnarray}

Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the sense of contrast is consistent in log-domain but in-consistent in original domain. Figure \ref{fig:residual_as_noise} illustrate good agreement between the analytical pdf and observable histogram of distance and contrast of the same area in log-transformed intensity RADARSAT-2 image. Distance is calculated as the difference between each value point and the average value of the patch, while contrast is calculated as the difference between two horizontally adjacent values in log-transformed domain.

\begin{figure}[h!]
\centering
%\begin{tabular}{c}
	\subfloat[distance]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_dispersion_hist_model_pdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill
	\subfloat[contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_contrast_hist_model_pdf_scene1.eps} 	
		 \label{intensity}
	}
%\end{tabular}
\caption{Observed and modelled pdf of distance and contrast in homogenous log-transformed intensity images}
\label{fig:residual_as_noise}
\end{figure}

Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the sense of observable distance in original SAR data differs, ie. is inconsistent, across different homogenous areas. The observable distance in log-transformed domain however is consistently the same across different homogenous areas. One possible benefit is that should the sigma filter be designed against the $pdf(C_{L^I})$, the scale estimator would no longer be required.

The conclusion in this section can be extended to larger number of pixels via the analysis of observable sample variance.

\subsection{Sampling distribution of Variance in Log-Transformed domain}

From previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as

\begin{IEEEeqnarray}{l l l}
pdf(V_{L^I}) &=& 
	\frac{\ln2}{2} \frac{1}{\sqrt{V_{L^I}}} \left( \frac{2^{\sqrt{V_{L^I}}}}{\left( 1+2^{\sqrt{V_{L^I}}} \right)^2} + \frac{2^{-\sqrt{V_{L^I}}}}{\left( 1+2^{-\sqrt{V_{L^I}}} \right)^2} \right)\\
pdf(V_{L^A}) &=&
	\frac{\ln2}{4} \frac{1}{\sqrt{V_{L^A}}} \left( \frac{2^{\sqrt{4 V_{L^A}}}}{\left( 1+2^{\sqrt{4 V_{L^A}}} \right)^2} + \frac{2^{-\sqrt{4 V_{L^A}}}}{\left( 1+2^{-2\sqrt{V_{L^A}}} \right)^2} \right)
\end{IEEEeqnarray}

As log-transformed amplitude $L_A$ is simply half of log-transformed intensity values $L_I$, for brevity purposes, only results for log-transformed intensity values are presented.

It could be seen that, in log-transformed domain, not only the expected mean of observable variance is constant, the sampling distribution of this random variable is independent to $\sigma$. We have seen this analytically for two sample variances. For larger number of samples, Monte-Carlo simulation is used to visuallize pdf of sample variances.

\begin{enumerate}
\item Each input sample is a random and independent set of n samples each drawn from a single pdf given in $pdf(L_A)$ or $pdf(L_I)$
\item For each input set, the sample variance is calculated
\item For all input set, a histogram of calculated values is ploted
\item Number of input sets data generated is pre-determined as either 10000 (rough line) or 1000000 (smooth line)
\end{enumerate}

Here a figure giving simulated sampling distribution of variances with number of samples ranging from 2-9, analytical charts of 2, homogenous sample variances of 9. purpose to show match of is simulation with analytical, and simulation with measured data.

Here gives an example showing sample variance calculated from a SAR image.

\subsection{Statistical Hypothesis testing of homogenity}

It should be noted that all discussions in section ??? and ??? is based on the assumption of homogenous thus single stochastic process. In a real given analysis area in SAR images, such condition is unknown. Fortunately homoskedastic property, manifested in the sampling distribution of variance, provide a method for testing this homo/heterogeneity condition.

Under the null hypothesis that the given analysis area is homogenous, the theoretical distribution of sample variance has been given in previous sub-section. Thus given measured values and calculated log-transformed sample variance, we could accept / the notion that the given analysis area is heterogenous or homogenous with certain degrees of confidence. This form the basic of the statistical hypothesis test of homogenity.

The test statistics used is the sample variance. The pdf, and cdf of this test can be derived using Monte-Carlo simulation, illustrated above, and in the simple case of two samples can be given analytically.

This give a figure of cdf for sampling distribution of variance. It is clear that if the sample variance is higher than a cut-off degree, the null hypothesis can be rejected with certain confidence.

A table for cut-off values is also given here!

It should be noted there is a difference between accepting the null hypothesis and simply failing to reject it. However, in the section that followed, the decision rule in use is that if the sample variance is lower than the cut-off value, the null hypothesis is accepted. A  short analysis is given below to show that for the purpose of speckle-filtering the difference is negligible.

\section{Speckle Filtering in Log-Transformed domain}

Given an area of analysis, its non-homogesousity can be detected by the statistical hypothesis test decribed above. If that is likely to be the case, clustering algorithm can be applied to partition the area into smaller regions. The process can be applied iteratively until all partitions can be considered to be homogenous (accepting the null hypothesis). This form the basis of our proposed speckle filtering technique.

\subsection{Homogenous Maximum Likelyhood Clustering}

Given a data set $X^e=\{x^e_1,...,x^e_n\}$ which follows exponential distribution $f^e(x)=\lambda e^{-\lambda x} $. We have already proven that the derivative data set $X^l=ln(X^e)$ follows Fisher Tippet distribution $f^l(x) = e^{d-e^d}$ with $d=x^l_i-\mu_0$. Next we are going to show analytically that, in the case of single-cluster, MLE of $\lambda$ from $X^e$ will equals MLE estimate of $\mu_0$ from $X^l$

Assume that the parameter of the distributions (ie. $\lambda$ or $\mu_0$ denoted as $\rho$) is known. MLE strategy maximize the conditional (likelyhood) probability $P(X^e | \rho )$. Product rule indicate that $P(X^e | \rho )=\displaystyle{\prod^n_{i=1}{P(x^e_i | \rho ) }}$. Maximize $P(X^e | \rho )$ also maximizes $\ln(P(X^e | \rho )) = \displaystyle{\sum^n_{i=1}{ \ln(P(x^e_i | \rho )) }}$. The parameter $\rho_0$ which maximizes likelyhood is found by setting

\begin{equation}
   \displaystyle{ \frac{ \partial{ \ln[P( X^e | \rho )] }  }{\partial{ \rho }} 
= \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^e_i | \rho )) } }{ \partial{ \rho } } }} 
= 0 }   
\end{equation}

Applying to log-transformed exponential distribution $X^l = \ln( X^e )$ we have
\begin{enumerate}
 \item $P(x^l_i | \mu) = e^{d - e^d}$ with $d=x^l-\mu $ thus $ \ln( P(x^l_i | \mu) ) = d - e^d$
 \item thus $ \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^l_i | \mu )) } }{ \partial{ \mu } } } = \sum^n_{i=1}{[ e^{ (x^l_i - \mu) } - 1 ]} } =  \sum^n_{i=1}{ \frac{ e^{ x^l_i } }{ e^{ \mu }} } - n $
 \item MLE estimate $\mu_0$ of $\mu$ is found by setting $\displaystyle{ \sum^n_{i=1}{ \frac{ e^{ x^l_i } }{ e^{ \mu_0 }}  } - n = 0}$ Noting that $ e^{ \mu_0 }$ can be moved out of the sum, that gives us $\displaystyle{ \sum^n_{i=1}{ e^{ x^l_i } } = e^{\mu_0} n }$
 \item Note that $ e^{ x^l_i } = x^e_i $ thus $\displaystyle{ \sum^n_{i=1}{ e^{ x^l_i } } = \sum^n_{i=1}{x^e_i} }$ or $\displaystyle{ e^{\mu_0} = \frac{ \displaystyle{ \sum^n_{i=1}{x^e_i} }}{n} }$
 \item This result consistent with the relation $\lambda_0 = e^{-\mu_0}$ (QED)
\end{enumerate}

In the case of samples coming from multiple random processes clustering algorithm can be used to partition the analysis area into homogenous areas. An adapted version of clustering is given as

\begin{enumerate}
\item Initialize the cluster centers
\item Assign each sample to a center $C_i$ that has the highest probability $P(x|C_i)$ (winner take all)
\item Recalculate cluster centers for each $C_i$
\item Iterate above 3 steps until there is no more changes in membership from the last iteration
\end{enumerate}

It could be see that the partition here is rudimental. A more elaborate gradient-descent algorithm is mentioned next

\subsection{Heterogenous Gradient Descent Possibilistic Clustering}

In this section, it is assumed that the sample is known to be coming from different underlying back-scattering radar cross section.

MLE strategy is to find $C$ by maximizing criterion function: $ \Upsilon = P(X|C) = \displaystyle \prod_{i=1}^n{P(x_i|C)}$ . Log-transform the MLE target function leads to $\log(\Upsilon)  = \displaystyle \sum_{i=1}^n{\log[P(x_i|C)]}$ which needs to be maximized

The standard iterative gradient descent learning where each cluster center is moved in a direction so as to maximize criterion function. To do that the ''moving force`` that is placed on each cluster $c_j$ is to be determined as

%\begin{equation}
\begin{eqnarray}
\label{eqn:single_cluster_move_force}
\frac{\partial(\log(\Upsilon))}{\partial(c_j)} 
	&=& \displaystyle \sum_{i=1}^n { \left( \frac{\partial(\log \left[ P(x_i|C) \right] }{\partial(c_j)} \right) }  
	\nonumber \\ 
	&=& \displaystyle \sum_{i=1}^n { \left( \frac{1}{P(x_i|C) } \cdot \frac{\partial(P(x_i|C))}{\partial(c_j)} \right) }
\end{eqnarray}
%\end{equation}

Eqn. \ref{eqn:single_cluster_move_force} is nice in the sense that the force applied on each cluster centers equals the sum of impacts from each data point. For each point, Eqn. (\ref{eqn:single_cluster_sample_derivative}) form the basis of the gradient descent MLE clustering

\begin{figure*}[t!]
\centering
\begin{eqnarray}
\label{eqn:single_cluster_sample_derivative}
\frac{\partial(P(x_i|C))}{\partial(c_j)} 
	= \left( \frac{ \partial(P(x_i|c_j) )}{\partial(c_j)}  \cdot \displaystyle \prod_{k=1,k \neq j}^c { \left[ 1-P(x_i|c_k) \right] } \right)
	%\nonumber \\
 	- \displaystyle \sum_{t=1,t \neq j}^c{ \left(  P(x_i|c_t) \cdot \displaystyle \prod_{k=1,k \neq j,t}^c { \left[ 1-P(x_i|c_k) \right] } \cdot \frac{ \partial(P(x_i|c_j) )}{\partial(c_j)}  \right) }
\end{eqnarray}
\end{figure*}

\begin{enumerate}
 \item The centers are initialized, possibly from the previous section
 \item Each cluster center $c_j$ is moved in proportion to $\frac{\partial(P(x_i|C))}{\partial(c_j)}$
\item The algorithm stops when the MLE $P(x_i|C)$ is no longer decreasing
\end{enumerate}

\section{Experiement Results and Discussions}%describe analysis and compare

\subsection{Evaluation on Simulated data}
The experiment setup is similar to \cite{Lee_TGRS_2009}. Evaluation is based on mean AND variance of total square error between estimated value and ground-truthed original values.

\subsection{Evaluation on Real Images}
Other algorithms' result and comparisions.

Comparisions criteria
\begin{enumerate}
\item Equivalent Number of Look 
\item Point target preservation
\item Texture preservation (if possible)
\end{enumerate}

\subsection{Discussions}

Issues to discuss
\begin{enumerate}
 \item Decision rule used in the hypothesis test
\item The confidence level used
\item The learning ratio used 
\end{enumerate}

%\appendices
\section{Conclusion}

The nature of SAR speckle is stochastics. The speckle filtering problem has been casted into statistical estimation theory framework. Speckle filtering, by and large, means the removal of stochastic component in SAR images. Various negative effects of heteroskedastic statiscal property of original SAR values are discussed. Log-transformation is shown to provide homoskedasticity in SAR modelling. Homoskedastic feature is shown here to help speckle-filtering, it might be possible that this features might also be found helpful in neural networks and other computational intelligence approaches.

The use of simulation and modelling in speckle filtering allow for faster simulation and evaluation of different underlying parameter estimations. Initial analysis can be done on simulated small data without the need of a real large image. Stochastics simulation also allows to evaluate efficiency of particular estimators. Inversely, qualititative requirements of speckle removal process can be mapped into specific requirements in designing speckle filters. As certain filters are good for certain frequency range, certain estimators are good in certain situations. Combination of estimators, aka. filter banks, may become achievable should their efficiency be estimated, and a situation-dependent measure indicating a prefered estimator is established and employed. Variance in log-transformed domain is shown to be such a measure.

The speckle filtering technique proposed in this paper has been shown to work for single-look SAR images. Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. The filter is developed from an easy to understand winner take all clustering approach to a more fuzzy possibilistic clustering algorithm. Should the fuzzyness taken to a new level, an optimal filter which requires no clustering may be specified and designed.

% references section
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,article}

\end{document}

### 2012-07-07 src/simulation_schema.tex
comment: initalia push

\documentclass{article}

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{pst-eps}
\begin{document}
\pagestyle{empty}

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=8em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, text centered,text width=7em, 
    minimum height=2em]
\tikzstyle{dummy} = [draw, ellipse, text centered,text width=7em, 
    minimum height=2em]

\begin{TeXtoEPS}
\begin{tikzpicture}[auto]
    % Place nodes
    \node [cloud] (gt) {$X$ \\ (ground-truth)};
    \node [block, right of=gt, node distance = 16em] (system) {SAR \\ Processor};
    \node [right of=system, node distance = 16em] (dummy1) {};
    \node [cloud, below of=dummy1, node distance = 6em] (observed) {$\tilde{X}$ \\ (observed)};
    \node [below of=observed, node distance = 6em] (dummy2) {};
    \node [block, left of=dummy2, node distance = 16em] (filter) {SAR \\ Speckle Filter};
    \node [cloud, left of=filter, node distance = 16em] (estimated) {$\hat{X}$ \\ (estimated)};
    % Draw edges
    \path [line] (gt) -- (system);
    \path [line] (system) -| (observed);
    \path [line] (observed) |- (filter);
    \path [line] (filter) -- (estimated);
\end{tikzpicture}
\end{TeXtoEPS}

\end{document}

### 2012-07-07 src/bdd.sh

@@ -1,0 +1,4 @@
+/opt/matlab/bin/matlab -r 'bdd()' -nojvm -nosplash -logfile out.log < exit_cmd.m &> /dev/null
+#cat out.log | less
+gimp bdd.eps &
+

### 2012-07-07 src/build.sh

@@ -1,0 +1,23 @@
+/opt/matlab/bin/matlab -r 'generate_scene2_log_intensity()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp scene2_log_intensity.eps &
+
+/opt/matlab/bin/matlab -r 'generate_scene1_log_intensity()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp scene1_log_intensity.eps &
+
+/opt/matlab/bin/matlab -r 'plot_amplitude_hist_model_pdf_scene1()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp amplitude_hist_model_pdf_scene1.eps &
+
+/opt/matlab/bin/matlab -r 'plot_intensity_hist_model_pdf_scene1()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp intensity_hist_model_pdf_scene1.eps &
+
+/opt/matlab/bin/matlab -r 'plot_log_amplitude_hist_model_pdf_scene1()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp log_amplitude_hist_model_pdf_scene1.eps &
+
+/opt/matlab/bin/matlab -r 'plot_log_intensity_hist_model_pdf_scene1()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp log_intensity_hist_model_pdf_scene1.eps &
+
+/opt/matlab/bin/matlab -r 'plot_log_intensity_dispersion_hist_model_pdf_scene1()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp log_intensity_residual_hist_model_pdf_scene1.eps
+
+/opt/matlab/bin/matlab -r 'plot_log_intensity_contrast_hist_model_pdf_scene1()' -nojvm -nosplash -logfile out.log < exit_cmd.m 
+#gimp log_intensity_contrast_hist_model_pdf_scene1.eps &

### 2012-07-09 article.tex
some comment for your changes

@@
 		 \epsfysize=1.5in
-		 \epsffile{src/amplitude_hist_model_pdf_scene1.eps} 	
+		 \epsffile{src/amplitude_histogram.eps} 	
 		 \label{amplitude}
@@
 		 \epsfysize=1.5in
-		 \epsffile{src/intensity_hist_model_pdf_scene1.eps} 	
+		 \epsffile{src/intensity_histogram.eps} 	
 		 \label{intensity}
@@
 Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
-The following subsection gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
+Subsection \ref{sec:homogeneous_theoretical} gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
 The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.
+But before we begin, a brief schematic overview description of our evaluational methodology is presented.
 
@@
 
-Before we begin, Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of the various experiments presented in this paper.
+Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of the various experiments presented in this paper.
 The ``SAR Processor'' block indicates either 
@@
 \subsection{ Estimating ENL from MSE index in homogeneous areas }
+\label{sec:homogeneous_theoretical}
 
@@
 \begin{equation}
-L = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
+\hat{L}_{est} = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
 \label{eqn:enl_analytic}
@@
 \centering
-\begin{tabular}{r|c|c|c|r}
-ENL & Var (Theory) & Var (Analysis) & Var (Observed) & ENL (Estimated) \\
+\begin{tabular}{r|c|c|c|c}
+ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
 \hline
@@
 \begin{tabular}{c|r|c|c|r}
-Pattern  & Filter  & AUC & MSE (true)   & MSE (noise)      \\% &85\%             &90\%\\
+Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
 \hline
@@
 \centering
-\begin{tabular}{c|r|c|c|r}
-Pattern  & AUC - true MSE (p-value) & AUC - benchmark MSE (p-value) \\
+\begin{tabular}{c|c|c}
+Pattern  & AUC - $MSE_{true}$ (p-value) & AUC - $MSE_{benchmark}$ (p-value) \\
 \hline
@@
 		 \epsfysize=1.5in
-		 \epsffile{src/P1090360.eps} 	
+		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
 		 \label{amplitude}
@@
 		 \epsfysize=1.5in
-		 \epsffile{src/P1090253.eps} 	
+		 \epsffile{src/simulated_images.hanoi_suburb.gt.jpg.eps} 	
 		 \label{intensity}
@@
 \begin{tabular}{r|r|c|c}
-Pattern  & Filter  & MSE (true)   & MSE (noise)      \\% &85\%             &90\%\\
+Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
 %\hline
@@
 	\subfloat[Simulated GrayScale Image (ground-truth)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
 		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
@@
 	\hfill	
-	\subfloat[Unfiltered Noisy Image (true MSE = 4.1174)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
 		 \epsffile{src/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
@@
 	} \\
-	\subfloat[PDE Result (true MSE = 3.8022, residual MSE = 0.0073)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
 		 \epsffile{src/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
@@
 	\hfill	
-	\subfloat[Lee Result (true MSE = 0.4984, residual MSE = 3.25553)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
 		 \epsffile{src/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
@@
 	} \\
-	\subfloat[Frost Result (true MSE = 0.3490, residual MSE = 4.6856)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
 		 \epsffile{src/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
@@
 	\hfill	
-	\subfloat[Boxcar Result (true MSE = 0.3107, residual MSE = 4.2328)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
 		 \epsffile{src/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
@@
 \centering
-\begin{tabular}{c|r}
-filter & MSE (noise)\\
-\hline
-pde & 0.2583\\
-map & 2.6936\\
-kuan & 3.3924\\
-lee & 3.4172\\
-boxcar & 3.6918\\
-frost & 4.1191\\
-\hline
-SLC unfiltered MSE & 4.1167  
+\begin{tabular}{c|r|r}
+filter & $MSE_{noise}$ & $MSE_{benchmark}$\\
+\hline
+pde & 0.2583 & 3.8584 \\
+map & 2.6936 & 1.4231 \\
+kuan & 3.3924 & 0.7243 \\
+lee & 3.4172 & 0.6995 \\
+boxcar & 3.6918 & 0.4249 \\
+frost & 4.1191 & 0.0024 \\
+\hline
+SLC unfiltered MSE & 4.1167 & 4.1167 
 \end{tabular}
@@
 \begin{tabular}{c}
-	\subfloat[PDE Filter: MSE (noise) = 0.2583]{
+	\subfloat[PDE Filter: $MSE_{benchmark}=3.8584$]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[MAP Filter: MSE (noise) = 2.6936]{
+	\subfloat[MAP Filter: $MSE_{benchmark}=1.4231$]{
 		 \epsfxsize=1.5in
@@
 	} \\
-	\subfloat[Lee Filter: MSE (noise) = 3.4172]{
+	\subfloat[Lee Filter: $MSE_{benchmark}=0.6995$]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[Frost Filter: MSE (noise) = 4.1191]{
+	\subfloat[Frost Filter: $MSE_{benchmark}=0.0024$]{
 		 \epsfxsize=1.5in
@@
 
-\caption{Filtering Real Images: Visual Validation}
+\caption{Filtering Real Images: Smaller $MSE_{benchmark}$ suggests visually better images}
 \label{fig:real_image_results}

### 2012-07-10 article.tex
201207_Jul10

@@
 	a few consistent measures of distance emerge.
-With these subtractive differences become consistent and predictable, 
-	we show, through experiments and analysis, that 
+With these, subtractive differences become consistent and predictable. 
+We show, through experiments and analysis, that 
 	the familiar mean squared error (MSE) criteria can reliably serve 
@@
 
-%\textbf{Keywords: } Synthetic Aperture Radar, speckle-filtering, homoskedasticity
-
 \IEEEpeerreviewmaketitle
@@
 
-The nature of SAR speckle is that:
+The nature of SAR speckle is that
 	it is stochastic even when the underlying radiometry is constant, 
 	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
-Nevertheless, statistical models are developed to derive the underlying back-scattering coefficient ($\sigma$) from the measured SAR data. 
-Then speckle filters are, by and large, estimators that attempt to determine the unknown coefficient from observable SAR data.
+Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
+Then speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.
 
 SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
-The stages in this statistical framework consist of statistical modelling, estimator development and evaluating of the performance of estimators. 
+The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
 The estimators are typically evaluated based on the bias and variance properties of their estimates; 
-	with lower bias and / or lower variance, hence lower MSE, indicates better performances. 
-Ideally, estimators' evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-Also, due to the stochastic nature of SAR and simulation process, 
-	statistical summaries of repeated simulating experiments are normally preferred to single-run results.
-
-A survey of SAR speckle filter research, however, indicates 
+	with lower bias and / or lower variance, hence lower MSE, indicating more accurate performance.
+Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
+Also, due to the stochastic nature of SAR processing as well as simulating process, 
+	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.
+
+Our survey of SAR speckle filter research, however, indicates 
 	a different picture from the standard practice of the statistical framework, 
@@
 	bias and variance evaluation may not be the most useful measures. 
-Thus, the standard evaluation metric of mean-squared-error is found to be inapplicable.
-%This makes the standard mean-squared-error evaluation to be inapplicable, at least in the original domain. 
+Thus, the standard evaluation metric of mean-squared-error is not applicable,
+	as alternative evaluation criteria are proposed.
 In fact, a survey of relevant literature fails to reveal 
-	a single universally agreed quantitative metric to evaluate speckle filters.
-
-The common theme is that each newly proposed speckle filter is often found to be published along with a customised methodology of evaluating its own performance.
-And many papers lack any comparative basis beyond simple visual qualititave comparisions on a few image scenes. 
+	a single universally agreed quantitative metric for the evaluation of speckle filters.
+
+The common theme is that each newly proposed speckle filter tends to be published along with a customised methodology for evaluating its own performance.
+Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
 While such visual comparison is useful, as an evaluative methodology, regretably it lacks scientific objectivity. 
@@
 	however  due to the lack of a standardized performance criteria, 
-	the evaluation metrics change eccentrically from one paper to the next.
-
+	the evaluation metrics can change eccentrically from one paper to the next.
+
+In this paper, we propose the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
 The rest of this paper is structured as follows.
@@
 Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
-Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous area.
-Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
+Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
+Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
 	to choose the most suitable speckle filter for a given satellite-captured SAR image.
@@
 %Addressing this issue, 
-There has been a few published articles dedicated to the topic of evaluating speckle filters.
-However, our survey of SAR speckle filtering research indicates 
-	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
-In the rest of this introductory section, we briefly review published work 
+%There have been a few published articles dedicated to the topic of evaluating speckle filters.
+%However, our survey of SAR speckle filtering research indicates 
+%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
+In this section, we briefly review published work 
 	related to the topic of evaluating SAR speckle filters.	
-
 It is customary to divide the evaluation of speckle filters into two scenarios:
-	homogeneous area and heterogeneous scenes.
-In homogeneous area,
+	homogeneous areas and heterogeneous scenes.
+In homogeneous areas,
 	speckle filters are expected to estimate with negligible radiometric bias.
-Thus evaluating speckle filters on homogeneous area have traditionally been focused on evaluating the variation of the estimators' output.
-In contrast, the methodologies to evaluate speckle filters in heterogeneous area are much more complex, probably due to the following difficulties.
+Thus evaluating speckle filters on homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
+By contrast, the methodologies to evaluate speckle filters in heterogeneous areas are much more complex, probably due to the following difficulties.
 The first difficulty is to find out an absolute ground-truth against which quantitative criteria can be measured.
 The second challenge is to come up with a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
-In this subsection, various published work in evaluating SAR speckle filters are critically reviewed.
-
-The general requirement for speckle filters is that its application should allow easier detection and classification of the imaging features.
-As shown in the subsequent section, 
-	one can choose to work in original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
-	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
-In this log-transformed domain, the requirement of speckle filtering can be broken down into two smaller requirements.
-On the one hand, the filters should preserve the underlying radiometric signal (i.e.
-radiometric preservation), while on the other hand, they should reduce the variation of the additive noise (i.e.
-speckle suppression).
-These smaller requirements can be intepreted and evaluated by evaluating, also in log-transformed domain, the output's bias and variance error.
-The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirement of speckle filtering.
+%In this subsection, various published work in evaluating SAR speckle filters are critically reviewed.
+
+We believe that the metric to evaluate speckle filter should be relevant to the normal usage of such filters.
+The general requirement for a speckle filter in SAR processing framework is that its application should allow easier measurement, detection and classification of the underlying radiometric features.
+%As shown in the subsequent section, 
+%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
+%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
+As shown in the subsequent sections, in the log-transformed domain, 
+	this overall requirement of speckle filtering can be broken down into two smaller requirements.
+On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement), while on the other hand, they should reduce the variation of the additive noise (i.e.
+speckle suppression power).
+These requirements can be measured and evaluated by determining, in the log-transformed domain, the bias and variance error of the output.
+The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirements of speckle filtering.
 %Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.
@@
 For homogeneous scenes, 
-	where the underlying radiometry is assumed to be unchanged, 
-	the filtered results can be statistically considered as samples of 
+	where the underlying radiometry is assumed to be constant, 
+	the filtered results, statistically speaking, can be considered as samples of 
 		a single but complex stochastic process.
 %Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
-From the logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can then be judged using the familiar bias and variance evaluation.
+Then, from the logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
 	%are expected to estimate with no radiometry bias. 
@@
 
-A metric that can be used to detect radiomtric distortion is the ratio between the noisy pixel to the estimated value $r = X_{org}/X_{est}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
-In the log-transformed domain, the equivalent index would, of course, be a simple substraction.
-In \cite{Shi_IGARSS_1994}, Shi et al found that 
+A metric that can be used to detect radiomtric distortion is the ratio between the estimated number and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
+A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
+In the log-transformed domain, the equivalent index for $r$ would, of course, be a simple substraction.
+In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.
+
+Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
 	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias.
-In this paper, we also observe that all of these standard filters not only can preserves the expected radiometric values, but in the log-transformed domain they also can preserve a few substractive and consistent measures of distance.
+In this paper, we will also show that all of these standard filters 
+	not only can preserves the expected radiometric values, 
+	but in the log-transformed domain they also can preserve a few substractive and consistent measures of distance.
 
@@
 Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
-In section 3, it will be shown that, for homogeneous areas, ENL is related to variance in log-transformed domain.
-The link is also consistent with other independent results concerning measures of homogeneity where, Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity,
-	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ to evaluate scene heterogeneity.
+In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the log-transformed domain.
 %However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
-In this paper we propose the use of variance to evaluate the noise suppression power of speckle filters.
-Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
-	which is a component of MSE evaluation, 
-	can be and practically has been used to evaluate speckle filters.
-%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters in homogeneous area.
-
-Real-life and practical images, however, are not homogeneous, 
-	and there are a few associated difficulties in evaluating speckle filters in heterogenous scenes.
+Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters which is the primary criteria to evaluate speckle filters over homogeneous area.
+%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
+%	which is a component of MSE evaluation, 
+%	can be and practically has been used to evaluate speckle filters.
+%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.
+
+Real-life and practical images, however, are not homogeneous.
+Thus there are a few associated difficulties in evaluating speckle filters in heterogenous scenes.
 %and there are many proposed methods of evaluating speckle filters in such areas. 
@@
 %and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
-The first difficulty in evaluating speckle filters for heterogeneous scene is to find the bases for comparision. 
+The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
 It is trivially easy to estimate the underlying radiometric co-efficient if an area is known to be homogeneous
@@
 Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
-Under a multiplicative model, the ratio images is expected to comprise the noise being removed, (i.e. it should be completely random). 
+Under a multiplicative model, the ratio image is expected to comprise the noise being removed, (i.e. it should be completely random). 
 Being random, this should display as little ``visible'' structure as possible. 
 %Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
-However, when displaying such images for visual evaluations, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
+However, when displaying such images for visual evaluation, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
 We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
@@
 Evaluation would then determine how closely related the two feature maps are. 
-Various methods may be applied extract features; some that have been used are the Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} or edge map \cite{Frost_PAMI_1982}.
-While significant effort has been spent on these evaluations, we have serious doubts about the precision of this methodology.
+Various methods may be applied to extract features; some that have been used are the Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} or edge map \cite{Frost_PAMI_1982}.
+While significant effort has been spent on these evaluations, serious doubts remain concerning the precision of this methodology.
 This is because feature extraction algorithms are only approximations 
@@
 		but also heavily reliant on the inherent noise.
-Unfortunately, speckle filters invariably alter the noise's characteristics.
+Unfortunately, speckle filters invariably alter the noise characteristics.
 Thus without a clear understanding of these dependencies and no absolute ground truth, 
-	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interprete the accuracy of its results.
+	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interpret the results and especially its accuracy.
 %is just too imprecise for us.
@@
 In this paper, we also make use of a similar methodology discussed above with two important changes.
-Firstly, our simulated experiments offer absolute ground-truth, serving as the base of comparisons.
-Secondly, our threshold based feature extraction algorithm is extremely simple.
-More importantly, the dependency between the algorithm's performance and the noise level is well established. 
-This performance 
-	can conveniently be visualised by plotting the Receiver Operating Characteristics Curve (ROC) 
-	as well as objectively be quantified by measuring the Area Under this Curve (AUC). 
-As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria then allow for the comparative evaluation of feature preservation capabilities of different speckle filters.
+Firstly, our simulated experiments offer absolute ground-truth.
+Secondly, our threshold-based feature extraction algorithm is extremely simple.
+More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
+This performance can be 
+	conveniently visualised by plotting the Receiver Operating Characteristics Curve (ROC) 
+	as well as objectively quantified by measuring the Area Under this Curve (AUC). 
+As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of feature preservation capabilities for different speckle filters.
 
@@
 
-(TO REWRITE) Overall, we see many different methods and metrics used for evaluating speckle filters.
+Overall, many different methods and metrics have been proposed to evaluate varios aspects of speckle filters. 
 However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
@@
 
-Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
-	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
-The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
-However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
+%Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
+%	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
+%The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
+%However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
 %Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
@@
 
-Another attempt is to apply a universal mean squared error criteria into the context of SAR data. However since SAR data is heteroskedastic, the use of MSE is not straightforward. 
+Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
+However since SAR data is heteroskedastic, which violaes the Gauss Markov theorem, the use of MSE is not straightforward. 
 Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation.
@@
 
-In this paper, we propose the use of MSE in the homoskedastic log-transformed domain.
-This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean).
+%Thus we propose the use of MSE in the homoskedastic log-transformed domain to evaluate eps. 
+%This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean).
 We also show experimentally that this MSE measure is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability can be.
+
+In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
+As the important Gauss Markov theorem becomes applicable again, 
+	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
+Initial intitution suggests that each components of the MSE measure, 
+	namely bias and variance evaluation, can be mapped into 
+	the requirements of radiometric preservation and speckle suppression for speckle filters.
+Before the details of our evaluation methodology is presented, 
+	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
 
@@
 \end{table}
+
+The finding here is also consistent with other independent results where, Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
+	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ to evaluate scene heterogeneity.
 

### 2012-07-24 article.tex
auto

@@
 The estimators are typically evaluated based on the bias and variance properties of their estimates; 
-	with lower bias and / or lower variance, hence lower MSE, indicating more accurate performance.
+	with lower bias and / or lower variance, hence lower MSE, indicating better accuracy.
 Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-Also, due to the stochastic nature of SAR processing as well as simulating process, 
+Also, due to the stochastic nature of SAR processing, hence, of the underlying simulation process, 
 	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.
@@
 Our survey of SAR speckle filter research, however, indicates 
-	a different picture from the standard practice of the statistical framework, 
+	a different picture from the standard practice of this statistical framework, 
 	specifically, in the stage of performance evaluation. 
@@
 In fact, a survey of relevant literature fails to reveal 
-	a single universally agreed quantitative metric for the evaluation of speckle filters.
+	a single universally agreed quantitative metric for the performance of speckle filters.
 
@@
 While such visual comparison is useful, as an evaluative methodology, regretably it lacks scientific objectivity. 
-Other papers do present quantitative measurements, 
+Some papers do present quantitative measurements, 
 	however  due to the lack of a standardized performance criteria, 
@@
 %	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
-In this section, we briefly review published work 
-	related to the topic of evaluating SAR speckle filters.	
+%In this section, we briefly review published work 
+%	related to the topic of evaluating SAR speckle filters.	
 It is customary to divide the evaluation of speckle filters into two scenarios:
@@
 Thus evaluating speckle filters on homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
-By contrast, the methodologies to evaluate speckle filters in heterogeneous areas are much more complex, probably due to the following difficulties.
+By contrast, the methodologies used to evaluate speckle filters in heterogeneous areas are much more complex, probably due to the following difficulties.
 The first difficulty is to find out an absolute ground-truth against which quantitative criteria can be measured.
 The second challenge is to come up with a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
-%In this subsection, various published work in evaluating SAR speckle filters are critically reviewed.
-
-We believe that the metric to evaluate speckle filter should be relevant to the normal usage of such filters.
-The general requirement for a speckle filter in SAR processing framework is that its application should allow easier measurement, detection and classification of the underlying radiometric features.
+In this section, various published work in evaluating SAR speckle filters are reviewed.
+
+The metric to evaluate speckle filter should be relevant to the normal usage of such filters.
+The general requirement for a speckle filter in SAR processing frameworks is that its application should allow easier measurement, detection and classification of the underlying radiometric features.
 %As shown in the subsequent section, 
@@
 %	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
-As shown in the subsequent sections, in the log-transformed domain, 
+As shown in the subsequent sections, by applying log-transformation, 
 	this overall requirement of speckle filtering can be broken down into two smaller requirements.
-On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement), while on the other hand, they should reduce the variation of the additive noise (i.e.
-speckle suppression power).
-These requirements can be measured and evaluated by determining, in the log-transformed domain, the bias and variance error of the output.
-The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirements of speckle filtering.
+On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement).
+On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
+These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
+The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirement of speckle filtering.
 %Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.
@@
 	where the underlying radiometry is assumed to be constant, 
-	the filtered results, statistically speaking, can be considered as samples of 
+	the filtered results, statistically speaking, are considered to be samples of 
 		a single but complex stochastic process.
@@
 
-A metric that can be used to detect radiomtric distortion is the ratio between the estimated number and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
+A metric that can be used to detect radiometric distortion is the ratio between the estimated number and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
 A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
-In the log-transformed domain, the equivalent index for $r$ would, of course, be a simple substraction.
+In the log-transformed domain, the equivalent index for evaluation would, of course, be a simple substraction.
 In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.
@@
 In this paper, we will also show that all of these standard filters 
-	not only can preserves the expected radiometric values, 
-	but in the log-transformed domain they also can preserve a few substractive and consistent measures of distance.
+	not only preserves the expected radiometric values, 
+	but in the log-transformed domain they also preserve a few subtractive and consistent measures of distance.
 
@@
 It is trivially easy to estimate the underlying radiometric co-efficient if an area is known to be homogeneous
-However, without simulation or access to lab environment ground-truth, it is practically impossible to do so for real-life images (thus the need for speckle filters' estimation).
+However, without simulation or access to lab environment ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters' estimation).
 
@@
 The ratio image then becomes a simple substraction image.
-The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see section \ref{sec:practical_conjecture}).
+The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).
 
@@
 Unfortunately, speckle filters invariably alter the noise characteristics.
-Thus without a clear understanding of these dependencies and no absolute ground truth, 
-	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interpret the results and especially its accuracy.
+Thus, without a clear understanding of these dependencies and no absolute ground truth, 
+	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interpret the results, especially its accuracy.
 %is just too imprecise for us.
@@
 
-Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements too.
+Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
 This is the second difficulty in evaluating speckle filters for heterogenous scenes.
 Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional level.
-In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preservating underlying radiometric differences (such as causing excessive blurring), and vice versa.
+In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa.
 %One can relatively easily satisfy one of these criteria, but not easily satisfy both.
@@
 However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
-Wang \cite{Wang_2005_MIPR} has attempted to look at the problem: he proposed using fuzzy membership to weight opinions of an expert panel. 
+Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
 Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and is still subjective in nature.
@@
 Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
-However since SAR data is heteroskedastic, which violaes the Gauss Markov theorem, the use of MSE is not straightforward. 
+However since SAR data is heteroskedastic, which violaes the assumptions of Gauss Markov theorem, the use of MSE is not straightforward. 
 Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation.
@@
 	and it may also explain why in original SAR domain the ratio based detector / classifier is prefered to the differential measures, which is not consistent. 
-An example application of this is described in our fMLE speckle filter.
+An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
 The consistent sense of contrast also gives rise to the consistent measure of variance, which can be used to test if a group of pixel can form an homogenous area.
@@
 
-\section{Evaluating Speckle Filters on Homogeneous Areas}
-\label{sec:eval_homo}
-
-In this section, the methodology to evaluate speckle filters on homogeneous area in log-transformed domain is illustrated.
-Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
-Then the filters are traditionally compared by measuring its speckle suppression power using the ENL index.
-Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
-Subsection \ref{sec:homogeneous_theoretical} gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
-The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.
-But before we begin, a brief schematic overview description of our evaluational methodology is presented.
-
-\subsection{ Speckle Filtering Process: General Schema and Evaluation Metrics }
-
-Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of the various experiments presented in this paper.
-The ``SAR Processor'' block indicates either 
-	the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is captured in $\tilde{X}$ or
-	the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
-In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
-Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.
-
-The ``SAR Speckle Filter'' block indicates the speckle filtering process, 
-	which takes in the noisy speckled SAR data $\tilde{X}$ 
-		and outputs $\hat{X}$ as a better estimate of the ground-truth (i.e. $X$).
-The speckle filters used in this paper are: 
-	boxcar filter, Lee filter, Kuan filter, Frost filter, Gamma Map filter and PDE filter.
-Evidently when there is no filter applied then $\hat{X}_{none} = \tilde{X}$.
+\subsection{ Speckle Filtering Process And The Homoskedastic Log-transformed Domain}
+\label{sec:schema_log_images}
 
@@
  \centering
- \epsfxsize=3in
- \epsfysize=1.5in
+ \epsfxsize=2.4in
+ \epsfysize=1.2in
  \epsffile{src/simulation_schema.eps} 	
@@
 
-Different metrics to evaluate speckle filters, that are investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
-When ground-truth is available, 
-	either in simulated experiments or in homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated values and its true values.
-In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
-The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be think of as the level of noise being removed by speckle filtering process.
-While as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) is normally known or can be estimated reasonably well.
-Thus the base MSE level which also a measure of the speckle noise level can also be estimated.
-Naturally, the speckle filter should remove as much noise as possible, 
-	while it also should not remove more variations than that caused by the speckle noise.
-%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base
+Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and SAR speckle filtering process.
+The ``SAR Processor'' block indicates either of the following processes.
+First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded in $\tilde{X}$.
+And second is the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known ground-truth pattern $X$.
+%In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
+%Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.
+
+The ``SAR Speckle Filter'' block indicates the speckle filtering process, 
+	which takes the noisy speckled SAR data $\tilde{X}$ as input
+	and outputs $\hat{X}$ as a better estimation of the ground-truth (i.e. $X$).
+The speckle filters used in this paper are: 
+	boxcar filter, enhanced Lee filter, enhanced Kuan filter, enhanced Frost filter, Gamma Map filter and PDE filter \cite{You_TIP_2000}.
+Evidently in the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
+%Thus $MSE_{residual}^{none} = MSE_{base}$
+
+Logarithmic transformation offers several consistent measures of distance, 
+	which is hypothised to be significant  in evaluating speckle filters.
+	A case in point is in visual evaluation of filtered results on real captured SAR images.
+Since the radiometric ground-truth is not available, %the most common 
+%In real SAR captured images, the radiometric ground-truth normally is not available.
+	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
+Traditional method is to investigate the ratio images between the filtered output and the noisy input images.
+Since logarithmic transformation convert these ratio into substractive residual
+	, which are consistent, residual analysis can be used to analyse and evaluate the performance of speckle filters.
+To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig.
+\ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
+``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is extremely subjective.
+
+%Our qualititative conclusion is that
+%	a. it is apparently easier to notice the ``visible structure'' being removed in the residual noise pictures than the ratio mages, and
+%	b. even so, the above conclusion is at best quite subjective.
+%Thus to compare the filters against each other, 
+%	quantitative measures are preferred.
+
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[Original Patch]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Boxcar Filtered Result]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.boxcar.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Ratio: Filtered / Original]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.ratio2.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Ratio: Original / Filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.ratio1.eps} 	
+		 \label{intensity}
+	}  \\
+	\subfloat[Log Residual: Filtered - Original]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.residual2.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Log Residual: Original - Filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.residual1.eps} 	
+		 \label{intensity}
+	} 
+\end{tabular}
+\caption{Visualising Removed ``Noise'': Ratio images in the original domain vs. Residual images in the log-transformed domain}
+\label{fig:real_image_ratio_vs_residual}
+\end{figure}
 
@@
 \begin{align}
-MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
-MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
-MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
-MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
+MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
+MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
+MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
+MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
 \end{align}
@@
 %\end{eqnarray}
+
+As qualititative visual evaluation is subjective by nature,
+	quantitative metrics and measurements are preferred.
+Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
+When ground-truth is available, 
+	either in simulated experiments or in homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated values and its true values.
+
+In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
+The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be think of as the level of noise being removed by speckle filtering process.
+Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) is normally known or can be estimated reasonably well.
+Thus the base MSE level which also a measure of the speckle noise level can also be estimated.
+Naturally, the speckle filter should remove as much noise as possible, 
+	while it also should not remove more variations than that caused by the speckle noise.
+%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base
+
+\section{Evaluating Speckle Filters on Homogeneous Areas}
+\label{sec:eval_homo}
+
+In this section, the methodology to evaluate speckle filters on homogeneous area in log-transformed domain is illustrated.
+Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
+Then the filters are traditionally compared by measuring its speckle suppression power using the ENL index.
+Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
+Subsection \ref{sec:homogeneous_theoretical} gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
+The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.
 
@@
 
-The finding here is also consistent with other independent results where, Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
+The finding here is also consistent with other independent results where, 
+	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
 	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ to evaluate scene heterogeneity.
@@
 \centering
-\begin{tabular}{c|c|r|r|r}
-Filter & Set & Log-Variance & ENL (Estimated) & Avg Intensity \\
+\begin{tabular}{c|c|r|c|r}
+Filter & Set & Log-Variance & $\hat{L}_{est}$ & Avg Intensity \\
 \hline
@@
 
-For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
-First, several test patterns is created to simulate and determine the performance of various speckle filters.
-Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
-As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.
-
-We believe that the qualitative requirement of speckle suppression can be quantified as the variance in log-transformed domain. 
-The visual requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservations and speckle suppression.
-These smaller requirements are equivalent to the bias and variance evaluation of statistical estimator.
+%For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
+%First, several test patterns is created to simulate and determine the performance of various speckle filters.
+%Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
+%As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.
+
+In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
+From statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
+Because the log-transformation convert heteroskedastic SAR speckle into homoskedastic distribution model, 
+	the MSE in log-transformed domains is prefered to the MSE in original SAR domain.
+Experimentally, on clear-cut simple target-background patterns, the results that followed indicate that
+	the lower the MSE achievable by a speckle filter
+	the better feature preservation performance recorded for its output.
+
+%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in log-transformed domain. 
+The general requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservation and speckle suppression.
+In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of statistical estimators.
 Overall, while the MSE index combines the measurements of bias and variance evaluation, 
 	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC curve.
-We show experimentally that the MSE inversely correlated with the AUC index, for all of the simulated patterns.
-
-Since we expect the filters to be consistently behaved in the log-transformed domain, then as we repeat a pattern multiple times, the histograms of target and background areas can be obtained.
+We show experimentally that MSE inversely correlates with the AUC index, for all of the simulated patterns.
+
+Since the filters are expected to be consistently behaved in the log-transformed domain, then as we repeat a pattern multiple times, the histograms of target and background areas can be reliably obtained.
 %They are expected to be consistent in log-transformed domain.
 The target and background can then be seperated using a simple threshold based classification model.
-We judge the separability of the two stochastic populations by the standard ROC, and the quantitative metric of Area Under the ROC Curve (AUC) can then be used as an evaluation metric.
-
-The types of pattern created here are: point targets, line targets, edge targets and a heterogeneous scene.
+The separability of the two stochastic populations are judged by the standard ROC, 
+	and the quantitative and normalized metric of Area Under the ROC Curve (AUC) can then be used as an evaluation metric.
+
+The types of pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous check board scene. 
 These test patterns could, of course, be included into a larger composite test image. 
-However we would prefer to highlight the results separately for each individual area.
+%However we would prefer to highlight the results separately for each individual area.
+However, they are kept seperated to allow easier analysis of the results.
 All patterns are limited to two class of ground-truth: background and target areas. 
@@
 \begin{tabular}{c}
-	\subfloat[Line: each line is 2 pixel wide, separated by 6 pixels background]{
+	\subfloat[Line: each line is 2 pixels wide, separated by 6 pixels background]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[Edge: each stripe is 4 pixel in width]{
+	\subfloat[Edge: each stripe is 4 pixels in width]{
 		 \epsfxsize=1.5in
@@
 	} \\
-	\subfloat[Point: each point is a $2 \times 2$ squares spacing 4 pixels apart]{
+	\subfloat[Point: each point is a $2 \times 2$ square spacing 6 pixels apart]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[Checker board: the squares are 2 pixel wide each side]{
+	\subfloat[Checker board: the squares are 4 pixels wide each side]{
 		 \epsfxsize=1.5in
@@
 
-Large patches of these patterns ($512 \times 512$) are first corrupted with single look noise, and then the filters are applied onto these noised images.
-From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} show thats feature preservation can be evaluated by examining the separability of the two background and target populations.
-We visualize the separability of the two histograms by plotting the standard Receiver Operating Curve (ROC) and we measure it by computing the Area Under this Curve (AUC) index.
+Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle, and then the filters are applied onto these noised images.
+From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be evaluated by examining the separability of the two background and target populations.
+The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
+	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
+	and is measured by computing the Area Under these Curves (AUC).
 
@@
 		 \epsffile{src/heterogenous_patterns.edge.none.fi.jpg.eps} 	
-		 \label{amplitude}
+		 \label{fig:hetero_patterns_roc_auc:amplitude}
 	} 
@@
 		 \epsffile{src/heterogenous_patterns.edge.kuan.fi.jpg.eps} 	
-		 \label{intensity}
+		 \label{fig:hetero_patterns_roc_auc:intensity}
 	} \\
@@
 		 \epsffile{src/heterogenous_patterns.histograms.edge.none.fi.png.eps} 	
-		 \label{amplitude}
+		 \label{fig:hetero_patterns_roc_auc:hist_unfiltered}
 	} 
@@
 		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.fi.png.eps} 	
-		 \label{intensity}
+		 \label{fig:hetero_patterns_roc_auc:hist_kuan_filtered}
 	}  \\
-	\subfloat[ROC AUC: Unfiltered]{
+	\subfloat[ROC: Unfiltered]{
 		 \epsfxsize=1.5in
@@
 		 \epsffile{src/heterogenous_patterns.roc_auc.edge.none.fi.png.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[ROC AUC: Kuan Filtered]{
+		 \label{fig:hetero_patterns_roc_auc:roc_unfiltered}
+	} 
+	\hfill	
+	\subfloat[ROC: Kuan Filtered]{
 		 \epsfxsize=1.5in
@@
 		 \epsffile{src/heterogenous_patterns.roc_auc.edge.kuan.fi.png.eps} 	
-		 \label{intensity}
+		 \label{fig:hetero_patterns_roc_auc:roc_kuan_filtered}
 	} 
@@
 %}
-\caption{Target and Clutter Separability: ROC and AUC indices}
+\caption{Target and Clutter Separability: Histograms and resulting ROC Curve visualisation}
 \label{fig:hetero_patterns_roc_auc}
@@
 
-From a detailed analysis point of view, Fig. \ref{fig:hetero_patterns_mse} shows how the MSE is related to the histograms' capability to seperate.
-In pre-filtered images, subfigures \ref{fig:hetero_patterns_mse}(c and d), there is no bias error.
+Detailed investigation on figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
+	can help to understand how the MSE is related to the histograms' capability to seperate.
+In pre-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error.
 Then the seperability of clutter and target populations depends only on the variance of the additive noise. This variance is visualized as the horizontal spread of the histograms.
-Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) the better the separation capability can be.
-
-In post-filtered images (subfigures \ref{fig:hetero_patterns_mse}(d and f), the situation is more complicated.
+Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) the better the separation capability.
+
+In post-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and \ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
 Here, besides the effect of the histogram spread, one also needs to take into account bias error.
-Sub fig. \ref{fig:hetero_patterns_mse}(d) show that the Kuan filter, and in fact all of the other filters (whose plots are not reproduced here), introduces a bias error.
+Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of Kuan filter, and in fact all the outputs of all other filters (whose plots cannot be presented here, due to space constraints), introduces bias errors.
 Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are always over-estimated.
-This is probably due to the entropy reduction effect of speckle filters, and apparently, assuming that the variances are fixed, the lesser these bias errors, the better the separation capability.
+This is probably due to the entropy reduction effect of speckle filters.
+Apparently, assuming that the variances are fixed, the lesser these bias errors, the better the separation capability.
 
 %Also the speckle suppression is related to the measured variance.
-Thus we believe: the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
-In fact, table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
-We note that the MSE in inversely correlated to this separability index, suggesting that the lower MSE achivable by the filters would lead to better feature preservation in general.
+Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
+In fact, Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
+It shows that the MSE in inversely correlated to this separability index.
+The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
+The results suggest that the lower MSE achivable by the filters would lead to better feature preservation in general.
 
@@
 		 \epsffile{src/heterogenous_patterns.edge.none.gt.jpg.eps} 	
-		 \label{amplitude}
+		 \label{fig:hetero_patterns_mse:amplitude}
 	} 
@@
 		 \epsffile{src/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
-		 \label{intensity}
+		 \label{fig:hetero_patterns_mse:intensity}
 	} \\
@@
 		 \epsffile{src/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
-		 \label{amplitude}
+		 \label{fig:hetero_patterns_mse:unfiltered}
 	} 
@@
 		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
-		 \label{intensity}
-	}  %\\
-%	\subfloat[MSE: Unfiltered]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{src/heterogenous_patterns.mse_histogram.edge.none.gt.png.eps} 	
-%		 \label{amplitude}
-%	} 
-%	\hfill	
-%	\subfloat[MSE: Kuan Filtered]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{src/heterogenous_patterns.mse_histogram.edge.kuan.gt.png.eps} 	
-%		 \label{intensity}
-%	} 
-\end{tabular}
-%}
-\caption{MSE: Bias Error and Variance Error}
-\label{fig:hetero_patterns_roc_auc}
+		 \label{fig:hetero_patterns_mse:kuan_filtered}
+	}  
+\end{tabular}
+\caption{Bias Error Investigation: Images and Histograms Visualisation}
+\label{fig:hetero_patterns_mse}
 \end{figure}
@@
 \hline
-
-%edge & unfiltered & 0.8492 & 4.1557 & 1.4e-33\\
-%edge & frost & 0.8858 & 1.0889 & 5.8681\\
-%edge & boxcar & 0.9121 & 0.9717 & 5.3482\\
-%edge & map & 0.9168 & 2.0949 & 1.9044\\
-%edge & kuan & 0.9423 & 0.8222 & 4.5087\\
-%edge & lee & 0.9543 & 0.8278 & 3.3109\\
-%\hline
-%line2 & unfiltered & 0.8499 & 4.1306 & 1.7e-33\\
-%line2 & frost & 0.8926 & 1.0901 & 5.8411\\
-%line2 & map & 0.8945 & 2.0882 & 1.8861\\
-%line2 & boxcar & 0.9181 & 0.9733 & 5.3236\\
-%line2 & lee & 0.9421 & 0.8228 & 3.2832\\
-%line2 & kuan & 0.9438 & 0.8058 & 4.4654\\
-%\hline
-%point & unfiltered & 0.8479 & 4.1142 & 1.9e-33\\
-%point & map & 0.8616 & 1.7622 & 2.0999\\
-%point & frost & 0.8991 & 0.6649 & 5.1823\\
-%point & lee & 0.9105 & 0.6681 & 3.1121\\
-%point & boxcar & 0.9369 & 0.5842 & 4.6936\\
-%point & kuan & 0.9492 & 0.5192 & 3.9910\\
-%\hline
-%checker & unfiltered & 0.8502 & 4.1282 & 1.4e-33\\
-%checker & frost & 0.7598 & 1.6317 & 6.6242\\
-%checker & boxcar & 0.8110 & 1.4516 & 6.0471\\
-%checker & kuan & 0.8736 & 1.1765 & 5.0167\\
-%checker & map & 0.8842 & 2.5391 & 1.6571\\
-%checker & lee & 0.9058 & 1.0927 & 3.4421\\
-%\hline
 \end{tabular}
@@
 
-In this section our conjecture of using MSE in log-transformed domain to find the most suitable speckle filter for any given SAR images are described.
+In this section our conjecture of using MSE in log-transformed domain to find the most suitable speckle filter for practical real-captured SAR images is described.
+In these scenarios, the ground-truth and hencem the true MSE is not available.
+Then only the residential MSE is computable.
+Assumming the level of speckle noise (e.g. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
+Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
+This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters in any captured SAR images, 
+	where the ground-truth and hence true MSE is not available.
+Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its removed variation being closest to the inherent speckle noise.
+
+Experimental results are presented as empirical evidence supporting the conjecture.
 The experiments in the previous sections are repeated on SLC SAR images 
 	which are simulated from given ground-truth aerial images. 
-Experimental results are presented as empirical evidence supporting the conjecture.
-The a heuristic rule is that 
-	if the best filtered results are those with minimal MSE 
-	then just by observing the residual MSE, 
-	the observable measure of these results will also achieve 
-		being the closest to the MSE of the inherent noise.
-This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters in any captured SAR images, 
-	where the ground-truth and hence true MSE is not available.
-Besides using visual evaluation to validate the conjecture, 
-	the full justification of this conjecture is outside the scope of this paper.
-
-Real images however are more complex than the patterns illustrated above. 
+%The a heuristic rule is that 
+%	if the best filtered results are those with minimal MSE 
+%	then just by observing the residual MSE, 
+%	the observable measure of these results will also achieve 
+%		being the closest to the MSE of the inherent noise.
+%Besides using visual evaluation to validate the conjecture, 
+%	the full justification of this conjecture is outside the scope of this paper.
+%Real images however are more complex than the patterns illustrated above. 
 We also apply the filters on simulated SAR images, built by adding Single Look Noise into various aerial images. 
@@
 \hline
-vietnam rural	& none		& 4.1174	& 3.9e-35\\
-vietnam rural	& pde			& 3.8022	& 0.0368\\
-vietnam rural	& lee			& 0.4984	& 3.2555\\
-vietnam rural	& frost		& 0.3490	& 4.6856\\
-vietnam rural	& kuan		& 0.3396	& 3.6877\\
-vietnam rural	& boxcar	& 0.3107	& 4.2328\\
-\hline
-hanoi suburb	& none		& 4.1321	& 4.1e-35\\
-hanoi suburb	& pde			& 3.8004	& 0.0391\\
-hanoi suburb	& lee			& 0.5261	& 3.2598\\
-hanoi suburb	& frost		& 0.3811	& 4.7427\\
-hanoi suburb	& kuan		& 0.3619	& 3.7270\\
-hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
+Vietnam rural	& none		& 4.1174	& 3.9e-35\\
+Vietnam rural	& pde			& 3.8022	& 0.0368\\
+Vietnam rural	& lee			& 0.4984	& 3.2555\\
+Vietnam rural	& frost		& 0.3490	& 4.6856\\
+Vietnam rural	& kuan		& 0.3396	& 3.6877\\
+Vietnam rural	& boxcar	& 0.3107	& 4.2328\\
+\hline
+Hanoi suburb	& none		& 4.1321	& 4.1e-35\\
+Hanoi suburb	& pde			& 3.8004	& 0.0391\\
+Hanoi suburb	& lee			& 0.5261	& 3.2598\\
+Hanoi suburb	& frost		& 0.3811	& 4.7427\\
+Hanoi suburb	& kuan		& 0.3619	& 3.7270\\
+Hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
 \hline
@@
 
-In real SAR captured images, the radiometric ground-truth normally is not available.
-The most common way to evaluate speckle filters then is by qualitative visual evaluation.
-A more analytical method is to investigate the ratio images between the filtered output and the noisy input images.
-Since logarithmic transformation convert these ratio into substractive residual
-	, which are consistent, residual analysis can be used to analyse and evaluate the performance of speckle filters.
-To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig.
-\ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
-``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is extremely subjective.
-
-Our qualititative conclusion is that
-	a. it is apparently easier to notice the ``visible structure'' being removed in the residual noise pictures than the ratio mages, and
-	b. even so, the above conclusion is at best quite subjective.
-Thus to compare the filters against each other, 
-	quantitative measures are preferred.
-
-\begin{figure}
-\begin{tabular}{c}
-	\subfloat[Original Patch]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{src/heterogenous_real.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[Boxcar Filtered Result]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{src/heterogenous_real.boxcar.eps} 	
-		 \label{intensity}
-	} \\
-	\subfloat[Ratio: Filtered / Original]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{src/heterogenous_real.ratio2.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[Ratio: Original / Filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{src/heterogenous_real.ratio1.eps} 	
-		 \label{intensity}
-	}  \\
-	\subfloat[Log Residual: Filtered - Original]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{src/heterogenous_real.residual2.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[Log Residual: Original - Filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{src/heterogenous_real.residual1.eps} 	
-		 \label{intensity}
-	} 
-\end{tabular}
-\caption{Error Images: Ratio vs. Residual}
-\label{fig:real_image_ratio_vs_residual}
-\end{figure}
-
 Table \ref{tab:mse_in_real_image} tabulate the computed MSE of the ``removed'' additive noise.
@@
 \begin{tabular}{c|r|r}
-filter & $MSE_{noise}$ & $MSE_{benchmark}$\\
+Filter & $MSE_{residual}$ & $MSE_{benchmark}$\\
 \hline
@@
 \hline
-SLC unfiltered MSE & 4.1167 & 4.1167 
+none & $MSE_{base}$ & 4.1167 
 \end{tabular}

### 2012-07-31 article.tex
auto

@@
 Nanyang Technological University, Singapore,}% <-this % stops a space
-%\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
+\thanks{The authors wish to thank Dr.
+Ken-Yoong Lee and Dr.
+Timo Brestchneider of EADS InnovationWorks Singapore for initial discussions and for providing RADARSAT2 images used in this paper.
+}% <-this % stops a space
 \thanks{Manuscript received ?, 2012; revised ?.}}
@@
 
-\caption{The correlation between MSE and AUC measure of feature discrimination (inside the brackets are corresponding p-values)}
+\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
 \label{tab:mse_auc_corr_coeff}
@@
 Then only the residential MSE is computable.
-Assumming the level of speckle noise (e.g. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
+Assumming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
 Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
@@
 Experimental results are presented as empirical evidence supporting the conjecture.
-The experiments in the previous sections are repeated on SLC SAR images 
+The experiments in the previous sections are repeated on Single-Look SAR images 
 	which are simulated from given ground-truth aerial images. 
@@
 %Real images however are more complex than the patterns illustrated above. 
-We also apply the filters on simulated SAR images, built by adding Single Look Noise into various aerial images. 
+Then the filters are applied onto the simulated SAR images. 
 Fig. \ref{fig:real_simulated_images} illustrates some of the images used for our experiments.
@@
 		have the its observable residual MSE value being closest to the noise MSE (4.1167 in our case).
-We validate the idea by qualititative evaluation, an example of which is presented in Fig. \ref{fig:real_simulated_image_results}.
-The same conclusion can be found in our experiments with more images, which cannot be shown here due to space limitation.
+%We validate the idea by qualititative evaluation, an example of 
+The conjecture is also validated using visual evaluation, an example of
+	which is presented in Fig. \ref{fig:real_simulated_image_results}.
 
@@
 \hline
-Vietnam rural	& none		& 4.1174	& 3.9e-35\\
+Vietnam rural	& none		& 4.1174	& 4e-35\\
 Vietnam rural	& pde			& 3.8022	& 0.0368\\
@@
 \hline
-Hanoi suburb	& none		& 4.1321	& 4.1e-35\\
+Hanoi suburb	& none		& 4.1321	& 4e-35\\
 Hanoi suburb	& pde			& 3.8004	& 0.0391\\
@@
 \begin{tabular}{c}
-	\subfloat[Simulated GrayScale Image (ground-truth)]{
+	\subfloat[Ground-Truth Image ]{
 		 \epsfxsize=1.6in
@@
 
+The results from the experiments in previous sections can also be used to validate the use of residual and benchmark MSE.
+The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly correlated with feature classification capability, measured by the standard AUC index.
+
+The filters are also applied onto a real RADARSAT 2 image.
+In this case, since the ground-truth is not available, 
+	only visual evaluation can be used to validate our conjecture.
 Table \ref{tab:mse_in_real_image} tabulate the computed MSE of the ``removed'' additive noise.
@@
 Fig. \ref{fig:real_image_results} qualitatively confirmed our evaluation.
+The conclusions in this can be found in further experiments with more images, 
+	which cannot be shown here due to space limitation.
 

### 2012-08-12 article.tex
Hai

@@
 The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
-The estimators are typically evaluated based on the bias and variance properties of their estimates; 
-	with lower bias and / or lower variance, hence lower MSE, indicating better accuracy.
+Estimators are typically evaluated based on the bias and variance properties of their estimates; 
+	with lower bias and / or lower variance (hence lower MSE) indicating better accuracy.
 Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-Also, due to the stochastic nature of SAR processing, hence, of the underlying simulation process, 
+Also, due to the stochastic nature of SAR processing, as well as simulating process, 
 	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.
@@
 Our survey of SAR speckle filter research, however, indicates 
-	a different picture from the standard practice of this statistical framework, 
+	a different picture from the standard practice of the statistical framework, 
 	specifically, in the stage of performance evaluation. 
@@
 	bias and variance evaluation may not be the most useful measures. 
-Thus, the standard evaluation metric of mean-squared-error is not applicable,
-	as alternative evaluation criteria are proposed.
+Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
+	prompting alternative evaluation criteria to be proposed.
 In fact, a survey of relevant literature fails to reveal 
@@
 
-The common theme is that each newly proposed speckle filter tends to be published along with a customised methodology for evaluating its own performance.
+The common theme is that each newly proposed speckle filter tends to be published along with a methodology for evaluating its performance.
 Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
-While such visual comparison is useful, as an evaluative methodology, regretably it lacks scientific objectivity. 
+While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
 Some papers do present quantitative measurements, 
 	however  due to the lack of a standardized performance criteria, 
-	the evaluation metrics can change eccentrically from one paper to the next.
-
-In this paper, we propose the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
-The rest of this paper is structured as follows.
-While Section \ref{sec:lit_review} briefly surveys related work in published literature, Section \ref{sec:log_transform} provides a quick discussion of the Logarithmic Transformation.
+	the evaluation metrics can change significantly from one paper to the next.
+
+In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
+The paper is structured as follows.
+Section \ref{sec:lit_review} briefly surveys related work in the published literature, Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
 Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
@@
 Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
-	to choose the most suitable speckle filter for a given satellite-captured SAR image.
+	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
 %And the last section provides our discussion together with our concluding remarks.
-Finally, section \ref{sec:discussion} discusses the findings and presents concluding remarks.
+Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.
 
@@
 %	related to the topic of evaluating SAR speckle filters.	
-It is customary to divide the evaluation of speckle filters into two scenarios:
-	homogeneous areas and heterogeneous scenes.
-In homogeneous areas,
+It is customary to divide the performance evaluation of speckle filters across the two classes of 
+	homogeneous and heterogeneous regions.
+Across homogeneous areas,
 	speckle filters are expected to estimate with negligible radiometric bias.
-Thus evaluating speckle filters on homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
-By contrast, the methodologies used to evaluate speckle filters in heterogeneous areas are much more complex, probably due to the following difficulties.
-The first difficulty is to find out an absolute ground-truth against which quantitative criteria can be measured.
-The second challenge is to come up with a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
-In this section, various published work in evaluating SAR speckle filters are reviewed.
-
-The metric to evaluate speckle filter should be relevant to the normal usage of such filters.
-The general requirement for a speckle filter in SAR processing frameworks is that its application should allow easier measurement, detection and classification of the underlying radiometric features.
+Thus evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
+By contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, due in part to the following difficulties.
+The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
+The second challenge is then to define a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
+%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.
+
+In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
+
+Furthermore, its application in a SAR processing framework should allow an improvement in the measurement, detection or classification of the underlying radiometric features.
 %As shown in the subsequent section, 
@@
 These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
-The Mean-Squared-Error evaluation is a combined evaluation of bias and variance error evaluations, and hence is capable of evaluating the general requirement of speckle filtering.
+The MSE evaluation is a combined evaluation of bias and variance error, and is therefore capable of evaluating the general requirement of speckle filtering.
 %Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.
 
-For homogeneous scenes, 
-	where the underlying radiometry is assumed to be constant, 
+For homogeneous scenes where the underlying radiometry is assumed to be constant, 
 	the filtered results, statistically speaking, are considered to be samples of 
@@
 %Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
-Then, from the logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
+From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
 	%are expected to estimate with no radiometry bias. 
@@
 
-A metric that can be used to detect radiometric distortion is the ratio between the estimated number and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
+One metric that can be used to detect radiometric distortion is the ratio between the estimated and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
 A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
@@
 
-A few metrics have been used to evaluate speckle suppression power.
-The most common measure is the Equivalent Number of Looks index 
+Several metrics have been developed to evaluate speckle suppression power.
+The most common measure is the Equivalent Number of Looks (ENL) index 
 $ENL=avg(I)^2/var(I)$
@@
 Real-life and practical images, however, are not homogeneous.
-Thus there are a few associated difficulties in evaluating speckle filters in heterogenous scenes.
+Thus there are a few associated difficulties in evaluating speckle filters over heterogenous scenes.
 %and there are many proposed methods of evaluating speckle filters in such areas. 
@@
 The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
-It is trivially easy to estimate the underlying radiometric co-efficient if an area is known to be homogeneous
-However, without simulation or access to lab environment ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters' estimation).
+It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous
+However, without simulation or access to solid ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters estimation).
 
@@
 We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
-The ratio image then becomes a simple substraction image.
+The ratio image then becomes a simple subtraction image.
 The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).
@@
 This is the second difficulty in evaluating speckle filters for heterogenous scenes.
-Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional level.
+Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional levels.
 In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa.
@@
 Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
-However since SAR data is heteroskedastic, which violaes the assumptions of Gauss Markov theorem, the use of MSE is not straightforward. 
+However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, the use of MSE is not straightforward. 
 Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation.
-Others have suggest the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.
+Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.
 
@@
 	the requirements of radiometric preservation and speckle suppression for speckle filters.
-Before the details of our evaluation methodology is presented, 
+Before the details of our evaluation methodology is presented and discussed, 
 	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
@@
 
-SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scaterring components, each reflecting from different and distributed elementary scaterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}.
-These interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.
+SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components, each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}.
+This interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.
 The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.
@@
 
-It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
-These relationships evidently manifest a mutiplicative nature. 
-In fact, this condition has long been noted, but from different perspectives, in various SAR models including multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.
+It is then trivial to prove that amplitude and intensity are simply scaled versions of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
+These relationships evidently manifest a multiplicative nature. 
+In fact, this condition has long been noted, but from different perspectives, in various SAR models including the multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.
 
 If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process.
-Consequently, the population expected mean and variance of the four distributions are given in table \ref{tbl:orginal_sar_avg_var}
+Consequently, the population expected mean and variance of the four distributions are given in Table \ref{tbl:orginal_sar_avg_var}.
 
@@
 From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean.
-In the context of speckle filtering, table \ref{tbl:orginal_sar_avg_var} indicates the vicious circle: estimating variance is equal to estimating the mean and is equivalent to the main problem, ie.
+In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; estimating variance is equal to estimating the mean and is equivalent to the main problem, ie.
 estimating the unknown parameter $\sigma$.
 
-The formulas above has long been noted.
-In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al has noted the ratio of expected standard deviation to mean is a constant in both cases (ie.
+The formulas above have long been noted.
+In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both cases (ie.
 $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$).
@@
 
-\subsection{ The effects of Heteroskedasticity on Speckle Filters }
+\subsection{The effects of Heteroskedasticity on Speckle Filters}
 
@@
 %That is because: 
-Eventhough, the statistical model within individual resolution cell is well established, the applicability of its models is restricted to homogenous areas. 
+Even though the statistical model within individual resolution cells is well established, the applicability of its models is restricted to homogenous areas. 
 Practical images, however, are heterogenous.
 Crucially it is this spatial variation that is of high interest.
-This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.
+This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and subsequently what to do in the case of heterogeneity.
 
@@
 Unfortunately, by definition heteroskedasticity leads to inconsistent measures of distance. 
-This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods are believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods for SAR classification to underperform.
+This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods are
+ believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods for SAR classification to underperform.
 
@@
 
-In this paper, we propose using base-2 logarithmic transformtion of SAR orignal random variables.
-Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet it maintains the ability to transform heterskedactic speckle into a homoskedastic relationship.
+In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data.
+Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet maintains an ability to transform heterskedactic speckle into a homoskedastic relationship.
 Thus the original variables become:
@@
 
-Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as follows:
+Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variables as follows:
 
@@
 
-Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant.
+Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant.
 Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$
@@
 
-This result is consistence with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}.  
-The main difference would be the use of base-2 logarithm which is prefered here for faster computation.
-
-Table \ref{tbl:sar_variables_properties} summarize the discussion so far. 
-It can be seen that while the original data, especially intensity values, should be prefered for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast.
-Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (inculding wavelets) and computational (including artificial neural network) techniques into SAR data.
+This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. The main difference would be the use of base-2 logarithm which is prefered here for faster computation.
+
+Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
+It can be seen that while the original data, especially intensity values, should be preferred for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast.
+Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (including wavelets) and computational (including artificial neural network) techniques into SAR data.
 
@@
 
-Noting the results from previous section, the pdf for these variable can be trivially given as
+Noting the results from the previous section, the pdf for these variable can be trivially given as
 
@@
 
-From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider the random variable defined as the contrast between two measured samples, in the log-transformed domain:
+From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider a random variable defined as the contrast between two measured samples, in the log-transformed domain:
 
@@
 
-It could be seen that, in the log-transformed domain, not only the expected mean of observable variance is constant, the sampling distribution of this random variable is independent of $\sigma$. 
+It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance constant but the sampling distribution of this random variable is independent of $\sigma$.
 We have seen this analytically for two sample variances. 
-For larger number of samples, Monte-Carlo simulation is used to visualise the PDF of sample variances.
-
-In summary, a few measures of distance is shown to be consistent, which agrees with the consistent sense of variance / deviation and homoskedasticity.
-The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use as illustrated in our kMLE speckle filter.
-The consistent sense of contrast can be used to test if the any pair of measured data point belong to the same class of scatterrer, 
-	and it may also explain why in original SAR domain the ratio based detector / classifier is prefered to the differential measures, which is not consistent. 
+For a larger number of samples, Monte-Carlo simulation can be used to visualise the PDF of sample variances.
+
+In summary, a few measures of distance are shown to be consistent, which agree with the consistent sense of variance / deviation and homoskedasticity.
+The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use this way is illustrated in our kMLE speckle filter.
+The consistent sense of contrast can be used to test if any pair of measured data points belong to the same class of scatterer. It may also 
+explain why, in the original SAR domain, the ratio based detector / classifier is prefered to differential measures, which are not consistent. 
 An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
-The consistent sense of contrast also gives rise to the consistent measure of variance, which can be used to test if a group of pixel can form an homogenous area.
+The consistent sense of contrast also gives rise to a consistent measure of variance, which can be used to test if a group of pixels can form a homogenous area.
 This is applied in a clustering algorithm described in \cite{Le_2010_ACRS}.
@@
 Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and SAR speckle filtering process.
-The ``SAR Processor'' block indicates either of the following processes.
+The ``SAR processor'' block indicates that either of the following processes is occuring.
 First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded in $\tilde{X}$.
@@
 	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
-Traditional method is to investigate the ratio images between the filtered output and the noisy input images.
+A traditional method is to investigate the ratio images between the filtered output and the noisy input images.
 Since logarithmic transformation convert these ratio into substractive residual
@@
 \ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
-``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is extremely subjective.
+``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is of course itself a subjective one.
 
@@
 MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
-MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
+MSE_{noise} = MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
 MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
@@
 As qualititative visual evaluation is subjective by nature,
-	quantitative metrics and measurements are preferred.
+	quantitative metrics and measurements are preferred, if relevant and possible.
 Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
 When ground-truth is available, 
-	either in simulated experiments or in homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated values and its true values.
+	either in simulated experiments or over homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated and true values.
 
 In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
-The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be think of as the level of noise being removed by speckle filtering process.
-Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) is normally known or can be estimated reasonably well.
-Thus the base MSE level which also a measure of the speckle noise level can also be estimated.
+The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
+Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be estimated reasonably well.
+Thus the base MSE level which is also a measure of the speckle noise level, can also be estimated.
 Naturally, the speckle filter should remove as much noise as possible, 
@@
 
-In this section, the methodology to evaluate speckle filters on homogeneous area in log-transformed domain is illustrated.
+In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is illustrated.
 Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
-Then the filters are traditionally compared by measuring its speckle suppression power using the ENL index.
-Consequently in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other component, namely, variance evaluation. 
-Subsection \ref{sec:homogeneous_theoretical} gives theoretical justification for our methodology where variance evaluation is shown to be mathematically related to the ENL index.
-The last subsection details how variance evaluation in log-transformed domain can be employed to evaluate the levels of speckle in homogeneous area.
+Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
+Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other components, namely, variance evaluation. 
+Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance methods of evaluation are shown to be mathematically related to the ENL index.
+The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle over homogeneous areas.
 
@@
 
-In this subsection, we show that the variance in log-transformed domain is equationally related to the universal ENL index. 
+In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL index. 
 Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
-Assuming the filters achieves negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
+Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
 	then the MSE evaluation reduces to variance evaluation.
-That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in log-transformed domain.
+That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in the log-transformed domain.
 
@@
 %Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
-Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variable as: 
+Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variables as: 
 \begin{equation}
@@
 \end{equation}
-Thus, the Equivalent Number of Look, i.e. L, can be estimated as:
+Thus the ENL, i.e. $L$, can be estimated as:
 \begin{equation}
@@
 
-To verify the above analysis an experiment is carried out.
-In the experiment, a $512\times512$ homogeneous area is generated and corrupted with Single Look SAR-speckle PDF. 
-Different multi-look processing filters are then applied to the patch. 
-The observable variance in log-transformed domain is recorded and 
-	the ENL is estimated from Equation \ref{eqn:enl_analytic} for each simulation.
-We run the simulation multiple times and table \ref{tab:enl_in_log_domain} report the results in mean and standard deviation.
+The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and corrupted with single look SAR-speckle PDF. 
+Different multi-look processing filters are then applied to the image patch. 
+The observable variance in the log-transformed domain is recorded, and 
+	 ENL estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
+The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms of mean and standard deviation.
 The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
 	together with the analytical values from Eqn. \ref{eqn:perf_index_analytic}.
-The experimental results evidently validate the analysis given above.
-It also shows that: 
+These experimental results evidently validate the analysis given above.
+They also shows that 
 	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect, 
-	since ENL is supposed to be an integer, its conclusions are unambigous.
+	since ENL is supposed to be an integer, the value obtained actually corresponds very closely with the nearest correct integer result.
 
@@
 
-The finding here is also consistent with other independent results where, 
+The finding here may help to explain other seemingly unrelated results where, 
 	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
@@
 Fig.
-\ref{fig:log_consistency_filters} shows that the standard filters (Lee, Kuan, Frost and Gamma MAP) preserve this consistency in their filtered output.
-Intuitively, the boxcar filter is actually multi-look processing thus it also preserve the consistent property.
-This consistency will also lead to the consistent sense of distance described earlier and is significant because it is the tell-tale sign of the consistent contrast and variance.
-This ensures applicability of various target detection/classification algorithms which employ the statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.
+\ref{fig:log_consistency_filters} shows that all of the standard filters (Lee, Kuan, Frost and Gamma MAP) preserve this consistency in their filtered output.
+Intuitively, the boxcar filter is actually similar to multi-look processing, thus it also preserve the consistency property.
+This consistency will also lead to the consistent sense of distance described earlier, and is significant because it is the tell-tale indicator of the consistent contrast and variance.
+This ensures applicability of various target detection/classification algorithms which employ statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.
 
@@
 
-Table \ref{tab:homogeneous_performance_filters} gives a quantitative comparison among the filters.
-It shows that the filters can all preserves the underlying radiometric values, while their speckle suppression power can be equivalently measured using either variance in the log-transformed domain, or the standard Equivalent Number of Look index.
+Table \ref{tab:homogeneous_performance_filters} provides a quantitative comparison among the filters.
+It shows that the filters can all preserve the underlying radiometric values, while their speckle suppression power can be equivalently measured using either variance in the log-transformed domain, or the standard ENL index.
 
@@
 In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
-From statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
-Because the log-transformation convert heteroskedastic SAR speckle into homoskedastic distribution model, 
-	the MSE in log-transformed domains is prefered to the MSE in original SAR domain.
-Experimentally, on clear-cut simple target-background patterns, the results that followed indicate that
-	the lower the MSE achievable by a speckle filter
-	the better feature preservation performance recorded for its output.
+From a statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
+Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
+	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
+Experimentally, on clear-cut simple target-background patterns, the results that follow will indicate that
+	the lower the MSE achievable by a speckle filter,
+	the better the feature preservation performance recorded for its output.
 
@@
 Overall, while the MSE index combines the measurements of bias and variance evaluation, 
-	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC curve.
-We show experimentally that MSE inversely correlates with the AUC index, for all of the simulated patterns.
-
-Since the filters are expected to be consistently behaved in the log-transformed domain, then as we repeat a pattern multiple times, the histograms of target and background areas can be reliably obtained.
+	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC Curve (AUC).
+We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.
+
+Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern multiple times, the histograms of the target and background areas can be reliably obtained.
 %They are expected to be consistent in log-transformed domain.
@@
 The separability of the two stochastic populations are judged by the standard ROC, 
-	and the quantitative and normalized metric of Area Under the ROC Curve (AUC) can then be used as an evaluation metric.
-
-The types of pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous check board scene. 
-These test patterns could, of course, be included into a larger composite test image. 
+	and the quantitative and normalized metric of AUC can then be used as an evaluation metric.
+
+The types of pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous checker board scene. 
+These test patterns could, of course, be concatenated into a larger composite test image, although we will consider them as separate images to allow easier analysis of the results.
 %However we would prefer to highlight the results separately for each individual area.
-However, they are kept seperated to allow easier analysis of the results.
-All patterns are limited to two class of ground-truth: background and target areas. 
-We will follow the convention in the radar community where the target is signified by the brighter area of the image. 
+Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention in the radar community where the target is signified by the brighter area of the image. 
 Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.
@@
 From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be evaluated by examining the separability of the two background and target populations.
-The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
-	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
+Subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
+	allows visual evaluation of target and clutter histograms and their separability.
+Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), in subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
 	and is measured by computing the Area Under these Curves (AUC).
+
+%visualizes the two histograms
+%The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
+%	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
+%	and is measured by computing the Area Under these Curves (AUC).
 
@@
 	}  \\
-	\subfloat[ROC: Unfiltered]{
+	\subfloat[ROC: Unfiltered, AUC=0.738]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[ROC: Kuan Filtered]{
+	\subfloat[ROC: Kuan Filtered, AUC=0.885]{
 		 \epsfxsize=1.5in
@@
 
-Detailed investigation on figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
-	can help to understand how the MSE is related to the histograms' capability to seperate.
-In pre-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error.
+Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
+	can help to explain how the MSE is related to the histograms' capability to seperate.
+In pre-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
 Then the seperability of clutter and target populations depends only on the variance of the additive noise. This variance is visualized as the horizontal spread of the histograms.
@@
 Here, besides the effect of the histogram spread, one also needs to take into account bias error.
-Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of Kuan filter, and in fact all the outputs of all other filters (whose plots cannot be presented here, due to space constraints), introduces bias errors.
+Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicate that the output of the Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), also introduce bias errors.
 Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are always over-estimated.
-This is probably due to the entropy reduction effect of speckle filters.
-Apparently, assuming that the variances are fixed, the lesser these bias errors, the better the separation capability.
+This is probably due to the entropy reduction effect of the speckle filters.
+Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.
 
@@
 Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
-In fact, Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
-It shows that the MSE in inversely correlated to this separability index.
+Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
+It shows that the MSE is inversely correlated to this separability index.
 The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
@@
 \end{tabular}
-\caption{Bias Error Investigation: Images and Histograms Visualisation}
+\caption{Bias Error Investigation: Image and Histogram Visualisation}
 \label{fig:hetero_patterns_mse}
@@
 
-In this section our conjecture of using MSE in log-transformed domain to find the most suitable speckle filter for practical real-captured SAR images is described.
-In these scenarios, the ground-truth and hencem the true MSE is not available.
-Then only the residential MSE is computable.
-Assumming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
+In this section, our conjecture of using MSE in the log-transformed domain to find the most suitable speckle filter for practical real-captured SAR images is described.
+In these scenarios, the ground-truth and hence the true MSE is not available.
+Therefore only the residential MSE is computable.
+Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
 Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
-This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters in any captured SAR images, 
+This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters for a captured SAR image, 
 	where the ground-truth and hence true MSE is not available.
@@
 Experimental results are presented as empirical evidence supporting the conjecture.
-The experiments in the previous sections are repeated on Single-Look SAR images 
+The experiments in the previous sections are repeated on single-look SAR images 
 	which are simulated from given ground-truth aerial images. 
@@
 Table \ref{tab:mse_true_noise_log_domain} shows that among the various filters used, 
-	the most suitable filter are also the filter that 
-		have the its observable residual MSE value being closest to the noise MSE (4.1167 in our case).
+	the most suitable filter is also the filter that 
+		has its observable residual MSE value being closest to the noise MSE (4.1167 in the case of this example).
 %We validate the idea by qualititative evaluation, an example of 
@@
 
-The filters are also applied onto a real RADARSAT 2 image.
+The conjecture is also validated in real SAR images.
+Different speckle filters are applied onto a real RADARSAT-2 image.
 In this case, since the ground-truth is not available, 
 	only visual evaluation can be used to validate our conjecture.
-Table \ref{tab:mse_in_real_image} tabulate the computed MSE of the ``removed'' additive noise.
-Apparently all filters still left some noise ``unremoved'', in which case, the higher removed noise MSE would probably suggest a more suitable filter.
-Fig. \ref{fig:real_image_results} qualitatively confirmed our evaluation.
-The conclusions in this can be found in further experiments with more images, 
-	which cannot be shown here due to space limitation.
+Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
+Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE would probably suggest a more suitable filter.
+Fig. \ref{fig:real_image_results} tends to confirm this visually.
+%IVMThe conclusion in this can be found through further experiments with more images, 
+%IVM	which cannot be shown here due to space limitation.
 
@@
 
-Although it is widely known that log transformation transform multiplicative SAR speckle into additive noise, 
+Although it is widely known that log transformation transforms multiplicative SAR speckle into additive noise, 
 	one should note that the noise is not Gaussian.
-In fact, figures presented in previous sections show that 
+In fact, figures presented in the previous sections show that 
 	they are not even centered around the origin. 
@@
 Log tranformation also brings about a few consistent measures of dissimilarity.
-These consistency can be found not only in single-look or multi-look SAR data, 
+This consistency can be found not only in single-look or multi-look SAR data, 
 	but can also be found in filtered data of various ``standard'' speckle filters.
-This is significant probably because it ensures applicability of various target detection/classification algorithms
-	, which exploits these consitent statistical properties, 
+This is significant probably because it ensures the applicability of various target detection/classification algorithms, 
+	which exploit these consistent statistical properties, 
 	into not only pre-filtered data but also post-filtered data as well.
@@
 
-This consistent measures of distance in log-transformed domain could probably have implications beyond speckle filtering.
-For example, in the subsequent tasks of designing target detector or classifier design, 
+This consistent measures of distance in the log-transformed domain could probably have implications beyond speckle filtering.
+For example, in the subsequent tasks of designing target detectors or classifiers, 
 	it is normally desirable to engineer the solution to not only work on single-look or multi-look SAR data,
 	but also be applicable on post-filtered data.
-In such cases, these consistent measures of distance in log-transformed domain could provide a sound theoretical basis.
-In fact, a number of already proposed solutions appears to make use of this feature. 
+In such cases, these consistent measures of distance in the log-transformed domain could provide a sound theoretical basis.
+In fact, a number of already proposed solutions appear to make use of this feature. 
 %(cite here some SAR classification papers)
@@
 Looking backwards, in designing new speckle filters, by ensuring that the filtered output preserves this consistent property,
-	the new speckle filters would be eligible to be used as a pre-processing steps for availble classifiers / detector.
+	the new speckle filters would be eligible to be used as pre-processing steps for availble classifiers / detector.
 
@@
 One could argue that it would not be fair to the judge such filters using the MSE criteria, 
-	which is probably favors the ``standard'' filters.
-While we respect any other criteria that are used, we wish to reiterate two points.
-First, our MSE criteria is closely related to the basic ENL criteria.
-And our experimental results indicates that the ENL measures for such filter (i.e. the pde filter) differ depending on the radiometric values.
-Second, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
+	which tend to favour the ``standard'' filters.
+While we respect any other criteria that are used, we reiterate the two points that firstly
+our MSE criteria is closely related to the basic ENL criteria.
+The experimental results indicated that the ENL measures for such filter (i.e. the pde filter) differ depending on the radiometric values.
+Secondly, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
 The MSE criteria is shown to be related to feature preservation requirements.
 Thus it is relevant towards subsequent target detection / classification processing, 
-	which is believed to be a pretty common subsequent processing step.
-For these two reasons, the MSE criteria is strongly advocated.
+	which is believed to be a relatively common subsequent processing step.
+For these two reasons, the MSE criteria is advocated.
 
 In the experiments above, speckle filters with a $3 \times 3$ sliding window were used, 
-	eventhough we are aware that the normal window size used is much larger. 
-The reasons for maintaining a small window in these tests is that 
-	smaller-sized filters facilitate the use of smaller patterns without too much concern about crosstalk among adjacent targets.
-Secondly, we want to focus on advocating the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
-	and do not wish to advocate which filter is the ``best'' filter. 
-In other words, we are mainly addressing the methodology to evaluate speckle filters, 
-	and not directly addressing the issue of designing speckle filters.
-However, interested filter designers however are invited to download our Matlab evaluation code online to evaluate their designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
+	although we are aware that the normal window size used is much larger. 
+The reasons for maintaining a small window is that 
+	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk among adjacent targets.
+Secondly, we focussed on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
+	and do not wish to advocate a particular ``best'' filter in practice. 
+In other words, we addressed the methodology of evaluating speckle filters, 
+	and did not directly address the design of speckle filters.
+However, interested filter designers are invited to download the Matlab evaluation code used in this paper to evaluate their own designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
 
@@
 %The use of simulation and modelling in speckle filtering research allows for faster simulation and evaluation of different underlying scenarios. 
-The use of small and simple patterns allow detailed analysis can then be done repeatedly and reliably against the stochastic nature of SAR data.% on simulated small data sets without the need of a common real large image that is somehow representative.
-This helps the mapping of qualititative requirements for the speckle removal process into specific and quantitative requirements in the design of speckle filters.
-Its use also provides an absolute ground-truth, a solid base for comparison results.
-
-Its main drawback is that ground truth does not exist in real-captured SAR images.%, there is no ground-truth.
+The use of small and simple patterns allowing detailed analysis can then be done repeatedly and reliably against the stochastic nature of SAR data.% on simulated small data sets without the need of a common real large image that is somehow representative.
+This helps in the mapping of qualitative requirements for the speckle removal process into specific and quantitative requirements in the design of speckle filters.
+Its use also provides an absolute ground-truth, i.e. a solid base for comparison of results across different papers.
+
+The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.%, there is no ground-truth.
 Thus the result extension towards real images is only analogical.
-While the proposed rule is probably heuristics, 
-	the experimental results presented in this paper is evidently and empirically valid,
-	supporting the final conjecture.
+While the proposed rule is heuristic, 
+	the experimental results presented in this paper are shown empirically to be valid.
 
@@
 	different heterogenous patterns exhibits different levels of heterogeneity. 
-Eventhough different measures have been proposed to evaluate scene heterogeneity level or to test homogeneity hypothesis, 
+Even though different measures have been proposed to evaluate scene heterogeneity levels or to test for the homogeneity hypothesis, 
 	for real captured images, where the absolute ground-truth is not available, 
@@
 %Similarly for 
-The patterns used is chosen based on our exeriences and they may affects evaluation results. 
-As different patterns results in different degree in the scale of scene homogeneity / heterogeneity, 
-	and they also appears to affect the performance and ranking of each speckle filters.
+The patterns used are chosen based on our exerience and of course may affects evaluation results. 
+As different patterns result in different degrees in the scale of scene homogeneity / heterogeneity, 
+	and they also appear to affect the performance and ranking of each speckle filters.
 One extreme case is that of perfect homogeneity, where boxcar filters would be the best performer,
-	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that boxcar would actually lose out.
+	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that the boxcar would not perform well.
 %Our work suggest that the performance of speckle filters is probably scene dependent, 
@@
 
-Readers may also find that the idea of matching the most suitable speckle filter with a given scene is a bit foreign.
-In fact, one of our hope before carrying out this study is being able to find ``the single best'' speckle filter.
-In reality, the numbers in our experimental results however do not unanimous advocate a single best filter. 
-In hind-sight, this is probably not to be expected,
-	given that the well known trade off where a power speckle-suppression filter (e.g.
+%IVMReaders may also find the idea of matching the most suitable speckle filter to a given scene to be foreign.
+%IVMIn fact, one hope aim of this study is being able to find ``the single best'' speckle filter.
+%IVMIn reality, the numbers in our experimental results however do not unanimous advocate a single best filter. 
+%IVMIn hind-sight, this is probably not to be expected,
+%IVM	given that the well known trade off where a power speckle-suppression filter (e.g.
 the boxcar filter) would likely to perform poorly in highly heterogeneous scenes, where radiometric preservation becomes more critical.
-Such insight, when coupled with the fuzzy notion of homogeneity as being the special case of generalized heterogeneity, allow us to welcome the idea.
-
-Our current scheme of finding the most suitable speckle filter requires the application of all the filters before a decision is made.
-A probably better alternative is to predict the choice, thus escape such massive requirements of processing.
-Such study, however, is outside the scope of this paper.
+%IVMSuch insight, when coupled with the fuzzy notion of homogeneity as being the special case of generalized heterogeneity, allow us to welcome the idea.
+
+The current scheme of finding the most suitable speckle filter requires the application of all filters before a decision is made, something that may be computationally expensive.
+A possible better alternative would be to predict the choice, escaping such massive requirements of processing.
+This, however, is outside the scope of this paper.
 
@@
 To summarize, speckle filters are generally evaluated using many different qualitative criteria.
-To compare the filters against each other, however, a method is needed to quantify and measure these various qualitative requirements and results.
+To compare the filters against each other, a method is needed to quantify and measure these various qualitative requirements and results.
 Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
@@
 Thirdly, our major practical contribution is to suggest an heuristic rules using the benchmark MSE to find the most suitable speckle filter for any given scene. 
-In short, propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation scenarios, and suggest several test images that may be useful in this regard.
-
-It should also be noted that a similar consistent sense of distance also exists in POLSAR data. 
+In short, we propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation scenarios, and suggest several test images that may be useful in this regard.
+
+It should also be noted that a similar consistent sense of distance also exists in polarimetric SAR (POLSAR) data. 
 Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.

### 2012-09-10 old.article.tex
before submit to TGRS?

@@
 
-%\usepackage[caption=false]{caption}%for captions
+\usepackage[center]{caption}%for captions
 \usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
@@
 %opening
-\title{ SLC SAR speckle filtering using Homoskedastic effects of Logarithmic Transfomation }
+\title{ 
+	Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.
+}
 
@@
 \author{Thanh-Hai~Le,
-        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
-	Brian~Quang-Huy~Nguyen,
-	Ken-Yoong~Lee, 
-	and Timo~Brestchneider % <-this % stops a space
-\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen and Ian~McLoughlin are with the School of Computer Engineering, 
-Nanyang Technological University, Singapore,}% <-this % stops a space
-\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
-\thanks{Manuscript received ?, 2010; revised ?.}}
+        Ian~McLoughlin, 
+	Quang-Huy~Nguyen,
+	Chan-Hua~Vun%
+	%Ken-Yoong~Lee, 
+	%and Timo~Brestchneider % <-this % stops a space
+\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+\thanks{Manuscript received ?, 2012; revised ?.}}
 
-\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, April~2010}%
-{ Le \MakeLowercase{\textit{et al.}}: SLC SAR speckle filtering using Homoskedastic effects of Logarithmic Transfomation }
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}: Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters }
 
@@
 \begin{abstract}
-This paper note the ability of Logarithmic Transformation to convert heteroskedasticity of SAR single look data to homoskedastic values.
-Under the assumption of homogeneity, the sampling distribution of variance in log-transformed domain is constant and independent to the underlying back scattering coefficient.
-Then the observable sample variance in the log-transformed domain can be used as a measure of spatial non-homogeneity, thus statistical test on log-transformed variance can be formed to detect heterogeneity in a window of analysis.
-Using clustering algorithms, a novel speckle filtering algorithm is proposed to partition a non-homogenous area,  detected by the statistical test, into homogenous areas with estimated back scattering coefficient values.
+Logarithmic transformation has the potential to convert 
+	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
+	a simpler additive and homoskedastic distribution model.
+From this homoskedastic model, within the log-transformed domain, 
+	a few consistent measures of distance emerge.
+With these, subtractive differences become consistent and predictable. 
+We show, through experiments and analysis, that 
+	the familiar mean-squared-error (MSE) criteria can reliably serve 
+	as a single unifying performance indicator to evaluate SAR speckle filters. 
+In homogeneous areas, we establish a mathematical relationship that links the variance of 
+	log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
+For heterogeneous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
+	is shown to be equivalent to the ratio-based radiometric preservation criteria, frequently employed in the 
+	original domain. 
+Through experiments as well as analysis, we show that lower MSE suggests better feature detection and classification
+	ability, which can be an important requirement for subsequent post-filtering steps in practical SAR data processing.
+Combining bias and variance evaluation, we propose and describe the use of MSE evaluation in log-transformed domain to evaluate SAR speckle 
+	filters.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Synthetic aperture radar, stochastic-process, speckle-filtering, inverse-problems, homoskedasticity
+Synthetic aperture radar, speckle-filtering, homoskedasticity, mean-squared-error
 \end{IEEEkeywords}
-
-%\textbf{Keywords: } Synthetic Aperture Radar, speckle-filtering, homoskedasticity
 
@@
 \section{Introduction}
-%\section{Logarithmic Transformation of SAR Single look data}
 
-The nature of SAR speckle is stochastics over homogenous areas and heteroskedastic heterogenously.
-Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affect the distribution of measured SAR data.
-Speckle filtering, by and large, are estimators attempting to the unknown coefficient from observable SAR signal $(A)$.
+The nature of SAR speckle is that
+	it is stochastic even if the underlying radiometry is constant. 
+And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
+Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
+As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.
 
-SAR speckle-filtering can be and has been positioned within the context of estimation theory\cite{Touzi_2002_TGRS}.
-The statistical framework attempts to estimate unknown statistical parameters from observed data.
-The stages consist of statistical modelling, estimator development and evaluating of the performance of estimators.
-Estimators' are evaluated based on the bias and variance properties of their estimates.
-The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments.
-Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.
+SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
+The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
+%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
+%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
+Estimators are typically evaluated based on the bias and variance properties of their estimates:
+  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
+Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
+In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
+	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.
 
-For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily (cite here some latest).
-That is because: eventhough, the statistical model within individual resolution cell is well established, the applicability of its corresponding estimators is restricted to homogenous areas.
-Practical images, however, are heterogenous.
-Crucially it is this spatial variation that is of high interest.
-This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.
+Our survey of SAR speckle filter research, however, indicates 
+	a different picture from the standard practice of the statistical framework, 
+	specifically, in the stage of performance evaluation. 
+Due to the multiplicative and heteroskedastic nature of speckle noise, 
+	bias and variance evaluation may not be the most useful measures. 
+Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
+	prompting alternative evaluation criteria to be proposed.
+In fact, our survey of relevant literature fails to reveal 
+	a single universally agreed quantitative metric for the performance of speckle filters.
 
-Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review).
-Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the model to heterogenous images, virtually none has noted that spatial varition also gives rise to heteroskedasticity phenomena.
-Heteroskedastic, as explained in section ???, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean or equivalently its underlying back-scaterring coefficient $(\sigma)$.
-It is believed that heteroskedasticity give rise to serious negative impacts on various stages of speckle-filtering.
+Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
+	performance. 
+As such, many papers lack a comparative basis beyond simple visual qualitative comparison on a few image scenes. 
+While such visual comparison is useful, as an evaluative methodology, regrettably it lacks scientific objectivity. 
+Some papers do present quantitative measurements. 
+However, due to the lack of a standardized performance criteria, 
+	the evaluation metrics can change significantly from one paper to the next.
 
-In modelling, heteroskedasticity has direct consequences in the central question of homogeneity or heterogeneity.
-In normal images, the contrast or variance among neighboring pixels have been used to measure homogeneity.
-Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data.
-In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$.
-This make the problem of estimating variance is equal to the problem of estimating the mean and is the same as the main problem: estimating $\sigma$.
-The fact give rise to the vicious circle in SAR speckle filtering.
+In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
+The paper is structured as follows.
+Section \ref{sec:lit_review} briefly surveys related work in the published literature, 
+Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
+Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to 
+	evaluate different filters' speckle suppression power over homogeneous areas.
+Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
+Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
+	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
+Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.
 
-Case in point can be illustrated in the recently published improved sigma filter\cite{Lee_TGRS_2009}.
-The technique determines outlying points as being too far away from the standard deviation.
-However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required and used.
-It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.
+\section{Related Work in Literature}
+\label{sec:lit_review}
 
-Heteroskedasticity also poses numerous challenges in designing an efficient estimator.
-Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption.
-Thus it renders the efficiency of any naive Ordinary Least Square estimator in serious doubt \cite{Furno_1991_JStatCompSimul}.
-If the variance is known \textit{a priori}, it has been proven, cite Aitken, that a weighted mean estimator is the best linear unbiased estimator.
-Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators.
-The caveat however is that in SAR speckle filtering, variance is not known a priori.
-And eventhough variance can be estimated from observable values.
-And as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.
+It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
+	homogeneous and heterogeneous region evaluation.
+Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
+As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
+	output (a.k.a the speckle suppression power).
+In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
+	due in part to the following difficulties.
+The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
+The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
+	to be measured and compared.
 
-Heteroskedastic also decrease the effectiveness of estimators by increasing the variance of even best possible estimations.
-This fact makes it tricky to evaluate the performance of different estimators, even if quantitative experiments results is reported.
-In fact several quantitative simulated experiments has been carried out to compare the performance of different estimators\cite{Lee_TGRS_2009}.
-However only results of single experiment were reported.
-Due to the stochastic nature of the simulated experiement process, more experiments should be done to report the effectiveness, ie.
-variance, of each estimators' results.
+In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
+Furthermore, the application of any speckle filter in a SAR processing framework
+   should enable an improvement in the measurement, 
+	detection or classification of the underlying radiometric features.
+As shown in the subsequent sections, by applying log-transformation, 
+	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
+On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
+	preservation requirement).
+On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
+These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
+	and variance error of the output.
+As the MSE evaluation is a combination of bias and variance error, it is therefore capable of evaluating 
+	the general requirements of speckle filtering.
 
-Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation.
-Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification.
-All of these tasks requires a good similarity or discriminant functions.
-Foundation to all these is the need of a consistence sense of distance.
-Unfortunately, by definition heteroskedasticity provided inconsistent measures of distance.
-This inconsistent sense of distance coupled with the failure of the ordinary least square regression methods are believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods to underperform.
+For homogeneous scenes where the underlying radiometry is assumed to be constant, 
+	the filtered results are considered, statistically speaking, to be samples of 
+	a single but complex stochastic process.
+From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
+	of speckle filters can be judged using the familiar bias and variance evaluation.
 
-In this paper, we aim to neutralize these various impacts.
-The paper is organized as follows.
-Section ???
-will be devoted to discussion of the heteroskedastic phenomena in the original per-pixel SAR amplitude and intensity model.
-Logarithmic transformation is extended to the model and the homoskedastic property of it is asserted.
-Section ???
-will discuss how sampling distribution of variance in the log-transformed domain can be used to model various degrees of homogeneity.
-Section ???
-will presents a novel speckle filtering algorithm developed from heterogenous inference made possible by statistical testing of sample variances.
-Section ???
-will present evaluation of our estimator both quantitatively through simulated experiments and qualitatively on real-life images.
+One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
+	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
+A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
+In the log-transformed domain, the equivalent criteria for evaluation could be performed by a simple subtraction.
+In other words, it is clear that the bias evaluation in the log-transformed domain 
+	can be used to evaluate the radiometric preservation requirement of speckle filters.
 
-\section{SAR speckle statistic model}
+Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
+	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
+	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
+	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
+In this paper, we will also show that all of these standard filters preserve
+	not only the expected radiometric values
+	but also a number of subtractive and consistent measures of distance exhibited in the log-transformed domain.
 
-Useful, robust estimators require un-assuming models.
-This section will describe our model for speckle filtering.
-The first part will explain the heteroskedastic nature of original amplitude and intensity SAR data.
-In extending the original model to log-transformed domain, care has been taken to rely solely on rigorous mathematical and statistical principles.
+Several metrics have been developed to evaluate speckle suppression power.
+The most common measure is the Equivalent Number of Looks (ENL) index 
+$ENL=avg(I)^2/var(I)$
+that was proposed by Lee \cite{Lee_1981_CGIP}.
+Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
+In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is mathematically related to variance in the 
+	log-transformed domain.
+Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
+	which is the primary criteria used to evaluate speckle filters over homogeneous area.
+
+Real-life and practical images, however, are not homogeneous.
+Thus there are a number of associated difficulties in evaluating speckle filters over heterogeneous scenes.
+The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparison. 
+It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
+However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
+	real-life images.
+And hence, the need for speckle filters estimation is warranted.
+
+Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image mentioned above. 
+Under a multiplicative model, the ratio image is expected to comprise solely of
+    the noise being removed (i.e. it should be completely random). 
+Being random, this should display as little ``visible'' structure as possible. 
+However, when displaying such images for visual evaluation, the ratios that are smaller than unity are much 
+harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}. 
+We therefore propose to adopt a log-transformed domain perspective 
+  where the multiplicative noise would then be transformed into a more familiar additive model.
+More importantly, the ratio image would then become a simple subtraction image.
+The evaluation methodology for such adoption would not change. 
+Only that the residual image would become linear and additive.
+And thus it would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).
+
+Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
+of the original noised data and those of the filtered image. 
+When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
+Evaluation would then determine how closely related the two feature maps are. 
+Various methods may be applied to extract features; examples of those that have been used are the 
+	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
+	and edge map \cite{Frost_PAMI_1982}.
+While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
+of these methodologies.
+This is because feature extraction algorithms are only approximations,
+	whose accuracy is not only dependent upon the characteristics of the original image 
+		but also heavily affected by 
+		the inherent noise.
+Unfortunately, speckle filters invariably alter the noise characteristics.
+Thus, without a clear understanding of these dependencies and no absolute ground truth, 
+	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
+	how to interpret the results, especially its accuracy.
+
+Since SAR statistical models are quite well understood, 
+	simulation experiments with known ground-truth can be employed 
+		to evaluate speckle filters.
+In this paper, we also make use of a methodology similar to the ones discussed above with two important changes.
+Firstly, our simulated experiments offer absolute ground-truth.
+Secondly, our threshold-based feature extraction algorithm is extremely simple.
+More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
+This performance can be 
+	conveniently visualized by plotting the Receiver Operating Characteristics Curve (ROC).   
+It can also be objectively quantified by measuring the Area Under this Curve (AUC). 
+As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
+	feature preservation capabilities for different speckle filters.
+
+%There are two main ways that ground truths are used in evaluating speckle filters.
+%A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. 
+%Normally the image is large, with a number of different features and test conducted in once. 
+%The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. 
+%The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. 
+%It is of course, also dependent upon the nature of the test image and noise embedded process employed.
+%
+%Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
+%Since the structure is repeated many times, the combined results become more representative.
+Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
+%The drawback is that only a single type of target can be tested per image.
+These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).
+
+Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
+This is the second difficulty in evaluating speckle filters for heterogeneous scenes.
+Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
+	normally at local or regional levels.
+In fact, the common consensus is that a powerful speckle suppression filter (for example the boxcar filter) 
+	is likely to perform poorly in terms of preserving underlying radiometric differences 
+	(e.g. causing excessive blurring).
+Furthermore, we have not found many published articles combining the evaluation
+  of these two seemingly contradicting requirements.
+
+Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
+However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
+Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
+Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
+	subjective in nature.
+
+%Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
+%	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
+%The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
+%However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
+%Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
+%Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
+%	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
+%	where $E()$ denotes expectation operator.
+
+Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
+However since SAR data is heteroskedastic, which violates the assumptions of the Gauss-Markov theorem, 
+	the use of MSE is not straightforward. 
+Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
+  the ratio between the expected mean of the signal and the RMSE of the removed noise. 
+The metric is argued to be similar in interpretation to the standard signal-to-noise ratio (SNR). 
+Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.
+
+%Thus we propose the use of MSE in the homoskedastic log-transformed domain to evaluate eps. 
+%This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean).
+We also show experimentally that this MSE measure is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability can be.
+
+In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
+As the important Gauss-Markov theorem becomes applicable in this transformed domain, 
+	the use of MSE is shown to be again relevant for evaluating statistical estimators (i.e. speckle filters).
+Intuitively, each components of the MSE measure, 
+	namely bias and variance evaluation, can be mapped into 
+	the requirements of radiometric preservation and speckle suppression for speckle filters.
+Before the details of our evaluation methodology is presented and discussed, 
+	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
+
+\section{Logarithmic Transformation}
+\label{sec:log_transform}
+
+In 
+%the first portion of 
+this section, the SAR speckle model in the original domain is first shown to be multiplicative and heteroskedastic.
+The impacts of heteroskedasticity on speckle filtering is then discussed.
+Logarithmic transformation is then shown to convert original speckle data into an homoskedastic model, 
+	where the noise is not only additive, but also independent of the underlying radiometric signal.
+From the consistent and additive noise in log-transformed domain,
+    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and 
+	variance ($var(ln(I))$) are described.
 
@@
 
-SAR speckle phenomena is explained as the interference of many coherent but dephased back-scaterring components, each reflecting from different and distributed elementary scaterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}.
-These interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.
-The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.
+The SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components,
+	each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, 
+	Leith_ProcIEEE_1971}. This interference can be considered as a random walk on the 2D complex plane 
+	\cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, 
+	height, distance and thus random phase of each elementary scaterer and its response.
 
-Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}.
-Their probability density function (pdf) is given as:
+Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, the real part $A_r$ as well as 
+the imaginary part $A_i$ of the observed SAR signal $A$ can then be considered as random variables from 
+uncorrelated Gaussian distributed stochastic processes with zero means and 
+identical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:
 
@@
 
-It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distributed and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.
+It can then be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh 
+distribution and consequently the intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential 
+distributed random process.
 
 \begin{IEEEeqnarray}{l l l}
-pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
-pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
+pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -{A^2}/{\sigma^2} \right) }\\
+pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -{I}/{\sigma^2} \right) }
 \end{IEEEeqnarray}
 
-From statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to $\sigma$ unit distributions given below:
+From a statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to $\sigma$ unit distributions given below:
 
@@
 
-It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie.
-$A= \sigma A_1 $ and $I= \sigma^2 I_1 $.
-These relationships evidently manifest a mutiplicative nature.
-In fact, this condition has long been noted, but from different perspectives, in various SAR models including multiplicative model (cite JS Lee) and product model \cite{Jakeman_1980_JPhysAMathGen}.
+It is then trivial to prove that amplitude and intensity are simply scaled versions of these unit variables, 
+ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
+These relationships evidently manifest a multiplicative nature. 
+In fact, this condition has long been noted, but from different perspectives, in various SAR models including 
+the multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.
 
-If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process.
-Consequently, the population expected mean and variance of the four distributions are given in table \ref{tbl:orginal_sar_avg_var}
+If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, 
+then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic 
+process. Consequently, the population expected mean and variance of the four distributions are given in Table \ref{tbl:orginal_sar_avg_var}.
 
 \begin{table}[!h]
-\caption{ Mean and Variance of Original SAR data are both related to the scale factor $\sigma$ }
+\caption{Both the mean and the variance of original SAR data are related to the scale factor $\sigma$.}
 \label{tbl:orginal_sar_avg_var}
@@
 \hline
-$avg(A_1) = \frac{ \sqrt{\pi}}{2}$ & $var(A_1) = \frac{(4-\pi)}{4}$ \\
+$avg(A_1) = { \sqrt{\pi}}/{2}$ & $var(A_1) = {(4-\pi)}/{4}$ \\
 $avg(I_1) = 1$ & $var(I_1) = 1$ \\
-$avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ & $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ \\
+$avg(A) = {\sigma \cdot \sqrt{\pi}}/{2} $ & $var(A) = \sigma^2 \cdot {(4-\pi)}/{4} $ \\
 $avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
@@
 
-From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean.
-In the context of speckle filtering, table \ref{tbl:orginal_sar_avg_var} indicates the vicious circle: estimating variance is equal to estimating the mean and is as good as main problem, ie.
-estimating the unknown parameter $\sigma$
+From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic 
+phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional 
+expectation of the mean. 
+In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle: 
+estimating variance is equal to estimating the mean and to estimating the unknown parameter $\sigma$, 
+i.e. the main problem.
 
-The formulas above has long been noted.
-In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al has noted the ratio of expected standard deviation to mean is a constant in both cases (ie.
-$snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$).
-Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.
+The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of looks 
+(ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both 
+cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, 
+which sets the stage for the discussion of logarithmic transformtion.
+
+\subsection{The effects of Heteroskedasticity on Speckle Filters}
+
+%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
+%That is because: 
+Even though the statistical model within individual resolution cells is well established, the applicability of its 
+models is restricted to homogenous areas. 
+Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. 
+This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and 
+subsequently, what to do in the case of heterogeneity.
+
+Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed 
+review). Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous 
+original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial variation 
+also gives rise to the heteroskedasticity phenomena. 
+Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected 
+variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying 
+back-scattering coefficient $(\sigma)$.
+It is believed that this heteroskedasticity gives rise to serious negative impacts at various stages of 
+speckle-filtering.
+
+In modelling, heteroskedasticity has direct consequences to the central question of homogeneity or heterogeneity. 
+In normal images, the contrast or variance among neighboring pixels is often used to measure homogeneity. 
+Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
+In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
+This makes the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent 
+to estimating $\sigma$).
+%The fact give rise to the vicious circle in SAR speckle filtering.
+
+Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator. 
+Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
+Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, 
+together with the normal Mean Squared Error evaluation criteria in serious doubt. 
+If the variance is known \textit{a priori}, it has been proven that a weighted mean estimator is the 
+best linear unbiased estimator. 
+Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive 
+filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. 
+However, the caveat is that in SAR speckle filtering, variance is not known \textit{a priori}. 
+And even though variance can be estimated from observable values, as the vicious circle goes, 
+estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.
+
+A case in point is the recently improved sigma filter\cite{Lee_TGRS_2009}. 
+The technique determines outlying points as being too far away from the standard deviation. 
+However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required 
+and used. It is interesting to note that the MMSE estimator used to estimate the mean 
+in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.
+
+Last, but certainly not least is the bad impact of heteroskedastic on SAR image interpretation. 
+Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, 
+target segmentation and/or target classification. 
+Each of these tasks require good similarity or discriminant functions. 
+Fundamental to these is the need of a consistent measures of distance. 
+Unfortunately, by definition, heteroskedasticity leads to inconsistent measures of distance. 
+This inconsistent measure of distance, coupled with the failure of the ordinary least square regression methods, are
+ believed to cause a large class of artificial neural networks as well as a number of other computational 
+ intelligence methods for SAR classification to underperform.
 
@@
 
-We propose to consider base 2 logarithmic transformtion of SAR orignal random variables
-
-\begin{IEEEeqnarray}{l l l l l}
-L_{1^A} &=& \log_2(A_1) &=& L_{1^I} / 2 \\
-L_A &=& \log_2(A) 	&=& L_{1^A} + \log_2\sigma \\
-L_{1^I} &=& \log_2(I_1) \\
-L_I &=& \log_2(I) 	&=& L_{1^I} + 2 \log_2\sigma
-\end{IEEEeqnarray}
-
-The equations above also highlight the relationships among random variables in log-transformed domain.
-Two conclusions become evident from these formula.
-Firstly, in log-transformed domain, working on amplitude or intensity will tend to give identical results.
-Secondly, the effects of converting multiplicative nature to additive nature of logarithmic transformation is clearly manifested.
-Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as below:
-
-\begin{IEEEeqnarray}{l l l}
-pdf(L_{1^A}) &=& 2 \cdot 2^{\left[ 2 L_{1^A} - 2^{2 L_{1^A}} \right]} \\
-pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
-pdf(L_{1^I}) &=& 2^{\left[ L_{1^I} - 2^{L_{1^I}} \right]} \\
-pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} 
-\end{IEEEeqnarray}
-
-Noting that these distributions belong to Fisher-Tippet family, the population expected mean and variances are given in table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being Euler-Mascheroni constant.
-
-\begin{table}[!h]
-\caption{ Mean and Variance of Log Transformed SAR values. It can be seen that the means are biased and the variances are no longer related to $\sigma$ }
+\begin{table}[t]
+\caption{ Mean and Variance of Log Transformed values:
+  here the variance is no longer dependent on \sigma}
 \label{tbl:sar_log_domain_avg_var}
@@
 
-This result is consistence with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}.
-The main difference would be the use of base 2 logarithm which is prefered here for faster computation.
-Table \ref{tbl:sar_log_domain_avg_var} clearly confirms the condition of homoskedastic,  defined as  the independence of conditional expected variance on the conditional expectation of mean.
+In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data. 
+Base-2 is chosen for implementation reasons since it can be computed faster than either natural or 
+decimal logarithms, and yet maintains the ability to transform heterskedactic speckle into a 
+homoskedastic relationship. Thus the original variables become:
 
-Table \ref{tbl:sar_variables_properties} summarize the discussion so far.
-It can be seen that while original data, especially intensity values, should be prefered for multi-look processing, log-transformed domain, with its homoskedastic effects, offers consistence sense of dispersion and contrasts.
-Thus log transformation is proven here to be a homomorphic transformation allowing one to apply traditional linear, additive, least squared error regression signal processing (wavelet) and computational (neural networks) techniques into SAR data.
+\begin{IEEEeqnarray}{l l l l l}
+L_{1}^{A} &=& \log_2(A_1) &=& L_{1}^{I} / 2 \\
+L_A &=& \log_2(A) 	&=& L_{1}^{A} + \log_2\sigma \\
+L_{1}^{I} &=& \log_2(I_1) &=& 2 L_{1}^{A} \\
+L_I &=& \log_2(I) 	&=& L_{1}^{I} + 2 \log_2\sigma
+\end{IEEEeqnarray}
+
+Bearing the relationship among the random variables in mind, it is then trivial to 
+show that the probability distribution of these log-transformed variables are related as follows:
+
+\begin{IEEEeqnarray}{l l l}
+pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left[ 2 L_{1}^{A} - 2^{2 L_{1}^{A}} \right]} \\
+pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
+pdf(L_{1}^{I}) &=& 2^{\left[ L_{1}^{I} - 2^{L_{1}^{I}} \right]} \\
+pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} 
+\end{IEEEeqnarray}
+
+Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances 
+are obtained as in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. 
+Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$
+
+The equations above also highlight the relationships among random variables in the log-transformed domain. 
+Two conclusions become evident from these formulae. 
+Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
+Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation
+is clearly manifested. 
+Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  
+defined as the independence of the conditional expected variance on the conditional expectation of the mean. 
+This result is consistent with findings by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
+The main difference would be the use of base-2 logarithm which is preferred here for more efficient computation.
+
+Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
+It can be seen that while the original data, especially intensity values, should be preferred for 
+multi-look processing, the log-transformed domain with its homoskedastic distribution offers consistent measures of 
+dispersion and contrast. 
+Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, 
+additive, least squared error regression signal processing (including wavelets) and computational 
+(including artificial neural network) techniques on SAR data.
 
@@
 
-The result here is experimentally confirmed by inspecting measured data from a known homogenous area.
-Fig.
-\ref{fig:modelled_response} plot the histogram of observable data within a homogenous area imaged by RADARSAT2 against modelled PDF response.
-The excellent agreement between this model and various experiments has long been noted and undisputed.
-This modelling has been very successful in eplaining speckle phenomena and verified through scientific experiments \cite{Ulaby_TGRS_1988}.
+To verify this experimentally, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a 
+known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
+The excellent agreement is self-evident in the graph which confirmed the log-transformed model. 
+In fact, this modelling has been used successful in explaining speckle phenomena, also verified 
+through scientific experiments \cite{Ulaby_TGRS_1988}.
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
@@
 		 \epsfysize=1.5in
-		 \epsffile{src/log_amplitude_hist_model_pdf_scene1.eps} 	
+		 \epsffile{src/log_amplitude_histogram.eps} 	
 		 \label{amplitude}
@@
 		 \epsfysize=1.5in
-		 \epsffile{src/log_intensity_hist_model_pdf_scene1.eps} 	
+		 \epsffile{src/log_intensity_histogram.eps} 	
 		 \label{intensity}
@@
 
-Logarithmic transformation has long been noted \cite{Arsenault_JOptSocAm_1976} as being able to transform multiplicative nature of SAR data into additive nature but most of the focus has been on addition of multi-samples for multi-look processing in the log-transformed domain.
-However, in this paper the investigation of variance is the focus.
+\subsection{Consistent measures of distance in Log-Transformed domain}
 
-\section{Variance in Log-Transformed Domain}
-
-\subsection{Consistent sense of distance in Log-Transformed domain}
-
-The consistent sense is illustrated in this section from two different perspective.
-First, assume the back-scattering coefficient $\sigma$ is known a priori.
-Consider the random variable defined as the distance between an observable sample and its expected value.
+The consistent feature is explored and illustrated in this section from two different perspectives. 
+First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}. Consider the random 
+variable deviation defined as the distance between an observable sample and its expected value:
 
 \begin{IEEEeqnarray}{l l l l l}
-D^A &=& A &-& avg(A) \\
-D^I &=& I &-& avg(I) \\
-D^{L_A} &=& L_A &-& avg(L_A) \\
-D^{L_I} &=& L_I &-& avg(L_I)
+D_A &=& A &-& avg(A) \\
+D_I &=& I &-& avg(I) \\
+D_{L^A} &=& L_A &-& avg(L_A) = log_2{ \left( \frac{A}{avg(A)} \right)}\\
+D_{L^I} &=& L_I &-& avg(L_I) = log_2{ \left( \frac{I}{avg(I)} \right)}
 \end{IEEEeqnarray}
 
-Noting the results from previous section, the pdf for these variable can be trivially given as
+Noting the results from the previous section, the pdf for these variable can be derived as follows:
 
 \begin{IEEEeqnarray}{l l l}
-pdf(D^A) &=& \frac{2\left( D^A + \frac{\sqrt{\pi}}{2} \sigma \right)}{\sigma^2}e^{ \left( -\frac{\left( D^A + \frac{\sqrt{\pi}}{2} \sigma \right)^2}{\sigma^2} \right) } \\
-pdf(D^I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{\left( D^I + \sigma^2 \right)}{\sigma^2} \right) } \\
-pdf(D^{L_A}) &=& 2 \cdot 2^{\left[ \left( 2 D^{L_A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D^{L_A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
-pdf(D^{L_I}) &=& 2^{\left[ \left( D^{L_I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D^{L_I} + \frac{\gamma}{\ln2} \right)} \right]}
+pdf(D_A) &=& 2 \cdot \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)}{\sigma^2}e^{ \left[ - \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)^2}{\sigma^2}   \right] } \\
+pdf(D_I) &=& \frac{1}{\sigma^2}e^{\left[ -\left( D_I + \sigma^2 \right) / \sigma^2 \right] } \\
+pdf(D_{L^A}) &=& 2 \cdot 2^{\left[ \left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
+pdf(D_{L^I}) &=& 2^{\left[ \left( D_{L^I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} \right]}
 \end{IEEEeqnarray}
 
-It is evident from the equations that these distributions are dependent on $\sigma$ in the original SAR data but is independent of it in the log-transformed domain.
+From these equations, it is clear that these distributions, which are dependent on $\sigma$ in the original SAR data, 
+are now independent of it when presented in the log-transformed domain.
 
-From another perspective, given two adjacent resolution cells that is known to have the same but unknown back-scattering coefficient $\sigma$, consider the random variable defined as the contrast between two measured samples.
+From a second perspective, given two adjacent resolution cells that are known to have identical but 
+unknown back-scattering coefficient $\sigma$, consider, in the log-transformed domain, a random variable defined as the contrast between two 
+measured samples:
 
 \begin{IEEEeqnarray}{l l l l l}
-C_A &=& A_1^{\sigma} &-& A_2^{\sigma} \\
-C_I &=& I_1^{\sigma} &-& I_2^{\sigma} \\
-C_{L^A} &=& L_1^{A_\sigma} &-& L_2^{A_\sigma} \\
-C_{L^I} &=& L_1^{I_\sigma} &-& L_2^{I_\sigma} 
+C_{L^A} &=& L_1^{A_\sigma} &-& L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }\\
+C_{L^I} &=& L_1^{I_\sigma} &-& L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
 \end{IEEEeqnarray}
 
-The pdf of these variables can be given as:
+Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is consistent in the 
+log-domain but inconsistent in the original domain. The pdf of these variables can be expressed as:
 
 \begin{IEEEeqnarray}{l l l}
-pdf(C_A) &=& \text{ TBD dependent on } \sigma \\
-pdf(C_I) &=& \text{ TBD dependent on } \sigma \\
 pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
@@
 
-Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the sense of contrast is consistent in log-domain but in-consistent in original domain.
-Figure \ref{fig:residual_as_noise} illustrate good agreement between the analytical pdf and observable histogram of distance and contrast of the same area in log-transformed intensity RADARSAT-2 image.
-Distance is calculated as the difference between each value point and the average value of the patch, while contrast is calculated as the difference between two horizontally adjacent values in log-transformed domain.
+To illustrate this characteristic, Figure \ref{fig:residual_as_noise} is generated by using data from the RADARSAT-2 
+image. As can be seen, it shows excellent agreement between the analytical pdf and observable histogram of dispersion
+and contrast of the same area in a log-transformed intensity RADARSAT-2 image. 
+Distance is calculated as the difference between each value point and the average value of that region, 
+while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.
 
-\begin{figure}[h!]
+\begin{figure}[h]
 \centering
 %\begin{tabular}{c}
-	\subfloat[distance]{
+	\subfloat[dispersion]{
 		 \epsfxsize=1.5in
 		 \epsfysize=1.5in
-		 \epsffile{src/log_intensity_dispersion_hist_model_pdf_scene1.eps} 	
+		 \epsffile{src/log_intensity_dispersion_histogram.eps} 	
 		 \label{amplitude}
@@
 		 \epsfysize=1.5in
-		 \epsffile{src/log_intensity_contrast_hist_model_pdf_scene1.eps} 	
+		 \epsffile{src/log_intensity_contrast_histogram.eps} 	
 		 \label{intensity}
@@
 %\end{tabular}
-\caption{Observed and modelled pdf of distance and contrast in homogenous log-transformed intensity images}
+\caption{Observed and modelled pdf of dispersion 
+and contrast in homogenous log-transformed intensity images.}
 \label{fig:residual_as_noise}
@@
 
-Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the sense of observable distance in original SAR data differs, ie.
-is inconsistent, across different homogenous areas.
-The observable distance in log-transformed domain however is consistently the same across different homogenous areas.
-One possible benefit is that should the sigma filter be designed against the $pdf(C_{L^I})$, the scale estimator would no longer be required.
-
-The conclusion in this section can be extended to larger number of pixels via the analysis of observable sample variance.
+Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that 
+the measure of observable contrast in original SAR data differs, i.e. is inconsistent, across different homogenous 
+areas. On the other hand, the observable contrast in the log-transformed domain is consistently the same across 
+different homogenous areas. As such, one possible benefit is that should the sigma filter\cite{Lee_TGRS_2009} be 
+designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.
 
@@
 
-From previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as
+From the results of the previous section, two sample variance distribution ($V_x = C_x^2$) can be given analytically as 
+follows:
 
-\begin{IEEEeqnarray}{l l l}
+\begin{eqnarray}
 pdf(V_{L^I}) &=& 
-	\frac{\ln2}{2} \frac{1}{\sqrt{V_{L^I}}} \left( \frac{2^{\sqrt{V_{L^I}}}}{\left( 1+2^{\sqrt{V_{L^I}}} \right)^2} + \frac{2^{-\sqrt{V_{L^I}}}}{\left( 1+2^{-\sqrt{V_{L^I}}} \right)^2} \right)\\
+	\ln2 \frac{ 2^{\sqrt{V_{L^I}}}}{\sqrt{V_{L^I}} \left( 1+2^{\sqrt{V_{L^I}}} \right)^2} \\
 pdf(V_{L^A}) &=&
-	\frac{\ln2}{4} \frac{1}{\sqrt{V_{L^A}}} \left( \frac{2^{\sqrt{4 V_{L^A}}}}{\left( 1+2^{\sqrt{4 V_{L^A}}} \right)^2} + \frac{2^{-\sqrt{4 V_{L^A}}}}{\left( 1+2^{-2\sqrt{V_{L^A}}} \right)^2} \right)
-\end{IEEEeqnarray}
+	\ln2 \frac{2^{\sqrt{4V_{L^A}}}}{\sqrt{4V_{L^A}} \left( 1+2^{\sqrt{4V_{L^A}}} \right)^2} 
+\end{eqnarray}
 
-As log-transformed amplitude $L_A$ is simply half of log-transformed intensity values $L_I$, for brevity purposes, only results for log-transformed intensity values are presented.
+It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance 
+constant, the sampling distribution of this random variable is also independent of $\sigma$. 
+While we have observed this analytically for variances based on two samples, for a larger number of samples, 
+Monte-Carlo simulation can be used to visualise the PDF of samples' variances.
 
-It could be seen that, in log-transformed domain, not only the expected mean of observable variance is constant, the sampling distribution of this random variable is independent to $\sigma$.
-We have seen this analytically for two sample variances.
-For larger number of samples, Monte-Carlo simulation is used to visuallize pdf of sample variances.
+In summary, measurements of distance for a number of cases are shown to agree with the 
+consistent sense of variance / contrast and homoskedasticity. The measure of disimilarity can be used to test 
+if a pixel belongs to a ``known'' scatterrer, an example of its use in this way is illustrated in our kMLE speckle 
+filter \cite{Le_2010_ACRS}. The consistent sense of contrast can be used to test if any pair of measured data points belong to 
+the same class of scatterer. It may also explain why, in the original SAR domain, the ratio based 
+detector / classifier is preferred to differential measures, which are not consistent. 
+An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}. The consistent sense 
+of contrast also gives rise to a consistent measure of variance, which for example, can be used to test 
+if a group of pixels can form a homogenous area, as applied in a clustering 
+algorithm described in \cite{Le_2010_ACRS}.
 
-\begin{enumerate}
-\item Each input sample is a random and independent set of n samples each drawn from a single pdf given in $pdf(L_A)$ or $pdf(L_I)$
-\item For each input set, the sample variance is calculated
-\item For all input set, a histogram of calculated values is ploted
-\item Number of input sets data generated is pre-determined as either 10000 (rough line) or 1000000 (smooth line)
-\end{enumerate}
+\subsection{ Speckle Filtering Process And The Homoskedastic Log-transformed Domain}
+\label{sec:schema_log_images}
 
-Here a figure giving simulated sampling distribution of variances with number of samples ranging from 2-9, analytical charts of 2, homogenous sample variances of 9.
-purpose to show match of is simulation with analytical, and simulation with measured data.
+\begin{figure}[h]
+ \centering
+ \epsfxsize=2.4in
+ \epsfysize=1.2in
+ \epsffile{src/simulation_schema.eps} 	
+\caption{SAR simulation, processing and filtering schema}
+\label{fig:simul_process_filter_schema}
+\end{figure}
 
-Here gives an example showing sample variance calculated from a SAR image.
+Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and 
+SAR speckle filtering process.
+The ``SAR processor'' block indicates that either one of the following processes can occur.
+First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded 
+in $\tilde{X}$. Second is the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known 
+ground-truth pattern $X$.
+%In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
+%Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.
 
-\subsection{Statistical Hypothesis testing of homogenity}
+The ``SAR Speckle Filter'' block indicates the speckle filtering process, 
+	which takes the noisy speckled SAR data $\tilde{X}$ as input
+	and outputs $\hat{X}$ as a better estimation of the ground-truth (i.e. $X$).
+The speckle filters used in this paper are: 
+	boxcar filter, enhanced Lee filter, enhanced Kuan filter, enhanced Frost filter, Gamma Map filter 
+	and PDE filter \cite{You_TIP_2000}.
+Evidently for the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
+%Thus $MSE_{residual}^{none} = MSE_{base}$
 
-It should be noted that all discussions in section ???
-and ???
-is based on the assumption of homogenous thus single stochastic process.
-In a real given analysis area in SAR images, such condition is unknown.
-Fortunately homoskedastic property, manifested in the sampling distribution of variance, provide a method for testing this homo/heterogeneity condition.
+Logarithmic transformation offers several consistent measures of distance, which is hypothised to be 
+significant in evaluating speckle filters.
+	A case in point is in visual evaluation of filtered results obtained from real captured SAR images.
+Since the radiometric ground-truth is not available, %the most common 
+%In real SAR captured images, the radiometric ground-truth normally is not available.
+	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
+A conventional method is to investigate the ratio images between the filtered output and the noisy input images.
+Since logarithmic transformation converts these ratio into substractive residual which are consistent, residual 
+analysis can be used to analyse and evaluate the performance of speckle filters.
+%To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, 
+For visual comparison, Fig. \ref{fig:real_image_ratio_vs_residual} depicts the residual image in the log-transformed domain 
+and the ratio images in the original domain, where a simple boxcar filter has been applied to data obtained from a 
+real RADARSAT SAR image.
+``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in 
+the ratio images, although this conclusion is of course itself a subjective one.
 
-Under the null hypothesis that the given analysis area is homogenous, the theoretical distribution of sample variance has been given in previous sub-section.
-Thus given measured values and calculated log-transformed sample variance, we could accept / the notion that the given analysis area is heterogenous or homogenous with certain degrees of confidence.
-This form the basic of the statistical hypothesis test of homogenity.
+%Our qualititative conclusion is that
+%	a. it is apparently easier to notice the ``visible structure'' being removed in the residual noise pictures than the ratio mages, and
+%	b. even so, the above conclusion is at best quite subjective.
+%Thus to compare the filters against each other, 
+%	quantitative measures are preferred.
 
-The test statistics used is the sample variance.
-The pdf, and cdf of this test can be derived using Monte-Carlo simulation, illustrated above, and in the simple case of two samples can be given analytically.
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[Original Patch]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Boxcar Filtered Result]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.boxcar.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Ratio: Filtered / Original]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.ratio2.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Ratio: Original / Filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.ratio1.eps} 	
+		 \label{intensity}
+	}  \\
+	\subfloat[Log Residual: Filtered - Original]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.residual2.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Log Residual: Original - Filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.residual1.eps} 	
+		 \label{intensity}
+	} 
+\end{tabular}
+\caption{Visualising Removed ``Noise'': Ratio images in the original domain vs. Residual images in the log-transformed domain}
+\label{fig:real_image_ratio_vs_residual}
+\end{figure}
 
-This give a figure of cdf for sampling distribution of variance. It is clear that if the sample variance is higher than a cut-off degree, the null hypothesis can be rejected with certain confidence.
+\begin{subequations} \label{eqn:eval_metric}
+\begin{align}
+MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
+MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
+MSE_{noise} = MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
+MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
+\end{align}
+\end{subequations}
+%\begin{eqnarray}
+%MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
+%MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
+%MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
+%MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
+%\end{eqnarray}
 
-A table for cut-off values is also given here!
+As qualititative visual evaluation is subjective by nature,
+	quantitative metrics and measurements are preferred, if relevant and possible.
+Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, 
+are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
+When ground-truth is available, 
+	either in simulated experiments or over homogeneous area where it can be reasonably estimated, 
+	true MSE is the expected squared error between the estimated and true values.
 
-It should be noted there is a difference between accepting the null hypothesis and simply failing to reject it.
-However, in the section that followed, the decision rule in use is that if the sample variance is lower than the cut-off value, the null hypothesis is accepted.
-A  short analysis is given below to show that for the purpose of speckle-filtering the difference is negligible.
+However, in real captured SAR images where such ground truth is unknown, the evaluation can then be carried out 
+through a benchmarked MSE. 
+The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ 
+can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
+Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be 
+estimated reasonably well.
+Thus the base MSE level, which is also a measure of the speckle noise level, can also be estimated.
+Naturally, the speckle filter should remove as much noise as possible, 
+	while it also should not remove more variations than that caused by the speckle noise.
+%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base
 
-\section{Speckle Filtering in Log-Transformed domain}
+\section{Evaluating Speckle Filters on Homogeneous Areas}
+\label{sec:eval_homo}
 
-Given an area of analysis, its non-homogesousity can be detected by the statistical hypothesis test decribed above.
-If that is likely to be the case, clustering algorithm can be applied to partition the area into smaller regions.
-The process can be applied iteratively until all partitions can be considered to be homogenous (accepting the null hypothesis).
-This form the basis of our proposed speckle filtering technique.
+In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is 
+illustrated. Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
+Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
+Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is 
+probably insignificant in comparison to the other components, namely, variance evaluation. 
+Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance 
+methods of evaluation are shown to be mathematically related to the ENL index.
+The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
+over homogeneous areas.
 
-\subsection{Homogenous Maximum Likelyhood Clustering}
+\subsection{ Estimating ENL from MSE index in homogeneous areas }
+\label{sec:homogeneous_theoretical}
 
-Given a data set $X^e=\{x^e_1,...,x^e_n\}$ which follows exponential distribution $f^e(x)=\lambda e^{-\lambda x} $.
-We have already proven that the derivative data set $X^l=ln(X^e)$ follows Fisher Tippet distribution $f^l(x) = e^{d-e^d}$ with $d=x^l_i-\mu_0$.
-Next we are going to show analytically that, in the case of single-cluster, MLE of $\lambda$ from $X^e$ will equals MLE estimate of $\mu_0$ from $X^l$
+In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL 
+index. Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
+Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
+	then the MSE evaluation is reducced to variance evaluation.
+That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered 
+output in the log-transformed domain.
 
-Assume that the parameter of the distributions (ie.
-$\lambda$ or $\mu_0$ denoted as $\rho$) is known.
-MLE strategy maximize the conditional (likelyhood) probability $P(X^e | \rho )$.
-Product rule indicate that $P(X^e | \rho )=\displaystyle{\prod^n_{i=1}{P(x^e_i | \rho ) }}$.
-Maximize $P(X^e | \rho )$ also maximizes $\ln(P(X^e | \rho )) = \displaystyle{\sum^n_{i=1}{ \ln(P(x^e_i | \rho )) }}$.
-The parameter $\rho_0$ which maximizes likelyhood is found by setting
-
+Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
+%Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
+Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
+variables as: 
 \begin{equation}
-   \displaystyle{ \frac{ \partial{ \ln[P( X^e | \rho )] }  }{\partial{ \rho }} 
-= \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^e_i | \rho )) } }{ \partial{ \rho } } }} 
-= 0 }   
+var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
+\label{eqn:perf_index_theoretical}
 \end{equation}
 
-Applying to log-transformed exponential distribution $X^l = \ln( X^e )$ we have
-\begin{enumerate}
- \item $P(x^l_i | \mu) = e^{d - e^d}$ with $d=x^l-\mu $ thus $ \ln( P(x^l_i | \mu) ) = d - e^d$
- \item thus $ \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^l_i | \mu )) } }{ \partial{ \mu } } } = \sum^n_{i=1}{[ e^{ (x^l_i - \mu) } - 1 ]} } =  \sum^n_{i=1}{ \frac{ e^{ x^l_i } }{ e^{ \mu }} } - n $
- \item MLE estimate $\mu_0$ of $\mu$ is found by setting $\displaystyle{ \sum^n_{i=1}{ \frac{ e^{ x^l_i } }{ e^{ \mu_0 }}  } - n = 0}$ Noting that $ e^{ \mu_0 }$ can be moved out of the sum, that gives us $\displaystyle{ \sum^n_{i=1}{ e^{ x^l_i } } = e^{\mu_0} n }$
- \item Note that $ e^{ x^l_i } = x^e_i $ thus $\displaystyle{ \sum^n_{i=1}{ e^{ x^l_i } } = \sum^n_{i=1}{x^e_i} }$ or $\displaystyle{ e^{\mu_0} = \frac{ \displaystyle{ \sum^n_{i=1}{x^e_i} }}{n} }$
- \item This result consistent with the relation $\lambda_0 = e^{-\mu_0}$ (QED)
-\end{enumerate}
+%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
+Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
+Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
+In fact, we could estimate:
+\begin{equation}
+  var(\hat{X}^L) = \frac{1}{(L-0.5) \ln^2(2) }
+\label{eqn:perf_index_analytic}
+\end{equation}
+Thus the ENL, i.e. $L$, can be estimated as:
+\begin{equation}
+\hat{L}_{est} = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
+\label{eqn:enl_analytic}
+\end{equation}
 
-In the case of samples coming from multiple random processes clustering algorithm can be used to partition the analysis area into homogenous areas. An adapted version of clustering is given as
+The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and 
+corrupted with single look SAR-speckle PDF. 
+Different multi-look processing filters are then applied to the image patch. 
+The observable variance in the log-transformed domain is recorded, and 
+	 ENL is then estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
+The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms 
+of mean and standard deviation.
+The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
+	together with the analytical values from Eqn. \ref{eqn:perf_index_analytic}.
+These experimental results evidently validate the analysis given above.
+They also shows that 
+	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect, 
+	since ENL is supposed to be an integer, the value obtained actually corresponds very closely with the 
+	nearest correct integer result.
 
-\begin{enumerate}
-\item Initialize the cluster centers
-\item Assign each sample to a center $C_i$ that has the highest probability $P(x|C_i)$ (winner take all)
-\item Recalculate cluster centers for each $C_i$
-\item Iterate above 3 steps until there is no more changes in membership from the last iteration
-\end{enumerate}
+\begin{table}[h]
+\centering
+\begin{tabular}{r|c|c|c|c}
+ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
+\hline
+2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
+3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
+4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
+5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
+6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
+7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
+8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
+9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
+10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
+11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
+12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
+13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
+14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
+15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
+16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
+17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
+18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
+19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
+20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
+21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
+22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
+23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
+24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
+25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
+\end{tabular}
+\caption{ Speckle Suppression Power: ENL and Variance }
+\label{tab:enl_in_log_domain}
+\end{table}
 
-It could be see that the partition here is rudimental. A more elaborate gradient-descent algorithm is mentioned next
+The finding here may also help to explain other seemingly unrelated results. For example, 
+	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
+	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ 
+	to evaluate scene heterogeneity.
 
-\subsection{Heterogenous Gradient Descent Possibilistic Clustering}
+\subsection{Using log-variance to evaluate speckle filters}
 
-In this section, it is assumed that the sample is known to be coming from different underlying back-scattering radar cross section.
+Fig. \ref{fig:log_consistency_model} plots the histograms of homogenous SAR data over different radiometric values.
+Both single-look simulated and multi-look processed/box-car filtered data is displayed.
+Specifically the plots show that the log-transformed domain is consistent while the plots from the original 
+domain are not.
 
-MLE strategy is to find $C$ by maximizing criterion function: $ \Upsilon = P(X|C) = \displaystyle \prod_{i=1}^n{P(x_i|C)}$ .
-Log-transform the MLE target function leads to $\log(\Upsilon)  = \displaystyle \sum_{i=1}^n{\log[P(x_i|C)]}$ which needs to be maximized
+\begin{figure}[h]
+\begin{tabular}{c}
+	\subfloat[Single Look (Intensity)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/orig_inconsistency_none.png.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Multi Look (Intensity)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/orig_inconsistency_boxcar.png.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Single-Look in Log Domain]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/log_consistency_none.png.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Multi-Look in Log Domain]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/log_consistency_boxcar.png.eps} 	
+		 \label{intensity}
+	} 
+\end{tabular}
+%}
+\caption{The Inconsistency evident in the original SAR domain and the Emerged Consistency demonstrated in the log-transformed domain}
+\label{fig:log_consistency_model}
+\end{figure}
 
-The standard iterative gradient descent learning where each cluster center is moved in a direction so as to maximize criterion function.
-To do that the ''moving force`` that is placed on each cluster $c_j$ is to be determined as
+Fig. \ref{fig:log_consistency_filters} shows that all of the standard filters (Lee, Kuan, Frost and Gamma MAP) 
+preserve this consistency in their filtered output. Intuitively, as the boxcar filter is actually similar to 
+multi-look processing, thus its output also does exhibit the this consistency.
+This consistency will also lead to the consistent sense of distance described earlier, which is significant 
+because it is the tell-tale indicator of the consistent contrast and variance.
+This ensures applicability of various target detection/classification algorithms 
+which employ statistical properties in the un-filtered data, such as the ratio based discriminator 
+in the original domain or the differential based discriminator in the log-transformed domain.
 
-%\begin{equation}
-\begin{eqnarray}
-\label{eqn:single_cluster_move_force}
-\frac{\partial(\log(\Upsilon))}{\partial(c_j)} 
-	&=& \displaystyle \sum_{i=1}^n { \left( \frac{\partial(\log \left[ P(x_i|C) \right] }{\partial(c_j)} \right) }  
-	\nonumber \\ 
-	&=& \displaystyle \sum_{i=1}^n { \left( \frac{1}{P(x_i|C) } \cdot \frac{\partial(P(x_i|C))}{\partial(c_j)} \right) }
-\end{eqnarray}
-%\end{equation}
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[Lee filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/log_consistency_lee.png.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Kuan Filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/log_consistency_kuan.png.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Frost Filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/log_consistency_frost.png.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Gamma MAP filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/log_consistency_map.png.eps} 	
+		 \label{intensity}
+	} 
+\end{tabular}
+%}
+\caption{Filtered results: consistency in log-transformed domain}
+\label{fig:log_consistency_filters}
+\end{figure}
 
-Eqn.
-\ref{eqn:single_cluster_move_force} is nice in the sense that the force applied on each cluster centers equals the sum of impacts from each data point.
-For each point, Eqn.
-(\ref{eqn:single_cluster_sample_derivative}) form the basis of the gradient descent MLE clustering
+\begin{table}
+\centering
+\begin{tabular}{c|c|r|c|r}
+Filter & Set & Log-Variance & $\hat{L}_{est}$ & Avg Intensity \\
+\hline
+none & 1 & 3.4149 (0.0003) & 1.1095 (5.8e-5) & 3.4795 (0.0029)\\
+pde & 1 & 1.2674 (0.0014) & 2.1423 (0.0018) & 3.4806 (0.0029)\\
+map & 1 & 1.2651 (0.0055) & 2.1454 (0.0072) & 3.1627 (0.0002)\\
+lee & 1 & 0.4604 (0.0027) & 5.0206 (0.0268) & 3.4835 (0.0022)\\
+kuan & 1 & 0.2979 (0.0024) & 7.4864 (0.0574) & 3.4748 (0.0054)\\
+frost & 1 & 0.2852 (0.0012) & 7.7975 (0.0299) & 3.4799 (0.0027)\\
+boxcar & 1 & 0.2513 (0.0011) & 8.7819 (0.0353) & 3.4799 (0.0027)\\
+\hline
+none & 2 & 3.4191 (0.0068) & 1.1088 (0.0012) & 9.4925 (0.0049)\\
+pde & 2 & 1.6071 (0.0026) & 1.7952 (0.0021) & 9.4930 (0.0048)\\
+map & 2 & 1.2646 (0.0023) & 2.1459 (0.0029) & 8.6091 (0.0162)\\
+lee & 2 & 0.4653 (0.0026) & 4.9731 (0.0254) & 9.4936 (0.0080)\\
+kuan & 2 & 0.2999 (0.0026) & 7.4391 (0.0602) & 9.4761 (0.0014)\\
+frost & 2 & 0.2867 (0.0005) & 7.7595 (0.0128) & 9.4912 (0.0039)\\
+boxcar & 2 & 0.2532 (0.0006) & 8.7203 (0.0193) & 9.4914 (0.0040)\\
+\hline
+none & 3 & 3.4203 (0.0187) & 1.1068 (0.0033) & 25.6234 (0.0389)\\
+pde & 3 & 2.0353 (0.0021) & 1.5226 (0.0010) & 25.6236 (0.0389)\\
+map & 3 & 1.2799 (0.0091) & 2.1263 (0.0116) & 23.2628 (0.0304)\\
+lee & 3 & 0.4633 (2.4e-5) & 4.9926 (0.0002) & 25.6406 (0.0488)\\
+kuan & 3 & 0.2964 (0.0010) & 7.5225 (0.0244) & 25.6112 (0.0226)\\
+frost & 3 & 0.2862 (0.0008) & 7.7714 (0.0202) & 25.6263 (0.0409)\\
+boxcar & 3 & 0.2529 (0.0005) & 8.7296 (0.0178) & 25.6261 (0.0407)
+\end{tabular}
+\caption{ Filters' Performance: Homogeneous Area }
+\label{tab:homogeneous_performance_filters}
+\end{table}
 
-\begin{figure*}[t!]
+Table \ref{tab:homogeneous_performance_filters} provides a quantitative comparison among the filters.
+It shows that the filters can all preserve the underlying radiometric values, while their speckle suppression power can be equivalently measured using either variance in the log-transformed domain, or the standard ENL index.
+
+\section{Evaluating Speckle Filters on Heterogenous Area}
+\label{sec:eval_hetero}
+
+%For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
+%First, several test patterns is created to simulate and determine the performance of various speckle filters.
+%Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
+%As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.
+
+In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
+From a statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
+Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
+	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
+Experimentally, on clear-cut simple target-background patterns, the results that follow will indicate that
+	the lower the MSE achievable by a speckle filter,
+	the better the feature preservation performance recorded for its output.
+
+%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in 
+%log-transformed domain. 
+The general requirements of feature preservation, for simple scenes with only targets and clutter, can be broken 
+down into the requirements of radiometric preservation and speckle suppression.
+In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
+statistical estimators.
+Overall, while the MSE index combines the measurements of bias and variance evaluation, 
+	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
+	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
+We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.
+
+Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern 
+multiple times, the histograms of the target and background areas can be reliably obtained.
+%They are expected to be consistent in log-transformed domain.
+The target and background can then be seperated using a simple threshold based classification model.
+The separability of the two stochastic populations are judged by the standard ROC, 
+	and the quantitative and normalized metric of AUC can then be used as an evaluation metric.
+
+The types of test pattern used in this paper include the followings:
+  point targets, line targets, edge targets and a heterogeneous checker board. 
+These test patterns could of course be concatenated into a larger composite test image, 
+although we will consider them as separate images to allow easier analysis of the results.
+%However we would prefer to highlight the results separately for each individual area.
+Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention used in the 
+radar community where the target is signified by the brighter area of the image. 
+Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.
+
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[Line: each line is 2 pixels wide, separated by 6 pixels background]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/pattern_line2.png.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Edge: each stripe is 4 pixels in width]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/pattern_edge.png.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Point: each point is a $2 \times 2$ square spacing 6 pixels apart]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/pattern_point.png.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Checker board: the squares are 4 pixels wide each side]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/pattern_checker.png.eps} 	
+		 \label{intensity}
+	} 
+\end{tabular}
+%}
 \centering
-\begin{eqnarray}
-\label{eqn:single_cluster_sample_derivative}
-\frac{\partial(P(x_i|C))}{\partial(c_j)} 
-	= \left( \frac{ \partial(P(x_i|c_j) )}{\partial(c_j)}  \cdot \displaystyle \prod_{k=1,k \neq j}^c { \left[ 1-P(x_i|c_k) \right] } \right)
-	%\nonumber \\
- 	- \displaystyle \sum_{t=1,t \neq j}^c{ \left(  P(x_i|c_t) \cdot \displaystyle \prod_{k=1,k \neq j,t}^c { \left[ 1-P(x_i|c_k) \right] } \cdot \frac{ \partial(P(x_i|c_j) )}{\partial(c_j)}  \right) }
-\end{eqnarray}
-\end{figure*}
+\caption{Example windows of ground truth patterns, each $32 \times 32$ pixels in size.}
+\label{fig:hetero_patterns}
+\end{figure}
 
-\begin{enumerate}
- \item The centers are initialized, possibly from the previous section
- \item Each cluster center $c_j$ is moved in proportion to $\frac{\partial(P(x_i|C))}{\partial(c_j)}$
-\item The algorithm stops when the MLE $P(x_i|C)$ is no longer decreasing
-\end{enumerate}
+Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle. The 
+filters are then applied onto these noised images.
+From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
+evaluated by examining the separability of the two background and target populations.
+Subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
+	allows visual evaluation of target and clutter histograms and their separability.
+Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
+in subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
+respectively, and is measured by computing the Area Under these Curves (AUC).
 
-\section{Experiement Results and Discussions}%describe analysis and compare
+%visualizes the two histograms
+%The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
+%	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
+%	and is measured by computing the Area Under these Curves (AUC).
 
-\subsection{Evaluation on Simulated data}
-The experiment setup is similar to \cite{Lee_TGRS_2009}. Evaluation is based on mean AND variance of total square error between estimated value and ground-truthed original values.
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[Simulated Image]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.edge.none.fi.jpg.eps} 	
+		 \label{fig:hetero_patterns_roc_auc:amplitude}
+	} 
+	\hfill	
+	\subfloat[Kuan Filtered Image]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.edge.kuan.fi.jpg.eps} 	
+		 \label{fig:hetero_patterns_roc_auc:intensity}
+	} \\
+	\subfloat[Histograms: Unfiltered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.histograms.edge.none.fi.png.eps} 	
+		 \label{fig:hetero_patterns_roc_auc:hist_unfiltered}
+	} 
+	\hfill	
+	\subfloat[Histograms: Kuan Filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.fi.png.eps} 	
+		 \label{fig:hetero_patterns_roc_auc:hist_kuan_filtered}
+	}  \\
+	\subfloat[ROC: Unfiltered, AUC=0.738]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.roc_auc.edge.none.fi.png.eps} 	
+		 \label{fig:hetero_patterns_roc_auc:roc_unfiltered}
+	} 
+	\hfill	
+	\subfloat[ROC: Kuan Filtered, AUC=0.885]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.roc_auc.edge.kuan.fi.png.eps} 	
+		 \label{fig:hetero_patterns_roc_auc:roc_kuan_filtered}
+	} 
+\end{tabular}
+%}
+\caption{Target and Clutter Separability: Histograms and resulting ROC Curve visualisation}
+\label{fig:hetero_patterns_roc_auc}
+\end{figure}
 
-\subsection{Evaluation on Real Images}
-Other algorithms' result and comparisions.
+Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
+	can help to explain how the MSE is related to the histograms' separation capability.
+In pre-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
+\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
+Then the seperability of clutter and target populations depends only on the variance of the additive noise. 
+This variance is visualized as the horizontal spread of the histograms.
+Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance), 
+the better the separation capability.
 
-Comparisions criteria
-\begin{enumerate}
-\item Equivalent Number of Look 
-\item Point target preservation
-\item Texture preservation (if possible)
-\end{enumerate}
+In post-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
+\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
+Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
+Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
+Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
+also introduce bias errors.
+Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
+always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
+Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.
 
-\subsection{Discussions}
+%Also the speckle suppression is related to the measured variance.
+Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to 
+evaluate the separability of the two histograms. 
+Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and 
+patterns.
+It shows that the MSE is inversely correlated to this separability index.
+The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
+The results suggest that the lower MSE achievable by the filters would, in general, lead to better feature preservation.
 
-Issues to discuss
-\begin{enumerate}
- \item Decision rule used in the hypothesis test
-\item The confidence level used
-\item The learning ratio used 
-\end{enumerate}
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[Error Image: Unfiltered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.edge.none.gt.jpg.eps} 	
+		 \label{fig:hetero_patterns_mse:amplitude}
+	} 
+	\hfill	
+	\subfloat[Error Image: Kuan Filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
+		 \label{fig:hetero_patterns_mse:intensity}
+	} \\
+	\subfloat[Error Histograms: Unfiltered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
+		 \label{fig:hetero_patterns_mse:unfiltered}
+	} 
+	\hfill	
+	\subfloat[Error Histograms: Kuan-filtered]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
+		 \label{fig:hetero_patterns_mse:kuan_filtered}
+	}  
+\end{tabular}
+\caption{Bias Error Investigation: Image and Histogram Visualisation}
+\label{fig:hetero_patterns_mse}
+\end{figure}
 
-%\appendices
-\section{Conclusion}
+\begin{table}
+\centering
+\begin{tabular}{c|r|c|c|r}
+Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
+\hline
+ point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
+ point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
+ point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
+ point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
+ point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
+ point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
+ point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
+\hline
+ edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
+ edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
+ edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
+ edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
+ edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
+ edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
+ edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
+\hline
+ checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
+ checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
+ checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
+ checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
+ checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
+ checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
+ checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
+\hline
+ line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
+ line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
+ line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
+ line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
+ line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
+ line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
+ line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
+\hline
+\end{tabular}
 
-The nature of SAR speckle is stochastics.
-The speckle filtering problem has been casted into statistical estimation theory framework.
-Speckle filtering, by and large, means the removal of stochastic component in SAR images.
-Various negative effects of heteroskedastic statiscal property of original SAR values are discussed.
-Log-transformation is shown to provide homoskedasticity in SAR modelling.
-Homoskedastic feature is shown here to help speckle-filtering, it might be possible that this features might also be found helpful in neural networks and other computational intelligence approaches.
+\caption{Lower MSE suggest better feature detection, measured by the AUC index}
+\label{tab:mse_auc_in_log_domain}
+\end{table}
 
-The use of simulation and modelling in speckle filtering allow for faster simulation and evaluation of different underlying parameter estimations.
-Initial analysis can be done on simulated small data without the need of a real large image.
-Stochastics simulation also allows to evaluate efficiency of particular estimators.
-Inversely, qualititative requirements of speckle removal process can be mapped into specific requirements in designing speckle filters.
-As certain filters are good for certain frequency range, certain estimators are good in certain situations.
-Combination of estimators, aka.
-filter banks, may become achievable should their efficiency be estimated, and a situation-dependent measure indicating a prefered estimator is established and employed.
-Variance in log-transformed domain is shown to be such a measure.
+\begin{table}
+\centering
+\begin{tabular}{c|c|c}
+Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
+\hline
+edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
+point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
+checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
+line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
+\hline
+\end{tabular}
 
-The speckle filtering technique proposed in this paper has been shown to work for single-look SAR images.
-Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations.
-The filter is developed from an easy to understand winner take all clustering approach to a more fuzzy possibilistic clustering algorithm.
-Should the fuzzyness taken to a new level, an optimal filter which requires no clustering may be specified and designed.
+\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
+\label{tab:mse_auc_corr_coeff}
+\end{table}
+
+\section{Using MSE to find the most suitable speckle filter for practical SAR images}
+\label{sec:practical_conjecture}
+
+In this section, our conjecture
+%(??? you want to emphasize this is a proposal that can't be proven mathematically ?)
+%ans: it is true that the conclusion cannot be proved, due to lack of absolute ground truth in real SAR images
+%our conclusion however is 1. extended from a simulations which is believed to be in agreement with realities.
+of using MSE in the log-transformed domain to find the most suitable speckle filter 
+for practical real-captured SAR images is described.
+In these scenarios, the ground-truth, and hence the true MSE, is not available.
+Therefore, only the residential MSE is computable.
+Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark 
+MSE is also measurable.	
+Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
+This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters 
+for a captured SAR image, where the ground-truth and hence true MSE is not available.
+Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its 
+removed variation being closest to the inherent speckle noise.
+
+Experimental results are presented as empirical evidence supporting the conjecture.
+The experiments in the previous sections are repeated on single-look SAR images 
+	which are simulated from given ground-truth aerial images. 
+%The a heuristic rule is that 
+%	if the best filtered results are those with minimal MSE 
+%	then just by observing the residual MSE, 
+%	the observable measure of these results will also achieve 
+%		being the closest to the MSE of the inherent noise.
+%Besides using visual evaluation to validate the conjecture, 
+%	the full justification of this conjecture is outside the scope of this paper.
+%Real images however are more complex than the patterns illustrated above. 
+Then the filters are applied onto the simulated SAR images. 
+Fig. \ref{fig:real_simulated_images} illustrates some of the images used for our experiments.
+
+\begin{figure}
+\begin{tabular}{c}
+	\subfloat[A Rural Area in Vietnam]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[A Suburb of Ha Noi]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/simulated_images.hanoi_suburb.gt.jpg.eps} 	
+		 \label{intensity}
+	} %\\
+%	\subfloat[NTU Campus]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{src/Aerialcampus.eps} 	
+%		 \label{amplitude}
+%	} 
+%	\hfill	
+%	\subfloat[Chu Thap Island of Vietnam]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{src/fiery.eps} 	
+%		 \label{intensity}
+%	} 
+\end{tabular}
+\caption{Ground Truth Images for simulation}
+\label{fig:real_simulated_images}
+\end{figure}
+
+With the use of MSE being validated from previous experiments, 
+	the most suitable filter can be considered as the one with the lowest true MSE.
+Table \ref{tab:mse_true_noise_log_domain} shows that among the various filters used, 
+	the most suitable filter is also the filter that 
+		has its observable residual MSE value being closest to the noise MSE (4.1167 in the case of this example).
+%We validate the idea by qualititative evaluation, an example of 
+The conjecture is also validated using visual evaluation, an example of
+	which is presented in Fig. \ref{fig:real_simulated_image_results}.
+
+\begin{table}
+\centering
+\begin{tabular}{r|r|c|c}
+Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
+%\hline
+%chu thap island	& none		& 4.1066	& 1.2e-33\\
+%chu thap island	& pde			& 1.7966	& 1.0866\\
+%chu thap island	& lee			& 0.5772	& 3.2378\\
+%chu thap island	& frost		& 0.4701	& 4.8608\\
+%chu thap island	& kuan		& 0.4196	& 3.7945\\
+%chu thap island	& boxcar	& 0.4165	& 4.3952\\
+%\hline
+%ntu campus	& none		& 4.1231	& 8.7e-35\\
+%ntu campus	& pde			& 3.6598	& 0.0733\\
+%ntu campus	& lee			& 0.6335	& 3.2673\\
+%ntu campus	& frost		& 0.5776	& 5.0569\\
+%ntu campus	& boxcar	& 0.5136	& 4.5839\\
+%ntu campus	& kuan		& 0.4910	& 3.9444\\
+\hline
+Vietnam rural	& none		& 4.1174	& 4e-35\\
+Vietnam rural	& pde			& 3.8022	& 0.0368\\
+Vietnam rural	& lee			& 0.4984	& 3.2555\\
+Vietnam rural	& frost		& 0.3490	& 4.6856\\
+Vietnam rural	& kuan		& 0.3396	& 3.6877\\
+Vietnam rural	& boxcar	& 0.3107	& 4.2328\\
+\hline
+Hanoi suburb	& none		& 4.1321	& 4e-35\\
+Hanoi suburb	& pde			& 3.8004	& 0.0391\\
+Hanoi suburb	& lee			& 0.5261	& 3.2598\\
+Hanoi suburb	& frost		& 0.3811	& 4.7427\\
+Hanoi suburb	& kuan		& 0.3619	& 3.7270\\
+Hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
+\hline
+\end{tabular}
+
+\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
+\label{tab:mse_true_noise_log_domain}
+\end{table}
+
+%\begin{figure*}
+\begin{figure}
+\normalsize
+\begin{center}
+\begin{tabular}{c}
+	\subfloat[Ground-Truth Image ]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
+		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
+		 \epsffile{src/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
+		 \epsffile{src/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
+		 \epsffile{src/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
+		 \epsffile{src/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
+		 \epsfxsize=1.6in
+		 \epsfysize=1.6in
+		 \epsffile{src/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
+		 \label{intensity}
+	}
+\end{tabular}
+
+\caption{Filtering Simulated Real Images: Qualititative Validation}
+\label{fig:real_simulated_image_results}
+\end{center}
+\end{figure}
+%\end{figure*}
+
+The results from the experiments in previous sections can also be used to validate the use of residual and 
+benchmark MSE.
+The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly 
+correlated with feature classification capability, measured by the standard AUC index.
+
+The conjecture is also validated in real SAR images.
+Different speckle filters are applied onto a real RADARSAT-2 image.
+In this case, since the ground-truth is not available, 
+	only visual evaluation can be used to validate our conjecture.
+Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
+Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE 
+would probably suggest a more suitable filter.
+Fig. \ref{fig:real_image_results} tends to confirm this visually.
+%IVMThe conclusion in this can be found through further experiments with more images, 
+%IVM	which cannot be shown here due to space limitation.
+
+\begin{table}
+\centering
+\begin{tabular}{c|r|r}
+Filter & $MSE_{residual}$ & $MSE_{benchmark}$\\
+\hline
+pde & 0.2583 & 3.8584 \\
+map & 2.6936 & 1.4231 \\
+kuan & 3.3924 & 0.7243 \\
+lee & 3.4172 & 0.6995 \\
+boxcar & 3.6918 & 0.4249 \\
+frost & 4.1191 & 0.0024 \\
+\hline
+none & $MSE_{base}$ & 4.1167 
+\end{tabular}
+\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
+\label{tab:mse_in_real_image}
+\end{table}
+
+%\begin{figure*}
+\begin{figure}
+\normalsize
+\begin{center}
+\begin{tabular}{c}
+	\subfloat[PDE Filter: $MSE_{benchmark}=3.8584$]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.log.image.pde.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[MAP Filter: $MSE_{benchmark}=1.4231$]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.log.image.map.jpg.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Lee Filter: $MSE_{benchmark}=0.6995$]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.log.image.lee.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Frost Filter: $MSE_{benchmark}=0.0024$]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{src/heterogenous_real.log.image.frost.jpg.eps} 	
+		 \label{intensity}
+	}
+\end{tabular}
+
+\caption{Filtering Real Images: Smaller $MSE_{benchmark}$ suggests visually better images}
+\label{fig:real_image_results}
+\end{center}
+\end{figure}
+%\end{figure*}
+
+\section{Discussion and Conclusion}
+\label{sec:discussion}
+\subsection{Discussion}
+
+Although it is widely known that log transformation transforms multiplicative SAR speckle into additive noise, 
+	one should note that the noise is not Gaussian. In fact, figures presented in the previous sections show that 
+	they are not even centered around the origin. 
+This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
+	work very well in practice.
+To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
+	is suggested \cite{Le_2011_ACRS}. Interestingly, averaging is also the MLE operator in the SAR's original domain.
+
+Log transformation also brings about a few consistent measures of dissimilarity.
+	This consistency can be found in single-look or multi-look SAR data, 
+	as well as in filtered outputs of various ``standard'' speckle filters.
+This allows a variety of target detection/classification algorithms
+  - which exploit these consistent statistical properties -
+  to not only perform brilliantly on pre-filtered data,
+  but also be found practically working on post-filtered data.
+
+These consistent measures of distance in the log-transformed domain could probably have implications beyond speckle filtering.
+For example, in the subsequent tasks of designing target detectors or classifiers,
+  it is normally desirable for the solution to work on both unfiltered and post-filtered SAR data.
+In such cases, these consistent dissimilarity measures found in the log-transformed domain could provide a sound theoretical
+	basis. In fact, a number of proposed solutions have already appeared to exploit this feature. 
+A case in point is the simple ratio based discriminator in the original SAR domain.
+Looking backwards, in designing new speckle filters,
+  by ensuring that the filtered output preserves these consistent properties,
+	the newly designed filters would be eligible to be employed as pre-processing step for properly designed classifiers / detector.
+From a higher level perspective, the applicability of Gauss-Markov theorem and consequently a meaningful MSE 
+  predict fruitful applications for a variety of least-squared-error algorithms in the homoskedastic log-transformed domain.
+
+Of course, there are other speckle filters that do not preserve such consistency 
+	(e.g. the PDE filter \cite{You_TIP_2000}). One could argue that it would not be fair to judge such filters 
+	using the MSE criteria, which tend to favour the ``standard'' filters.
+While we respect any other criteria that have been used, we reiterate the two salient points of our approach. 
+Firstly, our MSE criteria is closely related to the basic ENL criteria.
+As shown in previous sections, experimental results indicated that
+  the ENL measures for such filter (i.e. the PDE filter) differ depending  on the radiometric values. 
+Secondly, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
+The MSE criteria is shown to be related to feature preservation requirements.
+Thus it is relevant towards subsequent target detection / classification processing, 
+	believed to be a common subsequent processing step. 
+For these two reasons, the MSE criteria is advocated.
+
+In the experiments above, speckle filters with a $3 \times 3$ sliding window were used 
+	even though we are aware that the normal window size employed is much larger. 
+The reasons for maintaining such a small window is that 
+	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk 
+	among adjacent targets.
+In addition, we focused on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
+	and do not wish to advocate any particular ``best'' filter. 
+In other words, we addressed the methodology of evaluating speckle filters, 
+	and did not directly address the design of speckle filters.
+However, interested filter designers are invited to download the open Matlab source code used in this paper 
+for evaluating their own designs
+  \footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
+
+In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators 
+(i.e. speckle filters).
+The use of small and simple patterns allows detailed analysis
+  which can then be done repeatedly and reliably against the 
+stochastic nature of SAR data.
+This also helps in mapping qualitative requirements for the speckle removal process into specific and quantitative 
+requirements in the design of speckle filters.
+Its use also provides an absolute ground-truth as a solid base for comparison of results across different papers.
+
+The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.
+Thus the result extension towards real images is only analogical.
+While the proposed rule is heuristic, 
+	the experimental results presented in this paper are shown empirically to be valid.
+
+We distinctively divided speckle filtering into two distinct scenarios, that of homogeneity and heterogeneity.
+While perfect homogeneous ground truth can be defined, 
+	different heterogeneous patterns exhibits different levels of heterogeneity. 
+Even though different measures have been proposed to evaluate heterogeneity levels.
+Unfortunately, for real captured images, where the absolute ground-truth is not available, 
+	there is no known and certain way to assert a given image as being perfectly homogeneous or 
+	absolutely heterogeneous.
+Thus while the distinction helps in clarifying the concepts, 
+	it is probably a leaky abstraction.
+
+The patterns used are chosen based on our experience, which may affects evaluation results. 
+As different patterns result in different homogeneity/heterogeneity degrees, 
+	they also appear to affect the performance and ranking of each speckle filters.
+One extreme example is that of perfect homogeneity, where boxcar filters would exhibit a respectable performance.
+While, at the other end of the spectrum: that of high heterogeneity, it is common knowledge that the boxcar filter 
+	would not perform that well.
+
+The current scheme of finding the most suitable speckle filter requires the application of all filters before 
+a decision is made, which probably demands excessive processing. 
+A possibly better alternative would be to predict the choice, escaping such massive requirements of computational power.
+This, however, is outside the scope of this paper.
+
+\subsection{Conclusion}
+
+To summarise, speckle filters are generally evaluated using many different qualitative criteria.
+To compare the filters against each other, a methodology is needed
+  to quantify these qualitative requirements,
+  and subsequently to measure, compare and evaluate these quantities in the filtered results.
+Central to all these is the need for a consistent sense of distance.
+
+Logarithmic transformation has been shown 
+  not only to convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values,
+  but also to offer a few consistent measures of distance.
+With the Gauss-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the 
+log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.
+
+Our contribution is mainly centered around a few points. 
+Firstly, a mathematical equation is established to link the ENL index to the variance in the log-transformed domain. 
+We also illustrate the use of log-variance evaluation -
+  which is shown to be equivalent to the standard ENL evaluation -
+  in evaluating the speckle suppression effect of different speckle filters.
+Secondly we show that MSE is inversely correlated to the AUC index for simulated heterogeneous areas.
+The result suggests that the smaller MSE a filter could achieve, the better it would
+be at discriminating between the underlying radiometric features.
+%The result suggests that the smaller MSE a filter could achieve, the easier it would be discriminating the underlying radiometric features.
+Thirdly, the practical contribution is to suggest an heuristic rules using the benchmark MSE to find 
+the most suitable speckle filter for any given scene. 
+Combined, we propose the use of MSE in log-transformed domain in evaluating the performance of different speckle filters in a variety of evaluation scenarios, and suggest several evaluation methodologies that may be useful in this regard.
+
+It should also be noted that similar consistent measures of distance also exist in polarimetric SAR (POLSAR) data. 
+Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.
 
